### 2023-01-24 Paper/main.tex
Testing overleaf

\documentclass[modern]{aastex631}
\usepackage{amsmath}
\usepackage{soul}

% Abundance and stellar macros
\newcommand{\mgfe}[0]{[{\rm Mg/Fe}]} 
\newcommand{\Acc}{A_{\rm cc}}
\newcommand{\AIa}{A_{\rm Ia}} 
\newcommand{\RIa}{R_{\rm Ia}^X}
\newcommand{\aIa}{\alpha_{\rm Ia}}
\newcommand{\acc}{\alpha_{\rm cc}}
\newcommand{\afe}[0]{[\alpha/{\rm Fe}]}
\newcommand{\femg}{[{\rm Fe}/{\rm Mg}]} 
\newcommand{\xmg}{[{\rm X}/{\rm Mg}]} 
\newcommand{\mgh}{[{\rm Mg}/{\rm H}]}
\newcommand{\feh}[0]{[{\rm Fe/H}]} 
\newcommand{\pIa}{p_{\rm Ia}^{\rm X}}
\newcommand{\pcc}{p_{\rm cc}^{\rm X}}
\newcommand{\fcc}{f_{\rm cc}}
\newcommand{\xfe}{[{\rm X}/{\rm Fe}]} 
\newcommand{\pIasun}{p_{\rm Ia, \odot}^{\rm X}}
\newcommand{\pccsun}{p_{\rm cc, \odot}^{\rm X}}
\newcommand{\logg}{\log(g)}
\newcommand{\teff}{T_{\rm eff}}
\newcommand{\kpc}{\rm \; kpc}
\newcommand{\kel}{\rm \; K}
\newcommand{\msun}{M_{\odot}}
\newcommand{\rgc}{R_{\rm GC}}
\newcommand{\msunvice}{M_{\odot}/M_{\odot \rm formed}}
\newcommand{\MZAMS}{M_{\rm ZAMS}}
\newcommand{\Msun}{M_{\odot}}
\newcommand{\qIax}{q_{\rm Ia}^{\rm X}}
\newcommand{\qccx}{q_{\rm cc}^{\rm X}}
\newcommand{\qagbx}{q_{\rm AGB}^{\rm X}}
\newcommand{\qIa}{q_{\rm Ia}}
\newcommand{\qcc}{q_{\rm cc}}
\newcommand{\qagb}{q_{\rm AGB}}
\newcommand{\Aagb}{A_{\rm AGB}}
\newcommand{\eumg}{[{\rm Eu}/{\rm Mg}]} 
\newcommand{\mgmn}{[{\rm Mg}/{\rm Mn}]} 
\newcommand{\alfe}{[{\rm Al}/{\rm Fe}]} 
\newcommand{\omg}{[{\rm O}/{\rm Mg}]} 
\newcommand{\xo}{[{\rm X}/{\rm O}]} 
\newcommand{\xh}{[{\rm X}/{\rm H}]} 
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\ejg}[1]{\textcolor{red}{EJG: #1}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

%\submitjournal{ApJ}

\newcommand{\name}{\textsl{Foo}} % Hogg's just making this up; change it!!
\newcommand{\documentname}{\textsl{Article}}

\shorttitle{data-driven few-process model for nucleosynthesis}
\shortauthors{griffith and hogg}
\addtolength{\topmargin}{-0.4in} % trust in Hogg
\addtolength{\textheight}{0.7in} % trust in Hogg
\setlength{\parindent}{1.6em}
\renewcommand{\paragraph}[1]{\bigskip\par\noindent{\textbf{#1}}~---}
\sloppy\sloppypar\raggedbottom\frenchspacing % Trust Hogg

\graphicspath{{./}{Figures/}}
\begin{document}

\title{\name: A data-driven few-process model for nucleosynthesis}

\correspondingauthor{Emily J. Griffith}
\email{Emily.Griffith-1@colorado.edu}

\author[0000-0001-9345-9977]{Emily J. Griffith}
\altaffiliation{NSF Astronomy and Astrophysics Postdoctoral Fellow}
\affiliation{Center for Astrophysics and Space Astronomy, Department of Astrophysical and Planetary Sciences, University of Colorado, 389~UCB, Boulder,~CO 80309-0389, USA}

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726~Broadway, New~York,~NY 10003, USA}
\affiliation{Max-Planck-Institut f{\"u}r Astronomie, K{\"o}nigstuhl 17, D-69117 Heidelberg, Germany}
\affiliation{Flatiron Institute, 162 Fifth Avenue, New~York,~NY 10010, USA}

% \author[0000-0001-7775-7261]{David H. Weinberg}
% \affiliation{The Department of Astronomy and Center of Cosmology and AstroParticle Physics, The Ohio State University, Columbus, OH 43210, USA}
% \affiliation{The Institute for Advanced Study, Princeton, NJ, 08540, USA}

\begin{abstract}\noindent % trust Hogg
Testing

Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
We analyze YYY abundance ratios (ratioed to Mg) for XXXX stars from APOGEE DR17 with a flexible two-process model, in which all element process amplitudes are free parameters.
The two-process model describes each element abundance of each star as the vector sum of a CCSN and SNIa process.
Prior work derives process amplitudes from median observed high-Ia and low-Ia abundance trends; we relax these assumptions and simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
We compare fit parameters from this new method to those derived from prior work [that the two methods produce similar results but with XXX differences and identify similar outlier stars??].
Our flexible method---dubbed \name---tests the validity of the standard two-process assumptions, such as Mg being a pure CCSN element, and that Solar abundances are generated by a roughly half-half combination of CCSN and SNIa processes.
We find [that the assumptions of prior work are generally confirmed??].
We capitalize on the flexibility to explore the addition of a third process, agnostic about its origin.
The third process most improves [X elements? most significant for X elements?].
Most importantly, \name{} can be extended to populations at very low metallicity, and populations without two clear abundance sequences, such as the LMC/SMC, Sagittarius, and Gaia-Enceladus (??), making it a general diagnostic for enrichment; in principle, it can also be used to constrain fundamental nucleosynthetic parameters.
\end{abstract}

\keywords{foo --- bar}

\section*{}\clearpage
HOGG SAY: Here are some things to do or think about:
\begin{itemize}
  \item Should we think of this as a 2-process model or as a $K$-process model, where $K$ is often 2? I'm leaning towards $K$.
  \item \ejg{I like the K-process model. (This is named $N$-Process model in W22)}
  \item What are we going to do in terms of interpreting the results? These process vectors aren't exactly yields; they are something way more complicated, right?
  \item \ejg{Interpret in terms of $\fcc$. Can also make inferences about the metalicity dependence of SNIa/CCSN enrichment to given elements based on how $\qcc$ and $\qIa$ evolve with time.}
\end{itemize}

\section{Introduction}\label{sec:intro}

After hydrogen, helium, lithium, and beryllium, essentially all other naturally occurring elements are made in stars, and the collisions of stars.
We are literally made of star stuff.
Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed (for most elements) record of the element abundances in the gas from which the star formed (though see \ejg{Add citations}).
These birth abundances were set by a combination of nucleosynthetic processes involved in making heavy atomic nuclei, and astrophysical processes involved in delivering atoms from stellar interiors to star-formation sites \citep[e.g.,][]{johnsonja2020}.
Thus nuclear physics and a wide swath of astrophysics are critically intertwined in our understanding of stellar surface abundances.
That's important, and motivates a lot of theoretical, experimental, and observational work in nuclear physics and astrophysics.

At the present day, stellar surface abundances are not very well explained by \textsl{ab initio}, physics-driven models.
Yields vary from set to set, as they are dependent on progenitor properties and explosion assumptions \citep[e.g.,][]{rybizki2017, griffith2021b}. 
The wide parameter space of progenitor and supernovae models coupled with uncertainties in reaction rates and explosion physics hinder the creation of an accurate nucleosynthetic model from theory alone.
In the long run, it is incumbent upon us to understand these issues and correct the assumptions or calculations underlying our nucleosynthetic and astrophysical models.
In the short run, however, we gather data---tens of millions of abundance measurements on millions of stars in different astronomical surveys such as RAVE, SEGUE, LAMOST, Gaia-ESO, APOGEE, GALAH, and H3 \citep{steinmetz2006, yanny2009, gilmore2012, desilva2015, luo2015, majewski2017, conroy2019}.
This raises the question: \emph{Can we take a data-driven approach to nucleosynthesis?}

In this \documentname{}, we build a purely data-driven model for the surface element abundances observed in stars.
We treat each star as being a linear combination of two nucleosynthetic processes, one of which is primarily responsible for the $\alpha$-element Mg \citep[core collapse supernovae (CCSN), e.g.][]{andrews2017}, and one of which is primarily \emph{not} (Type-Ia supernovae (SNIa)).
Beyond that up-front assumption, we try to be agnostic about how the elements are produced.

We build upon the work of \citet[][hereafter G22]{griffith2019, griffith2022} and \citet[][hereafter W22]{weinberg2019, weinberg2022}, who used the bimodality in [Mg/Fe] vs. [Fe/H] \citep[e.g.,][]{fuhrmann1998, bensby2003, adibekyan2012} to separate stars into populations with high and low SNIa enrichment. Using the median [X/Mg] vs. [Mg/H] abundance trends, these works explain data from the \textsl{GALAH}\footnote{GALAH = GALactic Archaeology with HERMES.} and SDSS-IV \textsl{APOGEE}\footnote{APOGEE = Apache Point Observatory Galactic Evolution Experiment, part of the Sloan Digital Sky Survey} surveys, respectively, with a two-process model. Because the median abundance trends in [X/Mg] vs. [Mg/H] space are largely insensitive to aspects of chemical evolution, such as outflows and variations in star formation history \citep{weinberg2019}, the population abundance trends are set by the nucleosynthetic processes and can be used to empirically constrain Galactic enrichment. To fit the two-process model to survey data, G22 and W22 assume that Mg is purely produced by CCSN, Fe is produced in equal amounts by CCSN and SNIa, and that the CCSN/SNIa yields of Mg and Fe are metallicity independent. While the first assumption is firmly grounded in nucleosynthetic theory \citep[e.g.,][]{andrews2017, rybizki2017}, the others are based on APOGEE abundance patterns and may not be realistic constraints.

Beyond the two-process model, many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep{kilpatrick2017}, or atypical supernovae explosion. After predicting stellar abundances from $\feh$ and $\mgfe$, \citet{ting2022} identify correlated abundance residuals that are unexplained by observational uncertainties, indicative of additional nucleosynthetic processes that standard disk CCSN and SNIa enrichment cannot explain. Results from G22 and W22 support this conclusion, and both works attempt to add additional processes to their models to account for non-CCSN and non-SNIa enrichment, though in a very restrictive manner.

\ejg{Add paragraph about how little work has been done to optimize stellar abundances to solve for enrichment processes in a more data-driven way. \citet{casey2019} apply a clustering algorithm to GALAH DR2 data, identifying latent factors corresponding to 6 processes. Difficult to interpret and breaks down with more data.}

In this work, our main innovations are to relax the assumptions made in G22 and W22, to be more agnostic about the nucleosynthetic processes, and to be more principled with the measurements or inferences from data. The benefit we will gain from this is better performance at fitting the data.
The cost we might pay is a possible reduction in interpretability.
We'll come back to all that at the end.

\ejg{Placeholder. We attempt to find the intersection between reliable facts about nucleosynthesis and good abundance measurements. We are trying to build an edifice of nucleosynthesis on a small number of facts. Because Mg is well-measured and well-understood theoretically, it's a good foundation for our model. We have a degeneracy with Fe because we don't have a nucleosynthesis fact.}

In Section~\ref{sec:data} we describe the APOGEE data samples fit in this paper. In Section~\ref{sec:model} we outline our $K$-process model, the assumptions we make, and our implementation of the optimization routine. We apply the data-driven $K$-process model to the W22 APOGEE sample and present our findings in Section~\ref{sec:results_W22}. \ejg{Add ending discussion sections...}

\section{Data Samples}\label{sec:data}

In this paper, we employ stellar abundances from APOGEE DR17 \citep{abdurrouf2022}, part of SDSS-IV \citep{majewski2017}. The APOGEE survey obtains high-resolution ($R\sim22,500$) near-infrared (IR) observations \citep{wilson2019} for stars in the Galactic disk, halo, bulge, and nearby satellites/streams. Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile. Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and parameters are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}. See \citet[][DR16]{jonsson2020} and Holtzman et al. (in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citep{zasowski2013, zasowski2017, santana2021} for a discussion of survey targeting.
\ejg{Is the DR17 paper out yet?}

APOGEE DR17 reports stellar parameters including $\teff$ and $\logg$ as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, Ti, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars. Among these elements and ions, some are measured more precisely than others. We exclude Ti from our analysis as there are large differences between the abundances derived from the \ion{Ti}{1} and \ion{Ti}{2} lines \citep{jonsson2020}. We also exclude P, as the P abundances are measured from a few very weak spectra features, and the abundance distribution displays strong artifacts \citep{jonsson2020}. Among the remaining elements, we note the following concerns:
\begin{itemize}
\itemsep0em
    \item Na - Spectral features are weak, one of the least precise elements in APOGEE (but matches optical data pretty well)
    \item S - Large abundance scatter in observations and no verification with optical data
    \item Cr - Significant systematic artifacts at super solar metallicity \citep{griffith2021a}
    \item Mn - Strong NLTE effects exist that are not taken into account
    \item Co - Abundance derived from one line, causing larger abundance scatter
    \item Ce - Abundance derived from one line. DR17 is the first time Ce abundances have been included in APOGEE data products. 
    \item Al,  V, and Mn require large offsets to place solar metallicity stars at solar [X/Fe].
\end{itemize}
\ejg{Will want to condense list for paper. Add a short description of some abundance systematics that we see re \citet{jonsson2020} and \citet{griffith2021a}}.

In this paper, we will explore two subsamples of APOGEE DR17 data: (1) the W22 sample, optimized to minimize statistical and systematic errors while probing a large portion of the Galactic disk, and (2) a sample with less stringent cuts, but better coverage of the low-metallicity ([Fe/H] $< -0.5$) disk.

\subsection{The W22 Sample}

W22 select a subset of APOGEE DR17 stars with the goal of minimizing statistical errors from poor observations and systematic errors from abundance trends with $\teff$ and/or $\logg$ while preserving a sufficient number of stars to conduct a meaningful statistical analysis across the Galactic disk. To remove poor quality data points, W22 require ASPCAP flags \texttt{STAR\_BAD} \texttt{NO\_ASPCAP\_RESULT} equal zero and remove all stars with \texttt{FE\_H\_FLAG} or \texttt{MG\_FE\_FLAG} set. They only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}. In addition to these quality cute, W22 apply the following sample selection cuts:
\begin{itemize}
\itemsep0em
    \item $R=3-13$ kpc, $|Z| \leq 2$ kpc (distances from \citet{leung2019})
    \item $-0.75 \leq \mgh \leq 0.45$
    \item S/N $\geq 200$ for $\mgh > -0.5$ and S/N $\geq 100$ for $\mgh < -0.5$
    \item $\logg = 1-2.5$ dex
    \item $\teff = 4000-4600$ K
\end{itemize}
By selecting stars from a small range of $\logg$ and $\teff$, they eliminate the red clump stars and minimize stellar parameter-dependent abundance trends \citep[see][]{griffith2021a}. The cuts result in a sample of 34,410 stars.

W22 present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, and Ce. While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant. W22 consider C+N as an element in their analysis, taking [(C+N)/H] to be 
\begin{equation}
    [\text{C+N}/\text{H}] = \log_{10}(10^{\text{[C/H]}+8.39} + 10^{\text{[N/H]}+7.78}) - \log_{10}(10^{8.39} + 10^{7.78})
\end{equation}
using logarithmic solar abundances for C (8.39) and N (7.78) from \citet{grevesse2007}.

\ejg{W22 use X/Fe error from APOGEE and don't convert it to X/Mg....Use C/Fe error for the C+N value because the ratio is mostly C... Need error discussion here and in next section.}

In the analysis of each element, X, stars with \texttt{X\_FE\_FLAG} are dropped (maximum of $\sim 560$ for Ce). We plot the distribution of abundances in [X/Mg] vs. [Mg/H] in Figure~\ref{fig:w22_xmg}. All elemental abundances have zero-point offsets applied and have been de-trended for correlations with $\teff$, as in W22 (see their Table 1).

\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{Figures/W22_xmg.pdf}
    \caption{W22 stellar abundance distributions. The number in the top right corner indicates the number of stars used in the analysis of that element. Elements are ordered by atomic number.}
    \label{fig:w22_xmg}
\end{figure}

\subsection{Our Sample}

\ejg{Not sure if this should go here or after we discuss the success of the K-process model on W22 data...}

While the W22 sample presented above is a good first test case of \name, we are interested in the behavior of our model when applied to a wider sample of data, in particular extending the metalicity range to lower values of [Mg/H]. To construct this sample, we apply the same quality cuts as taken by W22 (\texttt{STAR\_BAD} = 0, \texttt{NO\_ASPCAP\_RESULT} = 0, \texttt{FE\_H\_FLAG} = 0, \texttt{MG\_FE\_FLAG} = 0, and (\texttt{EXTRATARG} = 0). We add a cut for stars with the \texttt{ROTATION\_WARNING} flag set. We take the following sample selection cuts: 
\itemsep0em
\begin{itemize}
    \item S/N $\geq 100$
    \item $0 < \logg < 2.5$ dex
    \item $\teff = 4000-4600$ K
\end{itemize}
We make no cuts on the Galactic location, including stars from across the Galactic disk and halo, and make no cuts on the [Mg/H] values of our sample. The wider $\logg$ ranges expand the sample of giants. We select stars in the same small $\teff$ range as W22 to exclude the red clump \citep{vincenzo2021} and cool stars that show abundance artifacts \citep{jonsson2020}.
Our final sample includes 51,386 stars and extends to [Mg/H]=-2.2. As in W22, we only analyze [X/Mg] abundances for stars where the [X/Fe] value is unflagged. This has a minimal effect for most elements but reduces the sample size to 49,851 for Ce.

\ejg{Plus a magnitude cut as a proxy for distance? Right now I have H < 12, but I don't think that the cut impacts the global trends much...}

\begin{figure}[htb!]
    \centering
    \includegraphics[width=\textwidth]{Figures/xmg.pdf}
    \caption{Stellar abundance distributions for our wider stellar sample. The number in the top right corner indicates the number of stars used in the analysis of that element. Elements are ordered by atomic number.}
    \label{fig:w22_xmg}
\end{figure}

The expansion of the data sample does introduce abundance systematics that the W22 selection sought to exclude. As discussed in \citet{jonsson2020} and \citet{griffith2021a}, APGOEE DR16 and DR17 suffer from poorly understood abundance artifacts, such as a ``finger'' in [$\alpha$/M] and low-[X/Fe] banding in elements such as Al and Ni. In our expanded data set, we observe potential abundance artifacts in Al, K, V, and Cr. \ejg{Add more here. Stricter temperature cut helped to remove the artifacts...}

\ejg{Should check the spatial distribution of the final sample. Need to decide if we will also apply zero point offsets}

\ejg{Also need to add discussion that almost all stars below [Mg/H] of -0.75 appear chemically accreted...}

\section{Methods and Models}\label{sec:model}

We model each star as the sum of a CCSN and SNIa process vector (constant for all elements) and CCSN/SNIa amplitude such that

\begin{equation}
    m_{ij} = \log_{10}(A_i^{\rm CC} \vec{q}_{{\rm CC}, j}^{\,Z} + A_i^{\rm Ia} \vec{q}_{{\rm Ia}, j}^{\,Z}) 
\end{equation}

where the observed value of $\xh$ can be described as the model plus observational noise and/or contributions from an additional non-CCSN/SNIa process:

\begin{equation}
    \xh_{ij} = m_{ij} + \text{noise}.
\end{equation}

We fit this model to the data with a chi-squared ($\chi^2$) minimization such that

\begin{equation}
    \chi^2 = \sum_{i=1}^{N} (\xh_{ij} - m_{ij})^{\rm T} c_j^{-1} (\xh_{ij} - m_{ij}) + \text{regularization}~,
\end{equation}
where $c_j^{-1}$ is a matrix of the inverse variance squared,
\begin{equation}
    c^{-1} = \begin{bmatrix}
\frac{1}{\sigma_j^2} & 0 & ...\\
0 & \frac{1}{\sigma_j^2} & ... \\
0 & 0 & ... 
\end{bmatrix}
\end{equation}
$N$ stars, such that $1 \leq i \leq N$, and ``regularization'' stands in for some additional penalization terms that we will describe below.

$M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, CN, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, Ce} \}$, the elements in APGOEE DR17 and used in \citet{weinberg2022}.

\subsection{Assumptions}\label{subsec:assumptions}

Some of the assumptions that go into the two-process model \name{} are the following:

\paragraph{Two processes}
HOGG whatever.

\paragraph{Linearity}
At every metallicity, the abundances of a star can be expressed as a linear combination of two processes.
These processes themselves might depend on metallicity, but a linear sum is sufficient to explain all element abundances.
Because of dependences of yields on detailed abundances, and because different stars can get to their metallicities by different histories, this assumption must be slightly wrong in detail.

\paragraph{Non-negativity}
All process amplitudes for all elements are non-negative (elements heavier than XXX are only produced, not ever destroyed, by the two processes),
and all stars are made of a non-negative sum of the two non-negative processes.
This makes the model similar to a non-negative matrix factorization (\citealt{nnmf}).

\paragraph{Magnesium is a core-collapse element only}
All magnesium is produced in the core-collapse (CC) process, and none in the type-Ia (Ia) process.
This breaks (something like) a rotational symmetry in the process space, and makes the processes interpretable in terms of supernova types.

\paragraph{Metallicity dependence}
The fact that all magnesium is produced in the CC process is an assumption that is independent of metallicity.
All other process vectors are permitted to float as a function of metallicity.
The only exceptions are the magnesium level in the CC process and the iron level in the Ia process, but these constraints are just model normalizations; they don't restrict the overall model freedom, which is about abundance ratios.

\paragraph{\textsl{APOGEE} abundances}
We are assuming that the \textsl{APOGEE} abundances can be used for this project.
This is not quite the same as assuming that they are correct.
It is more like assuming that it is possible and useful to build an interpretable 2-process model to explain them.
EMILY: WE NEED A DATA SECTION that explains how we put together the data and which data we used.

\bigskip
These assumptions (above) mirror the assumptions of prior work (\citealt{griffith2022}; \citealt{weinberg2022}) but they are weaker.
In particular, they don't assume anything about the relationships between the processes and the morphologies of observed element-abundance ratio diagrams.
In addition to the above assumptions, which are about nucleosynthesis, there are assumptions about the data:

\paragraph{Measurement uncertainties}
HOGG

\paragraph{Likelihood function}
HOGG

\subsection{Constraints and Regularizations}\label{subsec:regularizations}

Some of the assumptions in our model directly translate to constraints and regularization.

We always enforce that the process vectors and amplitudes are greater than zero:
\begin{equation}
    \vec{q}_{{\rm CC}, j}^{\,Z}, \, \vec{q}_{{\rm Ia}, j}^{\,Z} \geq 0 \quad \forall \; j
\end{equation}

\begin{equation}
    A_i^{\rm CC}, \, A_i^{\rm Ia} \geq 0 \quad \forall \; i.
\end{equation}

We will start with the constraints from \citet{weinberg2022} as well:

\begin{equation}
    \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1 \quad \vec{q}_{{\rm Ia, Mg}}^{\,Z_{\odot}} = 0 \quad 
    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.5 \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.5 
\end{equation}

\begin{equation}
    \vec{q}_{{\rm CC, Mg}}^{\,Z} = \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} \quad 
    \vec{q}_{{\rm CC, Fe}}^{\,Z} = \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}}  \quad 
    \vec{q}_{{\rm Ia, Fe}}^{\,Z} = \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} 
\end{equation}

\begin{equation}
    \vec{q}_{{\rm CC}, j}^{\,Z_{\odot}} + \vec{q}_{{\rm Ia}, j}^{\,Z_{\odot}} = 1 \quad \forall \; j
\end{equation}

\section{Experiments and Results}

\section{Discussion}

\begin{itemize}
    \item What is the connection between this model and latent variable models of machine learning
    \item Casual inferences - which abundances are caused by the Mg abundance and which are not (statistician perspective)

\end{itemize}

\section{Summary}

\section{Acknowledgements}
It is a pleasure to thank
  Soledad Villar (JHU)
for valuable discussions.
This project benefited enormously from the Python package \texttt{jax} \citep{jax}.
E.J.G. is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.

% \software{Matplotlib \citep{hunter2007}, NumPy \citep{harris2020}, Pandas \citep{pandasa, pandasb}, Astropy \citep{astropy2013, astropy2018, astropy2022}, astroNN \citep{bovy2017}, EXOFASTv2 \citep{eastman2013, eastman2019}, iSpec \citep{blanco2014, blanco2019}, MOOG \citep{sneden1973}, galpy \citep{bovy2015, mackereth2018}}, jax \citep{jax}

\bibliography{sample631}{}
\bibliographystyle{aasjournal}

\end{document}

### 2023-02-22 Paper/main.tex
Testing overleaf change
Updates to overleaf intro, data, and methods

@@
 \documentclass[modern]{aastex631}
+%\documentclass[twocolumn]{aastex631}
+
 \usepackage{amsmath}
@@
 \begin{abstract}\noindent % trust Hogg
-Testing
-
 Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
@@
 Our flexible method---dubbed \name---tests the validity of the standard two-process assumptions, such as Mg being a pure CCSN element, and that Solar abundances are generated by a roughly half-half combination of CCSN and SNIa processes.
-We find [that the assumptions of prior work are generally confirmed??].
+We find [that the assumptions of prior work are generally confirmed. But that the inferred Fcc value of Fe peak elements is strongly dependent upon the chosen CCSN process strength for Fe].
 We capitalize on the flexibility to explore the addition of a third process, agnostic about its origin.
@@
 After hydrogen, helium, lithium, and beryllium, essentially all other naturally occurring elements are made in stars, and the collisions of stars.
-We are literally made of star stuff.
+%We are literally made of star stuff.
 Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed (for most elements) record of the element abundances in the gas from which the star formed (though see \ejg{Add citations}).
 These birth abundances were set by a combination of nucleosynthetic processes involved in making heavy atomic nuclei, and astrophysical processes involved in delivering atoms from stellar interiors to star-formation sites \citep[e.g.,][]{johnsonja2020}.
-Thus nuclear physics and a wide swath of astrophysics are critically intertwined in our understanding of stellar surface abundances.
-That's important, and motivates a lot of theoretical, experimental, and observational work in nuclear physics and astrophysics.
+Thus nuclear physics and a wide swath of astrophysics are critically intertwined in our understanding of stellar surface abundances, motivating theoretical, experimental, and observational work.
 
@@
 In the long run, it is incumbent upon us to understand these issues and correct the assumptions or calculations underlying our nucleosynthetic and astrophysical models.
-In the short run, however, we gather data---tens of millions of abundance measurements on millions of stars in different astronomical surveys such as RAVE, SEGUE, LAMOST, Gaia-ESO, APOGEE, GALAH, and H3 \citep{steinmetz2006, yanny2009, gilmore2012, desilva2015, luo2015, majewski2017, conroy2019}.
+In the short run, however, we gather data---tens of millions of abundance measurements on millions of stars in different astronomical surveys such as RAVE, SEGUE, LAMOST, Gaia-ESO, APOGEE/MWM, GALAH, and H3 \citep{steinmetz2006, yanny2009, gilmore2012, desilva2015, luo2015, majewski2017, conroy2019}.
 This raises the question: \emph{Can we take a data-driven approach to nucleosynthesis?}
@@
 In this \documentname{}, we build a purely data-driven model for the surface element abundances observed in stars.
-We treat each star as being a linear combination of two nucleosynthetic processes, one of which is primarily responsible for the $\alpha$-element Mg \citep[core collapse supernovae (CCSN), e.g.][]{andrews2017}, and one of which is primarily \emph{not} (Type-Ia supernovae (SNIa)).
+We treat each star as being a linear combination of nucleosynthetic processes, beginning with one that is primarily responsible for the $\alpha$-element Mg \citep[core collapse supernovae (CCSN), e.g.][]{andrews2017}, and one that is primarily \emph{not} (Type-Ia supernovae (SNIa)).
 Beyond that up-front assumption, we try to be agnostic about how the elements are produced.
@@
 
-\ejg{Add paragraph about how little work has been done to optimize stellar abundances to solve for enrichment processes in a more data-driven way.
-\citet{casey2019} apply a clustering algorithm to GALAH DR2 data, identifying latent factors corresponding to 6 processes.
-Difficult to interpret and breaks down with more data.}
+To date, survey abundances have not been fully exploited to create a data-driven model of nucleosynthesis.
+While works such as \citet{ting2012}, \citet{casey2019}, and \citet{ratcliffe2022} effectively use clustering algorithms to identify elements with like sources and reduce abundance dimensionality, the results are difficult to translate into a model of nucleosynthesis.
+Clustering components can be linked to nucleosynthesis sources and enrichment history, but cannot be used to describe the enrichment of a single star.
+\ejg{Add more description of these works?}
 
 In this work, our main innovations are to relax the assumptions made in G22 and W22, to be more agnostic about the nucleosynthetic processes, and to be more principled with the measurements or inferences from data.
-The benefit we will gain from this is better performance at fitting the data.
-The cost we might pay is a possible reduction in interpretability.
-We'll come back to all that at the end.
+In our model, we find the intersection between reliable facts about nucleosynthesis and good abundance measurements to build an edifice of nucleosynthesis.
+\ejg{Add more about high-quality metallicity labels and our model.}
 
-\ejg{Placeholder.
+This paper is organized as follows.
+In Section~\ref{sec:data} we describe the APOGEE data and the stellar samples employed in this paper.
+In Section~\ref{sec:model} we outline our $K$-process model, the assumptions we make, and the implementations of constraints and regularization.
+We apply the data-driven $K$-process model to the APOGEE data in Section~\ref{sec:optimize} and compare our results to those of W22 in Section~\ref{sec:results_W22}.
+In Section~\ref{sec:results_broad} we extend the optimization to a broader data sample, discussing the behavior at low metallicity and displaying the power of our optimized K-process abundances labels.
+Finally, we summarize our results in Section~\ref{sec:summary}
+
+%The benefit we will gain from this is better performance at fitting the data.
+%The cost we might pay is a possible reduction in interpretability.
+%We'll come back to all that at the end.
+
+%\ejg{Placeholder.
 We attempt to find the intersection between reliable facts about nucleosynthesis and good abundance measurements.
@@
 We have a degeneracy with Fe because we don't have a nucleosynthesis fact.}
-
-In Section~\ref{sec:data} we describe the APOGEE data samples fit in this paper.
-In Section~\ref{sec:model} we outline our $K$-process model, the assumptions we make, and our implementation of the optimization routine.
-We apply the data-driven $K$-process model to the W22 APOGEE sample and present our findings in Section~\ref{sec:results_W22}.
-\ejg{Add ending discussion sections...}
 
@@
 Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile.
-Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and parameters are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}.
+Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and abundances are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}.
 See \citet[][DR16]{jonsson2020} and Holtzman et al.
-(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citep{zasowski2013, zasowski2017, santana2021} for a discussion of survey targeting.
-\ejg{Is the DR17 paper out yet?}
+(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017} and \citet{santana2021} for a discussion of survey targeting.
 
-APOGEE DR17 reports stellar parameters including $\teff$ and $\logg$ as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, Ti, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
+APOGEE DR17 reports stellar parameters, including $\teff$ and $\logg$, as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, \ion{Ti}{1}, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
 Among these elements and ions, some are measured more precisely than others.
@@
 We also exclude P, as the P abundances are measured from a few very weak spectra features, and the abundance distribution displays strong artifacts \citep{jonsson2020}.
-Among the remaining elements, we note the following concerns:
-\begin{itemize}
-\itemsep0em
-    \item Na - Spectral features are weak, one of the least precise elements in APOGEE (but matches optical data pretty well)
-    \item S - Large abundance scatter in observations and no verification with optical data
-    \item Cr - Significant systematic artifacts at super solar metallicity \citep{griffith2021a}
-    \item Mn - Strong NLTE effects exist that are not taken into account
-    \item Co - Abundance derived from one line, causing larger abundance scatter
-    \item Ce - Abundance derived from one line. DR17 is the first time Ce abundances have been included in APOGEE data products. 
-    \item Al,  V, and Mn require large offsets to place solar metallicity stars at solar [X/Fe].
-\end{itemize}
-\ejg{Will want to condense list for paper. Add a short description of some abundance systematics that we see re \citet{jonsson2020} and \citet{griffith2021a}}.
+Among the remaining elements, we note the following concerns: weak Na spectral features, large abundances scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, strong unaccounted for NLTE effects on Mn abundances, and large abundance scatter in Co and Ce--both derived from one line.
+Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
+For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
+
+% \begin{itemize}
+% \itemsep0em
+%     \item Na - Spectral features are weak, one of the least precise elements in APOGEE (but matches optical data pretty well)
+%     \item S - Large abundance scatter in observations and no verification with optical data
+%     \item Cr - Significant systematic artifacts at super solar metallicity \citep{griffith2021a}
+%     \item Mn - Strong NLTE effects exist that are not taken into account
+%     \item Co - Abundance derived from one line, causing larger abundance scatter
+%     \item Ce - Abundance derived from one line. DR17 is the first time Ce abundances have been included in APOGEE data products. 
+%     \item Al,  V, and Mn require large offsets to place solar metallicity stars at solar [X/Fe].
+% \end{itemize}
 
 In this paper, we will explore two subsamples of APOGEE DR17 data: (1) the W22 sample, optimized to minimize statistical and systematic errors while probing a large portion of the Galactic disk, and (2) a sample with less stringent cuts, but better coverage of the low-metallicity ([Fe/H] $< -0.5$) disk.
+We discuss the model fits to the W22 sample in Section~\ref{sec:optimize} and ~\ref{sec:results_W22} and the fits the expanded sample in Section~\ref{sec:results_broad}.
 
-\subsection{The W22 Sample}
+\subsection{W22 Sample}
 
@@
 They only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}.
-In addition to these quality cute, W22 apply the following sample selection cuts:
+In addition to these quality cuts, W22 apply the following sample selection:
 \begin{itemize}
 \itemsep0em
-    \item $R=3-13$ kpc, $|Z| \leq 2$ kpc (distances from \citet{leung2019})
+    \item $R=3-13$ kpc, $|Z| \leq 2$ kpc (distances from \citealp{leung2019})
     \item $-0.75 \leq \mgh \leq 0.45$
@@
 \end{itemize}
-By selecting stars from a small range of $\logg$ and $\teff$, they eliminate the red clump stars and minimize stellar parameter-dependent abundance trends \citep[see][]{griffith2021a}.
+By selecting stars from a small range of $\logg$ and $\teff$, W22 eliminate the red clump stars \citep{vincenzo2021a} and minimize stellar parameter-dependent abundance trends \citep[see][]{griffith2021a}.
 The cuts result in a sample of 34,410 stars.
@@
 W22 present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, and Ce.
+In the analysis of each element, X, W22 drop stars with \texttt{X\_FE\_FLAG} (maximum of $\sim 560$ for Ce).
 While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
@@
 
-\ejg{W22 use X/Fe error from APOGEE and don't convert it to X/Mg....Use C/Fe error for the C+N value because the ratio is mostly C... Need error discussion here and in next section.}
+%\ejg{W22 use X/Fe error from APOGEE and don't convert it to X/Mg....Use C/Fe error for the C+N value because the ratio is mostly C... Need error discussion here and in next section.}
 
-In the analysis of each element, X, stars with \texttt{X\_FE\_FLAG} are dropped (maximum of $\sim 560$ for Ce).
+In this paper, we will analyze the same set of stars and elements as W22 (denoted ``W22 sample''), adopting the same definition of [C+N/H].
 We plot the distribution of abundances in [X/Mg] vs.
-[Mg/H] in Figure~\ref{fig:w22_xmg}.
+[Mg/H] for this sample in Figure~\ref{fig:w22_xmg}.
 All elemental abundances have zero-point offsets applied and have been de-trended for correlations with $\teff$, as in W22 (see their Table 1).
 
-\begin{figure}[htb!]
+\begin{figure*}[htb!]
     \centering
     \includegraphics[width=\textwidth]{Figures/W22_xmg.pdf}
-    \caption{W22 stellar abundance distributions. The number in the top right corner indicates the number of stars used in the analysis of that element. Elements are ordered by atomic number.}
+    \caption{Stellar abundance distributions for the W22 sample.
+The number in the top right corner indicates the number of stars used in the analysis of that element.
+Elements are ordered by atomic number.}
     \label{fig:w22_xmg}
-\end{figure}
+\end{figure*}
 
-\subsection{Our Sample}
-
-\ejg{Not sure if this should go here or after we discuss the success of the K-process model on W22 data...}
+\subsection{Expanded Sample}
 
 While the W22 sample presented above is a good first test case of \name, we are interested in the behavior of our model when applied to a wider sample of data, in particular extending the metalicity range to lower values of [Mg/H].
-To construct this sample, we apply the same quality cuts as taken by W22 (\texttt{STAR\_BAD} = 0, \texttt{NO\_ASPCAP\_RESULT} = 0, \texttt{FE\_H\_FLAG} = 0, \texttt{MG\_FE\_FLAG} = 0, and (\texttt{EXTRATARG} = 0).
+To construct this sample, we apply the same quality cuts as taken by W22 (\texttt{STAR\_BAD} = 0, \texttt{NO\_ASPCAP\_RESULT} = 0, \texttt{FE\_H\_FLAG} = 0, \texttt{MG\_FE\_FLAG} = 0, and \texttt{EXTRATARG} = 0).
 We add a cut for stars with the \texttt{ROTATION\_WARNING} flag set.
-We take the following sample selection cuts:
+We additionally take the following sample selection cuts:
 \itemsep0em
@@
     \item S/N $\geq 100$
-    \item $0 < \logg < 2.5$ dex
+    \item $\logg =  0 - 2.5$ dex
     \item $\teff = 4000-4600$ K
+    \item H $< 12$
 \end{itemize}
-We make no cuts on the Galactic location, including stars from across the Galactic disk and halo, and make no cuts on the [Mg/H] values of our sample.
-The wider $\logg$ ranges expand the sample of giants.
-We select stars in the same small $\teff$ range as W22 to exclude the red clump \citep{vincenzo2021} and cool stars that show abundance artifacts \citep{jonsson2020}.
+We make no cuts on the [Mg/H] abundances.
+The wider $\logg$ range expands the sample of giants, though we select stars in the same small $\teff$ range as W22 to exclude the red clump \citep{vincenzo2021a} and cool stars that show abundance artifacts \citep{jonsson2020}.
+The $H$-band magnitude cut acts as a proxy for a distance cut \ejg{Add how many stars it excludes.}
 Our final sample includes 51,386 stars and extends to [Mg/H]=-2.2.
@@
 
-\ejg{Plus a magnitude cut as a proxy for distance? Right now I have H < 12, but I don't think that the cut impacts the global trends much...}
-
-\begin{figure}[htb!]
+\begin{figure*}[htb!]
     \centering
     \includegraphics[width=\textwidth]{Figures/xmg.pdf}
-    \caption{Stellar abundance distributions for our wider stellar sample.
+    \caption{Stellar abundance distributions for our expanded stellar sample.
 The number in the top right corner indicates the number of stars used in the analysis of that element.
-Elements are ordered by atomic number.}
-    \label{fig:w22_xmg}
-\end{figure}
+Elements are ordered by atomic number.
+No zero-point offsets have been applied.}
+    \label{fig:exp_xmg}
+\end{figure*}
 
-The expansion of the data sample does introduce abundance systematics that the W22 selection sought to exclude.
+We plot the distribution of abundances in [X/Mg] vs.
+[Mg/H] for the expanded sample in Figure~\ref{fig:exp_xmg}.
+We do not apply zero-point offsets or temperature calibrations, as done in the W22 sample.
+
+The expansion of the data sample does introduce abundance systematics that the W22 cuts sought to exclude.
 As discussed in \citet{jonsson2020} and \citet{griffith2021a}, APGOEE DR16 and DR17 suffer from poorly understood abundance artifacts, such as a ``finger'' in [$\alpha$/M] and low-[X/Fe] banding in elements such as Al and Ni.
-In our expanded data set, we observe potential abundance artifacts in Al, K, V, and Cr.
-\ejg{Add more here.
-Stricter temperature cut helped to remove the artifacts...}
+In our expanded data set, we observe potential abundance artifacts in Al, K, V, and Cr, though the strict temperature cuts help to minimize these effects.
 
-\ejg{Should check the spatial distribution of the final sample. Need to decide if we will also apply zero point offsets}
+\section{The K-Proccess Model}\label{sec:model}
 
-\ejg{Also need to add discussion that almost all stars below [Mg/H] of -0.75 appear chemically accreted...}
+As in W22 and G22, we propose that all stellar abundances can be described by the sum of $K$ nucleosynthetic process vectors and amplitudes.
+Each element has unique, metallicity-dependent process vectors that are universal for the stellar sample, while each star has unique process amplitudes.
+To begin, we consider the case for $K=2$ with a CCSN and SNIa process---the nucleosynthetic sources that dominate the production of the APOGEE elements \citep[e.g.,][]{andrews2017} such that
 
-\section{Methods and Models}\label{sec:model}
-
-We model each star as the sum of a CCSN and SNIa process vector (constant for all elements) and CCSN/SNIa amplitude such that
-
-\begin{equation}
+\begin{equation} \label{eq:m_ij}
     m_{ij} = \log_{10}(A_i^{\rm CC} \vec{q}_{{\rm CC}, j}^{\,Z} + A_i^{\rm Ia} \vec{q}_{{\rm Ia}, j}^{\,Z}) 
@@
 
-where the observed value of $\xh$ can be described as the model plus observational noise and/or contributions from an additional non-CCSN/SNIa process:
+where there are $i$ stars and $j$ elements described by process amplitudes $A_i^{\rm CC}$ and $A_i^{\rm Ia}$ and process vectors $\vec{q}_{{\rm CC}, j}^{\,Z}$ and $\vec{q}_{{\rm Ia}, j}^{\,Z}$.
+The observed value of $\xh$ can be described as the model plus observational noise and/or contributions from an additional non-CCSN nor SNIa processes:
 
-\begin{equation}
+\begin{equation} \label{eq:xh}
     \xh_{ij} = m_{ij} + \text{noise}.
@@
 
-We fit this model to the data with a chi-squared ($\chi^2$) minimization such that
+While such a model could be fit to a set stellar abundances, there are many degenerate solutions when there are no constraints on the model parameters.
+To better define our model and to collapse such degeneracies, we put forth a set a set of assumptions in the following section.
 
+\subsection{Assumptions}\label{subsec:assumptions}
+
+In the K-Process model, \name{}, we make the following assumptions:
+
+\paragraph{1. Two processes}
+The majority of $\alpha$, light odd-Z, and Fe-peak elements are dominantly produced by two sources: CCSN and SNIa.
+This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful models (e.g., G22, \citealp{ting2022}, W22).
+However, the assumption fails to allow for enrichment from other known sources, such as merging neutron stars, unique classes of supernoave, and AGB stars, the latter of which significantly contribute to C+N and Ce production.
+
+\paragraph{2. Linearity}
+At every metallicity, the abundances of a star can be expressed as a linear combination of two processes.
+These processes themselves might depend on metallicity, but a linear sum is sufficient to explain all element abundances.
+Because of dependences of yields on detailed abundances, and because different stars can get to their metallicities by different histories, this assumption must be slightly wrong in detail.
+
+\paragraph{3. Non-negativity}
+All process amplitudes for all elements are non-negative (elements considered here are only produced, not ever destroyed, by the two processes),
+and all stars are made of a sum of the two non-negative processes.
+This makes the model similar to a non-negative matrix factorization (\citealt{nnmf} \ejg{CITATION}). This assumption is not enforced in G22 and W22.
+
+\paragraph{4. Mg is a pure CCSN}
+All magnesium is produced in the CCSN process and none in the SNIa process. This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017}.
+This breaks a rotational symmetry in the process space and makes the processes interpretable in terms of SN types.
+
+\paragraph{5. Metallicity dependence}
+The fact that all Mg is produced in the CCSN process is an assumption that is independent of metallicity.
+All other process vectors are permitted to float as a function of metallicity.
+The only exceptions are the Mg level in the CCSN process and the Fe level in the SNIa process, but these constraints are just model normalizations; they don't restrict the overall model freedom, which is about abundance ratios.
+\ejg{Check that this is right.
+Especially for Fe.}
+
+\bigskip
+The above assumptions  mirror the assumptions of prior work (G22, W22) but are weaker.
+In particular, they don't assume anything about the relationships between the processes and the morphologies of observed element-abundance ratio diagrams.
+In addition to the above assumptions, which are about nucleosynthesis, there are assumptions about the data:
+
+\paragraph{6. APOGEE abundances and uncertainties}
+We assume that the APOGEE abundances and uncertainties can be used for this project.
+This is not the same as assuming that they are correct, but rather we are assuming that it is possible and useful to build an interpretable 2-process model to explain them.
+We describe the potential data systemtics in Section~\ref{sec:data}.
+The APOGEE errors are likely underestimated for many more challenging elements.
+
+\paragraph{7. Likelihood function}
+\ejg{Hogg to add}
+
+\subsection{Model Constraints, Regularizations, and Implementation}\label{subsec:regularizations}
+
+Some of the assumptions listed above directly translate to model constraints and regularization.
+Assumptions 1 and 2 form the basis of the model as described by Equation~\ref{eq:m_ij}.
+Assumption 3 is enforced by requiring that the process vectors and amplitudes are always greater than or equal to zero:
+\begin{equation} \label{eq:constraint_zero}
+    \vec{q}_{{\rm CC}, j}^{\,Z}, \, \vec{q}_{{\rm Ia}, j}^{\,Z} \geq 0 \quad \forall \; j
+\text{   and   }
+    A_i^{\rm CC}, \, A_i^{\rm Ia} \geq 0 \quad \forall \; i.
+\end{equation}
+
+To enforce assumptions 4 and 5, we initialize the model with specific values of $\vec{q}_{{\rm CC}}$ and $\vec{q}_{{\rm Ia}}$ and place regularizations ($\lambda$) on these constraints so that the model disfavors an alternative solution.
+In the initial model, we strongly require that
+\begin{equation}\label{eq:qcc_solar}
+    \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1, \quad \vec{q}_{{\rm Ia, Mg}}^{\,Z_{\odot}} = 0, \quad 
+    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.5, \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.5
+\end{equation}
+at solar metallicity and
+
+\begin{equation}\label{eq:qcc_z}
+    \vec{q}_{{\rm CC, Mg}}^{\,Z} = \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}}, \quad 
+    \vec{q}_{{\rm CC, Fe}}^{\,Z} = \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}},  \quad 
+    \vec{q}_{{\rm Ia, Fe}}^{\,Z} = \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}}
+\end{equation}
+at all other metallicities.
+\ejg{Do we want to list regularization strengths? What is the difference between lambda a and lambda b in the notebook?} 
+While the CCSN process constraint (that Mg is a pure CCSN element) is grounded in nucleosynthetic theory, there is no equivalent nucleosynthetic fact to constrain the SNIa process.
+We begin by initializing our model with the assumption that $\vec{q}_{{\rm CC, Fe}} = 0.5$, as in G22 and W22.
+This assumption places a pure CCSN star on the low metallicity [Mg/Fe] plateau near 0.3 dex, in agreement with APOGEE observations, but in contention with recent results from \citet{conroy2022} which places the [Mg/Fe] plateau near 0.6 dex.
+The flexibility of \name allows us to fit the model with different values of $\vec{q}_{{\rm CC, Fe}}$, allow for metallicity dependence in Fe CCSN and SNIa yields, and relax the regularization strengths in our initialization to see if the model prefers a different process vector.
+We explore different choices of $\vec{q}_{{\rm CC, Fe}}$ and regularization strengths in Section~\ref{subsec:fcc}.
+
+We initialize the model according to Equations~\ref{eq:qcc_solar} and~\ref{eq:qcc_z}, setting all other $\vec{q}_{{\rm CC,}j}$ = $\vec{q}_{{\rm Ia,}j} = 0.5$ and all $A_i^{\rm CC} = A_j^{\rm Ia} = 0$.
+\ejg{Is this right?}
+
+We then fit the $K$-process model to the W22 sample by minimizing the a chi-squared ($\chi^2$) with Gauss-Newton nonlinear least-squares solver in \texttt{jaxopt} where
 \begin{equation}
-    \chi^2 = \sum_{i=1}^{N} (\xh_{ij} - m_{ij})^{\rm T} c_j^{-1} (\xh_{ij} - m_{ij}) + \text{regularization}~,
+    \chi^2 = \sum_{i=1}^{N} (\xh_{ij} - m_{ij})^{\rm T} c_j^{-1} (\xh_{ij} - m_{ij}) + \lambda~,
 \end{equation}
-where $c_j^{-1}$ is a matrix of the inverse variance squared,
+and $c_j^{-1}$ is a matrix of the inverse variance squared,
 \begin{equation}
@@
 0 & 0 & ... 
-\end{bmatrix}
+\end{bmatrix} .
 \end{equation}
-$N$ stars, such that $1 \leq i \leq N$, and ``regularization'' stands in for some additional penalization terms that we will describe below.
+We fit the model to $N$ stars, such that $1 \leq i \leq N$, and $M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, CN, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, Ce} \}$, by iteratively optimizing the process vectors (dubbed the q-step) and the process amplitudes (dubbed the A-step).
+\ejg{Add bit about how we determine how many times to repeat the iterations.}
 
-$M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, CN, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, Ce} \}$, the elements in APGOEE DR17 and used in \citet{weinberg2022}.
+\section{Optimization of \name} \label{sec:optimize}
 
-\subsection{Assumptions}\label{subsec:assumptions}
+\section{Comparing the W22 Two-Process Model and \name} \label{sec:results_W22}
 
-Some of the assumptions that go into the two-process model \name{} are the following:
+\begin{itemize}
+    \item Differences/similarities between the W22 fits and our fits. What do the differences mean
+    \item Dependence of results on assumptions on assumptions such as the Fe yield/plateau value. Contrast the results for different assumptions and show the uncertainty in fcc 
+\end{itemize}
 
-\paragraph{Two processes}
-HOGG whatever.
+\subsection{Dependence of $\fcc$ on Assumptions} \label{subsec:fcc}
 
-\paragraph{Linearity}
-At every metallicity, the abundances of a star can be expressed as a linear combination of two processes.
-These processes themselves might depend on metallicity, but a linear sum is sufficient to explain all element abundances.
-Because of dependences of yields on detailed abundances, and because different stars can get to their metallicities by different histories, this assumption must be slightly wrong in detail.
+\section{Application to a Broader Data Sample} \label{sec:results_broad}
 
-\paragraph{Non-negativity}
-All process amplitudes for all elements are non-negative (elements heavier than XXX are only produced, not ever destroyed, by the two processes),
-and all stars are made of a non-negative sum of the two non-negative processes.
-This makes the model similar to a non-negative matrix factorization (\citealt{nnmf}).
+\begin{itemize}
+    \item Look at residuals from the K=2 fit, are there elements with correlated residuals? Are they the same as in W22? 
+    \item show results for adding 3rd and 4th process to the data
+\end{itemize}
 
-\paragraph{Magnesium is a core-collapse element only}
-All magnesium is produced in the core-collapse (CC) process, and none in the type-Ia (Ia) process.
-This breaks (something like) a rotational symmetry in the process space, and makes the processes interpretable in terms of supernova types.
+\section{Summary}\label{sec:summary}
 
-\paragraph{Metallicity dependence}
-The fact that all magnesium is produced in the CC process is an assumption that is independent of metallicity.
-All other process vectors are permitted to float as a function of metallicity.
-The only exceptions are the magnesium level in the CC process and the iron level in the Ia process, but these constraints are just model normalizations; they don't restrict the overall model freedom, which is about abundance ratios.
-
-\paragraph{\textsl{APOGEE} abundances}
-We are assuming that the \textsl{APOGEE} abundances can be used for this project.
-This is not quite the same as assuming that they are correct.
-It is more like assuming that it is possible and useful to build an interpretable 2-process model to explain them.
-EMILY: WE NEED A DATA SECTION that explains how we put together the data and which data we used.
-
-\bigskip
-These assumptions (above) mirror the assumptions of prior work (\citealt{griffith2022}; \citealt{weinberg2022}) but they are weaker.
-In particular, they don't assume anything about the relationships between the processes and the morphologies of observed element-abundance ratio diagrams.
-In addition to the above assumptions, which are about nucleosynthesis, there are assumptions about the data:
-
-\paragraph{Measurement uncertainties}
-HOGG
-
-\paragraph{Likelihood function}
-HOGG
-
-\subsection{Constraints and Regularizations}\label{subsec:regularizations}
-
-Some of the assumptions in our model directly translate to constraints and regularization.
-
-We always enforce that the process vectors and amplitudes are greater than zero:
-\begin{equation}
-    \vec{q}_{{\rm CC}, j}^{\,Z}, \, \vec{q}_{{\rm Ia}, j}^{\,Z} \geq 0 \quad \forall \; j
-\end{equation}
-
-\begin{equation}
-    A_i^{\rm CC}, \, A_i^{\rm Ia} \geq 0 \quad \forall \; i.
-\end{equation}
-
-We will start with the constraints from \citet{weinberg2022} as well:
-
-\begin{equation}
-    \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1 \quad \vec{q}_{{\rm Ia, Mg}}^{\,Z_{\odot}} = 0 \quad 
-    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.5 \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.5 
-\end{equation}
-
-\begin{equation}
-    \vec{q}_{{\rm CC, Mg}}^{\,Z} = \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} \quad 
-    \vec{q}_{{\rm CC, Fe}}^{\,Z} = \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}}  \quad 
-    \vec{q}_{{\rm Ia, Fe}}^{\,Z} = \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} 
-\end{equation}
-
-\begin{equation}
-    \vec{q}_{{\rm CC}, j}^{\,Z_{\odot}} + \vec{q}_{{\rm Ia}, j}^{\,Z_{\odot}} = 1 \quad \forall \; j
-\end{equation}
-
-\section{Experiments and Results}
-
-\section{Discussion}
+Notes
 
@@
     \item Casual inferences - which abundances are caused by the Mg abundance and which are not (statistician perspective)
-
+    \item Implications of differences at high metallicity
+    \item Observational motivation for additional processes, what elements are critical for spectral surveys to observe
+    \item Why this version of the 2 process model is more flexible than W22
 \end{itemize}
-
-\section{Summary}
 
@@
 E.J.G. is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.
+CU Boulder Research Computing services and staff
 

### 2023-03-29 Paper/main.tex
Updated text on fiducial model

@@
 \newcommand{\mgfe}[0]{[{\rm Mg/Fe}]} 
-\newcommand{\Acc}{A_{\rm cc}}
-\newcommand{\AIa}{A_{\rm Ia}} 
-\newcommand{\RIa}{R_{\rm Ia}^X}
-\newcommand{\aIa}{\alpha_{\rm Ia}}
-\newcommand{\acc}{\alpha_{\rm cc}}
 \newcommand{\afe}[0]{[\alpha/{\rm Fe}]}
@@
 \newcommand{\feh}[0]{[{\rm Fe/H}]} 
-\newcommand{\pIa}{p_{\rm Ia}^{\rm X}}
-\newcommand{\pcc}{p_{\rm cc}^{\rm X}}
-\newcommand{\fcc}{f_{\rm cc}}
 \newcommand{\xfe}{[{\rm X}/{\rm Fe}]} 
-\newcommand{\pIasun}{p_{\rm Ia, \odot}^{\rm X}}
-\newcommand{\pccsun}{p_{\rm cc, \odot}^{\rm X}}
+\newcommand{\xh}{[{\rm X}/{\rm H}]}
+
 \newcommand{\logg}{\log(g)}
@@
 \newcommand{\MZAMS}{M_{\rm ZAMS}}
-\newcommand{\Msun}{M_{\odot}}
-\newcommand{\qIax}{q_{\rm Ia}^{\rm X}}
-\newcommand{\qccx}{q_{\rm cc}^{\rm X}}
-\newcommand{\qagbx}{q_{\rm AGB}^{\rm X}}
-\newcommand{\qIa}{q_{\rm Ia}}
-\newcommand{\qcc}{q_{\rm cc}}
-\newcommand{\qagb}{q_{\rm AGB}}
-\newcommand{\Aagb}{A_{\rm AGB}}
-\newcommand{\eumg}{[{\rm Eu}/{\rm Mg}]} 
-\newcommand{\mgmn}{[{\rm Mg}/{\rm Mn}]} 
-\newcommand{\alfe}{[{\rm Al}/{\rm Fe}]} 
-\newcommand{\omg}{[{\rm O}/{\rm Mg}]} 
-\newcommand{\xo}{[{\rm X}/{\rm O}]} 
-\newcommand{\xh}{[{\rm X}/{\rm H}]} 
-\newcommand{\angstrom}{\textup{\AA}}
+
+\newcommand{\qcc}{\vec{q}_{{\rm CC,}j}^{Z}}
+\newcommand{\qccFe}{\vec{q}_{{\rm CC, Fe}}^{Z}}
+\newcommand{\dqccFe}{d\vec{q}_{{\rm CC, Fe}}^{Z}/dZ}
+\newcommand{\qIa}{\vec{q}_{{\rm Ia,}j}^{Z}}
+\newcommand{\qIaFe}{\vec{q}_{{\rm Ia,Fe}}^{Z}}
+\newcommand{\Acc}{A^{\rm CC}_{i}}
+\newcommand{\AIa}{A^{\rm Ia}_{i}}
+\newcommand{\fcc}{f_{\rm CC}}
+
 \newcommand{\ejg}[1]{\textcolor{red}{EJG: #1}}
@@
 \begin{abstract}\noindent % trust Hogg
+
+\ejg{Need to update abstract}
+
 Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
@@
 
-\section{Data Samples}\label{sec:data}
-
-In this paper, we employ stellar abundances from APOGEE DR17 \citep{abdurrouf2022}, part of SDSS-IV \citep{majewski2017}.
-The APOGEE survey obtains high-resolution ($R\sim22,500$) near-infrared (IR) observations \citep{wilson2019} for stars in the Galactic disk, halo, bulge, and nearby satellites/streams.
-Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile.
-Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and abundances are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}.
-See \citet[][DR16]{jonsson2020} and Holtzman et al.
-(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017} and \citet{santana2021} for a discussion of survey targeting.
-
-APOGEE DR17 reports stellar parameters, including $\teff$ and $\logg$, as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, \ion{Ti}{1}, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
-Among these elements and ions, some are measured more precisely than others.
-We exclude Ti from our analysis as there are large differences between the abundances derived from the \ion{Ti}{1} and \ion{Ti}{2} lines \citep{jonsson2020}.
-We also exclude P, as the P abundances are measured from a few very weak spectra features, and the abundance distribution displays strong artifacts \citep{jonsson2020}.
-Among the remaining elements, we note the following concerns: weak Na spectral features, large abundances scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, strong unaccounted for NLTE effects on Mn abundances, and large abundance scatter in Co and Ce--both derived from one line.
-Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
-For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
-
-% \begin{itemize}
-% \itemsep0em
-%     \item Na - Spectral features are weak, one of the least precise elements in APOGEE (but matches optical data pretty well)
-%     \item S - Large abundance scatter in observations and no verification with optical data
-%     \item Cr - Significant systematic artifacts at super solar metallicity \citep{griffith2021a}
-%     \item Mn - Strong NLTE effects exist that are not taken into account
-%     \item Co - Abundance derived from one line, causing larger abundance scatter
-%     \item Ce - Abundance derived from one line. DR17 is the first time Ce abundances have been included in APOGEE data products. 
-%     \item Al,  V, and Mn require large offsets to place solar metallicity stars at solar [X/Fe].
-% \end{itemize}
-
-In this paper, we will explore two subsamples of APOGEE DR17 data: (1) the W22 sample, optimized to minimize statistical and systematic errors while probing a large portion of the Galactic disk, and (2) a sample with less stringent cuts, but better coverage of the low-metallicity ([Fe/H] $< -0.5$) disk.
-We discuss the model fits to the W22 sample in Section~\ref{sec:optimize} and ~\ref{sec:results_W22} and the fits the expanded sample in Section~\ref{sec:results_broad}.
-
-\subsection{W22 Sample}
-
-W22 select a subset of APOGEE DR17 stars with the goal of minimizing statistical errors from poor observations and systematic errors from abundance trends with $\teff$ and/or $\logg$ while preserving a sufficient number of stars to conduct a meaningful statistical analysis across the Galactic disk.
-To remove poor quality data points, W22 require ASPCAP flags \texttt{STAR\_BAD} \texttt{NO\_ASPCAP\_RESULT} equal zero and remove all stars with \texttt{FE\_H\_FLAG} or \texttt{MG\_FE\_FLAG} set.
-They only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}.
-In addition to these quality cuts, W22 apply the following sample selection:
-\begin{itemize}
-\itemsep0em
-    \item $R=3-13$ kpc, $|Z| \leq 2$ kpc (distances from \citealp{leung2019})
-    \item $-0.75 \leq \mgh \leq 0.45$
-    \item S/N $\geq 200$ for $\mgh > -0.5$ and S/N $\geq 100$ for $\mgh < -0.5$
-    \item $\logg = 1-2.5$ dex
-    \item $\teff = 4000-4600$ K
-\end{itemize}
-By selecting stars from a small range of $\logg$ and $\teff$, W22 eliminate the red clump stars \citep{vincenzo2021a} and minimize stellar parameter-dependent abundance trends \citep[see][]{griffith2021a}.
-The cuts result in a sample of 34,410 stars.
-
-W22 present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, and Ce.
-In the analysis of each element, X, W22 drop stars with \texttt{X\_FE\_FLAG} (maximum of $\sim 560$ for Ce).
-While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
-W22 consider C+N as an element in their analysis, taking [(C+N)/H] to be
-\begin{equation}
-    [\text{C+N}/\text{H}] = \log_{10}(10^{\text{[C/H]}+8.39} + 10^{\text{[N/H]}+7.78}) - \log_{10}(10^{8.39} + 10^{7.78})
-\end{equation}
-using logarithmic solar abundances for C (8.39) and N (7.78) from \citet{grevesse2007}.
-
-%\ejg{W22 use X/Fe error from APOGEE and don't convert it to X/Mg....Use C/Fe error for the C+N value because the ratio is mostly C... Need error discussion here and in next section.}
-
-In this paper, we will analyze the same set of stars and elements as W22 (denoted ``W22 sample''), adopting the same definition of [C+N/H].
-We plot the distribution of abundances in [X/Mg] vs.
-[Mg/H] for this sample in Figure~\ref{fig:w22_xmg}.
-All elemental abundances have zero-point offsets applied and have been de-trended for correlations with $\teff$, as in W22 (see their Table 1).
-
-\begin{figure*}[htb!]
-    \centering
-    \includegraphics[width=\textwidth]{Figures/W22_xmg.pdf}
-    \caption{Stellar abundance distributions for the W22 sample.
-The number in the top right corner indicates the number of stars used in the analysis of that element.
-Elements are ordered by atomic number.}
-    \label{fig:w22_xmg}
-\end{figure*}
-
-\subsection{Expanded Sample}
-
-While the W22 sample presented above is a good first test case of \name, we are interested in the behavior of our model when applied to a wider sample of data, in particular extending the metalicity range to lower values of [Mg/H].
-To construct this sample, we apply the same quality cuts as taken by W22 (\texttt{STAR\_BAD} = 0, \texttt{NO\_ASPCAP\_RESULT} = 0, \texttt{FE\_H\_FLAG} = 0, \texttt{MG\_FE\_FLAG} = 0, and \texttt{EXTRATARG} = 0).
-We add a cut for stars with the \texttt{ROTATION\_WARNING} flag set.
-We additionally take the following sample selection cuts:
-\itemsep0em
-\begin{itemize}
-    \item S/N $\geq 100$
-    \item $\logg =  0 - 2.5$ dex
-    \item $\teff = 4000-4600$ K
-    \item H $< 12$
-\end{itemize}
-We make no cuts on the [Mg/H] abundances.
-The wider $\logg$ range expands the sample of giants, though we select stars in the same small $\teff$ range as W22 to exclude the red clump \citep{vincenzo2021a} and cool stars that show abundance artifacts \citep{jonsson2020}.
-The $H$-band magnitude cut acts as a proxy for a distance cut \ejg{Add how many stars it excludes.}
-Our final sample includes 51,386 stars and extends to [Mg/H]=-2.2.
-As in W22, we only analyze [X/Mg] abundances for stars where the [X/Fe] value is unflagged.
-This has a minimal effect for most elements but reduces the sample size to 49,851 for Ce.
-
-\begin{figure*}[htb!]
-    \centering
-    \includegraphics[width=\textwidth]{Figures/xmg.pdf}
-    \caption{Stellar abundance distributions for our expanded stellar sample.
-The number in the top right corner indicates the number of stars used in the analysis of that element.
-Elements are ordered by atomic number.
-No zero-point offsets have been applied.}
-    \label{fig:exp_xmg}
-\end{figure*}
-
-We plot the distribution of abundances in [X/Mg] vs.
-[Mg/H] for the expanded sample in Figure~\ref{fig:exp_xmg}.
-We do not apply zero-point offsets or temperature calibrations, as done in the W22 sample.
-
-The expansion of the data sample does introduce abundance systematics that the W22 cuts sought to exclude.
-As discussed in \citet{jonsson2020} and \citet{griffith2021a}, APGOEE DR16 and DR17 suffer from poorly understood abundance artifacts, such as a ``finger'' in [$\alpha$/M] and low-[X/Fe] banding in elements such as Al and Ni.
-In our expanded data set, we observe potential abundance artifacts in Al, K, V, and Cr, though the strict temperature cuts help to minimize these effects.
-
-\section{The K-Proccess Model}\label{sec:model}
+\section{The K-Process Model}\label{sec:model}
 
@@
 where there are $i$ stars and $j$ elements described by process amplitudes $A_i^{\rm CC}$ and $A_i^{\rm Ia}$ and process vectors $\vec{q}_{{\rm CC}, j}^{\,Z}$ and $\vec{q}_{{\rm Ia}, j}^{\,Z}$.
-The observed value of $\xh$ can be described as the model plus observational noise and/or contributions from an additional non-CCSN nor SNIa processes:
+The observed value of [X/H] can be described as the model plus observational noise and/or contributions from an additional non-CCSN nor SNIa processes:
 
@@
 
-While such a model could be fit to a set stellar abundances, there are many degenerate solutions when there are no constraints on the model parameters.
-To better define our model and to collapse such degeneracies, we put forth a set a set of assumptions in the following section.
+While such a model could be fit to a set of stellar abundances, there are many degenerate solutions when there are no constraints on the model parameters.
+To better define our model and to collapse such degeneracies, we put forth a set of assumptions in the following section.
 
@@
 \paragraph{1. Two processes}
-The majority of $\alpha$, light odd-Z, and Fe-peak elements are dominantly produced by two sources: CCSN and SNIa.
+The majority of $\alpha$, light odd-Z, and Fe-peak elements are dominantly produced by two sources: prompt CCSN and delayed SNIa.
 This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful models (e.g., G22, \citealp{ting2022}, W22).
-However, the assumption fails to allow for enrichment from other known sources, such as merging neutron stars, unique classes of supernoave, and AGB stars, the latter of which significantly contribute to C+N and Ce production.
+However, the assumption fails to allow for enrichment from other known sources, such as merging neutron stars, unique classes of supernoave, and AGB stars, the latter of which contribute to C+N and Ce production.
 
@@
 and all stars are made of a sum of the two non-negative processes.
-This makes the model similar to a non-negative matrix factorization (\citealt{nnmf} \ejg{CITATION}). This assumption is not enforced in G22 and W22.
+This makes the model similar to a non-negative matrix factorization (\citealt{nnmf} \ejg{CITATION}).
+This assumption is not enforced in G22 and W22 where both process vectors and amplitudes can be negative.
 
-\paragraph{4. Mg is a pure CCSN}
-All magnesium is produced in the CCSN process and none in the SNIa process. This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017}.
-This breaks a rotational symmetry in the process space and makes the processes interpretable in terms of SN types.
+\paragraph{4. Mg is a pure CCSN element}
+All magnesium is produced in the CCSN process and none in the SNIa process, substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} This breaks a rotational symmetry in the process space and makes the processes interpretable in terms of SN types.
 
@@
 The fact that all Mg is produced in the CCSN process is an assumption that is independent of metallicity.
-All other process vectors are permitted to float as a function of metallicity.
-The only exceptions are the Mg level in the CCSN process and the Fe level in the SNIa process, but these constraints are just model normalizations; they don't restrict the overall model freedom, which is about abundance ratios.
-\ejg{Check that this is right.
-Especially for Fe.}
+All other process vectors, except Fe, are permitted to float as a function of metallicity.
+We further fix the Fe CCSN and SNIa processes, though vary the Fe assumptions as discussed in Section~\ref{subsec:qcc_fe}.
+These constraints are just model normalizations; they don't restrict the overall model freedom.
 
@@
 We assume that the APOGEE abundances and uncertainties can be used for this project.
-This is not the same as assuming that they are correct, but rather we are assuming that it is possible and useful to build an interpretable 2-process model to explain them.
-We describe the potential data systemtics in Section~\ref{sec:data}.
-The APOGEE errors are likely underestimated for many more challenging elements.
+This is not the same as assuming that they are correct, but rather we are assuming that it is possible and useful to build an interpretable Few-Process model to explain them.
+We describe the potential data systematics in Section~\ref{sec:data}.
+The APOGEE errors are likely underestimated for many elements.
 
@@
 To enforce assumptions 4 and 5, we initialize the model with specific values of $\vec{q}_{{\rm CC}}$ and $\vec{q}_{{\rm Ia}}$ and place regularizations ($\lambda$) on these constraints so that the model disfavors an alternative solution.
-In the initial model, we strongly require that
+In the fiducial model, we strongly require that
 \begin{equation}\label{eq:qcc_solar}
     \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1, \quad \vec{q}_{{\rm Ia, Mg}}^{\,Z_{\odot}} = 0, \quad 
-    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.5, \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.5
+    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.4, \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.6
 \end{equation}
@@
 While the CCSN process constraint (that Mg is a pure CCSN element) is grounded in nucleosynthetic theory, there is no equivalent nucleosynthetic fact to constrain the SNIa process.
-We begin by initializing our model with the assumption that $\vec{q}_{{\rm CC, Fe}} = 0.5$, as in G22 and W22.
-This assumption places a pure CCSN star on the low metallicity [Mg/Fe] plateau near 0.3 dex, in agreement with APOGEE observations, but in contention with recent results from \citet{conroy2022} which places the [Mg/Fe] plateau near 0.6 dex.
-The flexibility of \name allows us to fit the model with different values of $\vec{q}_{{\rm CC, Fe}}$, allow for metallicity dependence in Fe CCSN and SNIa yields, and relax the regularization strengths in our initialization to see if the model prefers a different process vector.
-We explore different choices of $\vec{q}_{{\rm CC, Fe}}$ and regularization strengths in Section~\ref{subsec:fcc}.
+We begin by initializing our model with the assumption that $\vec{q}_{{\rm CC, Fe}} = 0.4$.
+This assumption places a pure CCSN star on the low metallicity [Mg/Fe] plateau near 0.4 dex, in agreement with APOGEE observations, but in contention with recent results from \citet{conroy2022} which places the [Mg/Fe] plateau near 0.6 dex.
+The flexibility of the Few-Process model allows us to fit the model with different values of $\vec{q}_{{\rm CC, Fe}}$, allow for metallicity dependence in Fe CCSN and SNIa yields, and relax the regularization strengths in our initialization to see if the model prefers a different process vector.
+We explore different choices of $\vec{q}_{{\rm CC, Fe}}$ and regularization strengths in Section~\ref{subsec:qcc_fe}.
 
 We initialize the model according to Equations~\ref{eq:qcc_solar} and~\ref{eq:qcc_z}, setting all other $\vec{q}_{{\rm CC,}j}$ = $\vec{q}_{{\rm Ia,}j} = 0.5$ and all $A_i^{\rm CC} = A_j^{\rm Ia} = 0$.
-\ejg{Is this right?}
-
+\ejg{Is this right?}.
 We then fit the $K$-process model to the W22 sample by minimizing the a chi-squared ($\chi^2$) with Gauss-Newton nonlinear least-squares solver in \texttt{jaxopt} where
@@
 \end{equation}
-We fit the model to $N$ stars, such that $1 \leq i \leq N$, and $M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, CN, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, Ce} \}$, by iteratively optimizing the process vectors (dubbed the q-step) and the process amplitudes (dubbed the A-step).
-\ejg{Add bit about how we determine how many times to repeat the iterations.}
+We fit the model to $N$ stars, such that $1 \leq i \leq N$, and $M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, Mn, Co, Ce} \}$, by iteratively optimizing the process vectors (dubbed the q-step) and the process amplitudes (dubbed the A-step).
+In the initialization, we use only Mg and Fe in the A-step.
+We then repeat the A-step and q-step with all elements for all stars 48 times, only updating the best-fit process parameters when the objective function improves.
+We find few differences in the model when we decrease the number of iterations to 32, indicating that the model quickly finds a good solution.
 
-\section{Optimization of \name} \label{sec:optimize}
+In the few-process model, all stars and all unflagged abundances contribute to the optimization of $\qcc$, $\qIa$, $\Acc$, and $\AIa$.
+Outlier stars with large abundance errors will contribute minimally to the $\chi^2$ minimization, but outlier stars with truly unique abundances (and small errors) will pull the model away from the values favored by the larger population.
+To mitigate this effect, we artificially inflate the errors on abundances with values of $\chi^2$ such that
+\begin{equation}\label{eq:inflate_ivar}
+    \frac{1}{\sigma^2} = \frac{Q^2/\sigma_{\rm obs}^2}{Q^2 + (\xh_{\rm obs} - \xh_{\rm pred})^2 /\sigma_{\rm obs}^2 },    
+\end{equation}
+where $Q$ is the softening parameter. We inflate the errors after the initialization (with $Q=7$) and after the 16th and 32nd iteration (with $Q=5$).
 
-\section{Comparing the W22 Two-Process Model and \name} \label{sec:results_W22}
+\ejg{DH should check all of this and add some more statistics, I'm sure I have explained something incorrectly.}
 
+\section{Data}\label{sec:data}
+
+In this paper, we employ stellar abundances from APOGEE DR17 \citep{abdurrouf2022}, part of the SDSS-IV \citep{majewski2017}.
+The APOGEE survey obtains high-resolution ($R\sim22,500$) near-infrared (IR) observations \citep{wilson2019} for stars in the Galactic disk, halo, bulge, and nearby satellites/streams.
+Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile.
+Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and abundances are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}.
+See \citet[][DR16]{jonsson2020} and Holtzman et al.
+(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017} and \citet{santana2021} for a discussion of survey targeting.
+
+APOGEE DR17 reports stellar parameters, including $\teff$ and $\logg$, as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, \ion{Ti}{1}, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
+Among these elements and ions, some are measured more precisely than others.
+We exclude Ti from our analysis as there are large differences between the abundances derived from the \ion{Ti}{1} and \ion{Ti}{2} lines \citep{jonsson2020}.
+We also exclude P and V, as the P abundances are measured from a few very weak spectra features and V abundances are one of the least precise and least accurate labels \citep{jonsson2020}, Both P and V display strong abundance artifacts and large scatter.
+Among the remaining elements, we note the following concerns: weak Na spectral features, large abundances scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, strong unaccounted for NLTE effects on Mn abundances, and large abundance scatter in Co and Ce--both derived from one line.
+Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
+For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
+
+In this paper, we will explore two subsamples of APOGEE DR17 data: (1) a model training set, similar to the W22 sample, that is optimized to minimize statistical and systematic errors while probing a large portion of the Galactic disk, and (2) a testing sample comprised of all unflagged DR17 giant stars above [Fe/H] of $-0.75$.
+We discuss the training sample in depth in Sections~\ref{sec:fidutial} and ~\ref{sec:variations} and the fits to the testing sample in Section~\ref{sec:results_broad}.
+
+\subsection{Training Sample}\label{subsec:train}
+
+For our training sample, we select a subset of APOGEE DR17 stars with the goal of minimizing statistical errors from poor observations and systematic errors from abundance trends with $\teff$ and/or $\logg$ while preserving a sufficient number of stars to conduct a meaningful statistical analysis across the Galactic disk.
+To remove poor quality data points, we require ASPCAP flags \texttt{STAR\_BAD} \texttt{NO\_ASPCAP\_RESULT} equal zero.
+We only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}.
+In addition to these quality cuts, we apply the following sample selection:
 \begin{itemize}
-    \item Differences/similarities between the W22 fits and our fits. What do the differences mean
-    \item Dependence of results on assumptions on assumptions such as the Fe yield/plateau value. Contrast the results for different assumptions and show the uncertainty in fcc 
+\itemsep0em
+    \item $\mgh > -0.75$
+    \item S/N $\geq 200$
+    \item $\logg = 1-3$ dex
+    \item $\teff = 4000-5200$ K.
 \end{itemize}
+To eliminate red clump (RC) stars, which show abundance variations from the RGB sample \citep{vincenzo2021a}, we cross-match with and remove stars that appear in the APOGEE RC VAC \ejg{Add Citation}.
+These cuts result in a sample of 48,659 stars.
 
-\subsection{Dependence of $\fcc$ on Assumptions} \label{subsec:fcc}
+% W22 employ a smaller $\logg$ ($1.0-2.5$) and $\teff$ ($4000-4600$) range, add distance requirement ($R=3-13$ kpc with distances from \citealp{leung2019}), and place a weaker SNR requirement ($>100$) for stars with [Mg/H] $< -0.5$.
+By expanding the W22 sample, we increase the number of stars in the training set by a factor of 1.4.
+
+We present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, Mn, Co, and Ce.
+In the analysis of each element, X, we drop stars with \texttt{X\_FE\_FLAG} (maximum of $\sim 700$ for Ce).
+While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge-up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
+As in W22, we consider C+N as an element, taking [(C+N)/H] to be
+\begin{equation}
+    [\text{C+N}/\text{H}] = \log_{10}(10^{\text{[C/H]}+8.39} + 10^{\text{[N/H]}+7.78}) - \log_{10}(10^{8.39} + 10^{7.78})
+\end{equation}
+using logarithmic solar abundances for C (8.39) and N (7.78) from \citet{grevesse2007}.
+We further adopt the error on the [C/Fe] abundance as the error on [C+N/Fe], since C typically dominates in the abundance ratio.
+
+We plot the distributions of all abundances in [X/Mg] vs. [Mg/H] for the training sample in the first column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/all_param1.pdf}
+    \caption{Abundance distributions and Few-process model parameters for C+N, $\alpha$, and light odd-$Z$ elements.
+First column: observed abundance distributions in [X/Mg] vs.
+[Mg/H].
+Second column: fiducial few-process model predicted abundance distributions in [X/Mg] vs.
+[Mg/H].
+Third column: process vectors $\qcc$ (purple) and $\qIa$ (orange) from this work (solid, dark lines) and W22 (light, dashed lines).
+Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial few-process model.
+We plot the median $\fcc$ values of the low-Ia (orange square) and high-Ia (purple circle) populations in the solar metallicity bin from W22 for comparison.}
+    \label{fig:all_param1}
+\end{figure*}
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/all_param2.pdf}
+    \caption{Same as Figure~\ref{fig:all_param1}, but for Fe-peak elements and Ce.}
+    \label{fig:all_param2}
+\end{figure*}
+
+\section{The Fiducial Model} \label{sec:fiducial}
+
+We fit the training sample with our fiducial model of $K=2$ and $\qccFe = 0.4$ as described above.
+This fit produces process vectors $\qcc$ and $\qIa$ as a function of $\mgh$ for each element and process amplitudes $\Acc$ and $\AIa$ for each star.
+\ejg{Add sentence about the uncertainty on these values.} From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted two-process abundances.
+
+\subsection{Process Parameters and Fractional Contributions} \label{subsec:parameters}
+
+We plot the process vectors as a function of $\mgh$ in the third column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
+The process vectors inform us about the relative contribution of prompt and delayed processes to the formation of the elements, as well as the metallicity dependence of the enrichment.
+By definition, $\qccFe=0.4$ at all metallicities.
+For Fe only, we also require $\qccFe + \qIaFe = 1$, implying $\qIaFe=0.6$.
+No such constraints are placed on any other element.
+
+In the fourth column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}, we plot the distribution of fractional contributions from the prompt process ($\fcc$) to each element, where
+\begin{equation}\label{eq:fcc}
+    \fcc = \frac{\Acc\qcc}{\Acc\qcc + \AIa\qIa}.
+\end{equation}
+We generally find that the distributions are bimodal, like the observed abundance patterns, as the high-Ia and low-Ia populations have differing fractional contributions from prompt and delayed sources.
+
+We find that the $\alpha$-elements (O, Si, S, Ca) are best fit with $\qcc$ and $\fcc > 0.5$ at all metallicities.
+This is in agreement with theoretical prediction that $\alpha$-elements are dominated by prompt CCSN production \citep[e.g.][]{andrews2017}.
+O, a Mg-like element theoretically purely produced in prompt CCSN, shows $\fcc$ near 1 from $\mgh=-0.75$ to solar.
+At supersolar $\mgh$, the delayed process contributes to O production, driving the $\fcc$ value down to $\sim 0.8$ at $\mgh=0.4$.
+S behaves like O, with almost entirely prompt production up to solar metallicity, after which delayed enrichment contributes more significantly.
+Conversely, we find that Si and Ca are best fit with prompt and delayed enrichment at all metallicities, though the prompt process always dominates.
+For Si, the delayed process appear to increase linearly with $\mgh$, while the Ca delayed enrichment increases from $\mgh$ of $-0.75$ to $-0.1$ and then decreases from $\mgh$ of $-0.1$ to $0.5$.
+
+The process vectors of light odd-$Z$ elements Al and K resemble those of the $\alpha$-elements, such as S.
+Both exhibit $\qcc$ and $\fcc$ near 1 through solar metallicity, with an increase in $\qIa$ and downturn in $\fcc$ at supersolar metallicities (especially for K).
+The behavior of the Na process vectors is more complex, with peaks and troughs in $\qIa$.
+We find that Na has the strongest contributions from the delayed process of all $\alpha$ and light odd-$Z$ elements, with $\qIa \gtrsim 0.5$ at almost all values of $\mgh$ and $\fcc < 0.3$ at $\mgh > 0$.
+The strong delayed contribution to Na is in agreement with findings of W22 and G22, and in tension with theoretical yields \citep[e.g.][]{andrews2017, rybizki2017}.
+
+Unlike $\alpha$ and light odd-$Z$ elements whose delayed production is dominated by SNIa, C and N are thought to be promptly produced in CCSN with additional delayed enrichment from AGB stars \citep[e.g.][]{andrews2017}.
+We find that the prompt and delayed processes both contribute significantly, and nearly equally, across our stellar sample.
+Though theoretical N yields from AGB stars have a strong metallicity dependence \citep{karakas2010, ventura2013, cristallo2015, johnson2022}, we observe only a slight positive metallicity dependence in $\qcc$ and a shallow dip in $\qIa$.
+We find a population of stars with $\fcc$ near 0.9 and a population with $\fcc$ near 0.4.
+
+The Fe-peak elements (Cr, Mn, Fe, Co, Ni) are thought to be produced through prompt CCSN production and delayed SNIa production \citep[e.g.][]{andrews2017}.
+By construction, $\qccFe=0.4$ and $\qIaFe=0.6$ at all metallicities.
+This produces a bimodal distribution in $\fcc$ similar to that observed in abundances space.
+Because of our choice of $\qccFe$, only a few stars have $\fcc=1$ (see Section~\ref{subsec:qccFe}).
+We instead observe a population with $\fcc$ near 0.8 and a population with $\fcc$ near 0.4.
+The process vectors and $\fcc$ distribution for Cr and Ni strongly resemble those of Fe.
+All three elements have even atomic numbers.
+At supersolar metallicity, we find that the prompt process dominates Cr production, resulting in an upturn in $\fcc$.
+Conversely, Ni displays a dominant, and increasing, delayed proccess vector at supersolar metallicities.
+The process vectors for Mn and Co (odd atomic numbers) show a complex metallicity dependence, more resembling that of Na.
+Both elements display a strong delayed process, with the Mn $\qIa > 0.5$ at all metallicities and $> 1$ for $\mgh > 0.1$.
+Mn is the only element for which $\fcc$ decreases to 0 for $\mgh \gtrsim 0.2$.
+
+Finally, APOGEE DR17 reports abundances for one neutron capture element---Ce.
+We find that the delayed process dominates at intermediate metallicity, with $\qIa$ increasing up to $\mgh \approx -0.2$ and then decreasing to nearly 0 at $\mgh \approx 0.3$.
+The Ce $\fcc$ values are clustered near 0.25 around $\mgh$ of 0,2, then increase such that the abundances are almost entirely dominated by prompt enrichment at high metallicity.
+
+In addition to process vectors, each star is fit with a prompt and delayed process amplitude, $\Acc$ and $\AIa$ respectively.
+All elemental abundance are used in the calculation of these amplitudes.
+The value of $\Acc$ traces the metallicity (specifically $\mgh$) while the ratio of $\AIa/\Acc$ traces the $\femg$ abundance.
+In the left panel of Figure~\ref{fig:As} we plot the distribution of $\AIa/\Acc$ vs.
+$\Acc$.
+We find a bimodal distribution, similar to the Tinsley-Wallerstein diagram ($\mgfe$ vs.
+$\feh$, \citealp{wallerstein1962, tinsley1979, tinsley1980}), as was also found in W22 and G22.
+We stress, however, that the presence of the abundance bimodality was not fed into our model, and yet it is recovered in the best-fit process amplitudes.
+The stars with larger $\AIa/\Acc$ values correspond to the traditional high-Ia or low-$\alpha$ population, and those with low $\AIa/\Acc$ correspond to the low-Ia or high-$\alpha$ population.
+While in the Tinsley-Wallerstain diagram, the two populations blend together at high-metallicity, they are more distinguishable in amplitude space.
+To further show this, we plot $\AIa/\Acc$ vs.
+$\mgh$ in the right panel of Figure~\ref{fig:As}.
+The high-Ia and low-Ia populations are clearly seperable through $\mgh$ of 0.4.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=.8\textwidth]{Paper/Figures/As.pdf}
+    \caption{Left: distribution of $\AIa/\Acc$ vs.
+$\Acc$ for the fiducial model.
+Right: distribution of $\AIa/\Acc$ vs.
+$\mgh$.
+In both panels, we can clearly see the bimodality to high values of $\Acc$ and $\mgh$.}
+    \label{fig:As}
+\end{figure*}
+
+\subsection{Predicted Abundances} \label{subsec:preds}
+
+With the optimized process parameters in hand, we can use Equation~\ref{eq:xh} to calculate predicted abundances for $K=2$---the abundances our stellar population would have if the model assumptions are correct and only one prompt and one delayed process contribute.
+To simulate observational noise, to each abundance for each star, we add an error drawn from a Gaussian distribution with $\sigma$ equal to the reported APOGEE abundance error.
+In Figure~\ref{fig:all_param1} and~\ref{fig:all_param2} we plot the predicted abundances in the second columns.
+These distributions can be compared the the observed abundance distribution in the first columns.
+
+Overall, the fiducial model successfully reproduces the observed abundance distributions.
+It is capable of capturing metalicity dependences and bimodality.
+The predicted abundances are not, however, able to reproduce the observed abundance scatter, especially at low metallicity.
+This is especially noticeable for C+N, Na, Al, K, Co, and Ce.
+\ejg{Add that this suggests $K>2$ or underestimated APOGEE errors?}
+
+Amongst the $\alpha$-elements, the fiducial model successfully reproduces the near-solar [O/Mg] ratios, but does not capture the scatter above and below [O/Mg]$\approx 0$ at $\mgh\approx-0.5$ and -0.2, respectively.
+Similarly, the predicted abundances capture the slight negative metallicity dependence in the [S/Mg] abundances, but again fail to capture the scatter.
+The predicted [Si/Mg] and [Ca/Mg] abundance distributions both resemble the observed bimodal population with a small gap between the high-Ia and low-Ia populations.
+
+The fiducial model is also successful at reproducing the population abundance trends for the light odd-$Z$ elements, picking up the downturn in [Al/Mg] at low-$\mgh$, the upturn in [K/Mg] at high-$\mgh$, and the bimodal [Na/Mg] distribution.
+The predicted abundances obviously fail to capture the scatter in all light odd-$Z$ elements.
+Similarly, the scatter in the predicted [C+N/Mg] distribution is smaller than that of the observed.
+The $K=2$ model also struggles to reproduce the observed plateau at [C+N/Mg]$\approx -0.1$ and $\mgh\approx-0.5$.
+
+The abundance distributions of the Fe-peak elements all show strong bimodality, due in part to the substantial delayed production from SNIa.
+The fiducial model is able to capture the bimodality and metalicity dependence observed in Cr, Mn, Fe, Co, and Ni.
+We again note that the abundance scatter is slightly smaller in the predicted abundances.
+We also find that the [Fe/Mg] and [Ni/Mg] abundances of the high-Ia population are less dense and blurred.
+
+The [Ce/Mg] abundance distribution is unique, displaying a rising-then-falling metallicity dependence, similar to the behavior observed in [Ba/Mg] and [La/Mg], neutron capture elements observed by GALAH (e.g.
+G22).
+This metallicity dependence is expected from the slow-neutron capture process ($s$-process) where, at low metallicity, the number of seed increases, while at high metallicity, the number of neutrons per seed becomes increasingly insufficient to produce the heavier elements \citep{gallino1998}.
+The $K=2$ model is able to reproduce the peaked abundance pattern, but fails to reach the high [Ce/Mg] values observed in the data.
+The scatter in the observed abundance distribution is much larger than in the predicted distribution, suggesting that either the $K=2$ model is insufficient or that the APOGEE scatter is underestimated.
+
+\subsection{Comparing to W22}\label{subsec:w22}
+
+As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, the few-process model presented in this paper is based upon the two-process model developed in W19 and W22, but with increased flexibility and no forced dependence upon the bimodality or population abundance trends.
+Further, the few-process model utilizes all stellar abundances in the optimization of $\Acc$ and $\AIa$, where as only Mg and Fe are used in W19 and only Mg, O, Si, Ca, Fe, and Ni in W22.
+
+In the fiducial few-process model, we adopt $K=2$, as in W22, but assume $\qccFe = 0.4$, 0.1 dex lower than the $\qccFe$ value assumed in W22.
+In practice, this moves the implied ``pure'' CCSN enrichment plateau from $\femg=-0.3$ to $\femg=-0.4$ (though W22 plateau value is determined \textit{after} they apply a global offset of +0.05 to all $\femg$ abundances).
+Because our model is non-negative, it requires a lower $\qccFe$ and thus lower plateau value to correctly model the stars on the $\femg$ plateau, where as W22 assigns stars with $\femg < -0.3$ negative $\AIa$ values.
+
+While our stellar samples and model assumptions differ, we plot the W22 $\qcc$ and $\qIa$ vectors as well as the W22 median $\fcc$ values of their high-Ia and low-Ia populations at $\mgh=0$ in columns three and four, respectively, of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2} for comparison to the few-process model parameters.
+
+Amongst the process vectors, we generally observe similar behavior between our model and W22.
+Our $\qIa$ vectors tend to be $\sim 0.1$ greater than those of W22 for elements with significant delayed contributions because of our differing $\qccFe$ assumptions.
+The metallicity dependencies agree for most elements, with small variations at the high-$\mgh$ end for O, Al, K, and Ce.
+We also see good agreement between the two models' solar $\fcc$ values, with the W22 points slightly offset to larger values for elements with significant delayed contributions, again because of our differing $\qccFe$ assumptions.
+
+To compare the accuracy of the models' abilities to reproduce the observed abundances, we identify a subset of $\sim 23,000$ stars in our training sample and the W22 sample.
+We calculate the few-process and two-process predicted abundances for each star, then determine the $\chi^2$ value of the fits for each star (summing over the elements) and for each element (summing over the stars).
+We plot the cumulative stellar $\log(\chi^2)$ distribution and the total $\chi^2$ for each element in the right and left panels, respectively, of Figure~\ref{fig:comp_w22}.
+It is important to note that in the calculation of the W22 model residuals, we do not apply the temperature correction discussed in Section 5.1 of W22.
+We find that, overall, the $\log(\chi^2)$ decreases between the W22 two-process model and our few-process model, an indication that we better predict the stellar abundances.
+When we look at each element individually, we find that we better predict C+N, Na, K, Ni, Mn, Co, and Ce, with major improvements to C+N and Mn.
+Our fiducial model is significantly worse at predicting Mg, Ca, and Fe than the W22 model, all elements that W22 fit to.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/comp_w22.pdf}
+    \caption{Left: cumulative distribution of $\log \chi^2$ for W22 (dashed orange line) and our fiducial model (solid purple line). Right: $\chi^2$ per element for the same model fits. }
+    \label{fig:qs}
+\end{figure*}
+
+In this comparison, it is important to note our fiducial model is fit to a larger stellar sample that spans a wider range of $\teff$ and $\logg$ than the W22 sample.
+If we repeat our analysis on the W22 stellar sample with $\qccFe=0.5$ we almost perfectly recover the W22 process vectors, with small deviations at $\mgh>0.1$, and more substantially improve upon the stellar and elemental $\chi^2$ values.
+Most notably, the few-process model is better able to predict the abundances of stars with $\mgh>0$, where the high-Ia and low-Ia sequences blend together and the W22 division of high-Ia and low-Ia stars may be incorrect.
+\ejg{Would it be worth adding an appendix on this?}
+
+\section{Variations from the Fiducial Model} \label{sec:variations}
+
+\subsection{Choice of $\qccFe$} \label{subsec:fcc}
+
+\ejg{I think I have too many plots in this section....}
+
+While the few-process model is flexible, it still requires us to make assumptions in order for the parameters to converge.
+Specifically, it requires an element with ``known'' $\qcc$ and an element with known $\qIa$ to constrain each process and to break degeneracies.
+For the prompt process, we ground our assumption in the nucleosynthetic fact (\ejg{change wording}) that Mg is a pure CCSN element \citep[e.g.,][]{andrews2017}.
+Unfortunately, there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
+In order to regularize the delayed process, we choose to fix the Fe process vectors, making unsubstantiated assumptions about Fe enrichment.
+
+In the fiducial model, we choose $\qccFe = 0.4$ as this parameter choice is able to reproduce the observed [Fe/Mg] vs.
+[Mg/H] abundance distribution, as discussed in Section~\ref{subsec:parameters}.
+This choice impacts the predicted abundances as well as the implied $\fcc$ values of each star.
+In this section, we explore the implications of different $\qccFe$ assumptions, varying the zero point and metallicity dependence ($\dqccFe$).
+Because our model is non-negative, the choice of $\qccFe$ set the minimum [Fe/Mg] value attainable by our model ($\log_{10}(\qccFe)$).
+Under the $K=2$ few-process model, any observed [Fe/Mg] abundance below this boundary can only be explained by noise.
+In Figure~\ref{fig:qccFe_FeMg}, we plot the minimum [Fe/Mg] as a function of $\mgh$ for the $\qccFe$ and $\dqccFe$ parameters we explore.
+With a $\dqccFe=0.0$, we choose $\qccFe=0.5$ (the W22 value), 0.45 (approximate plateau value at $\mgh=-0.75$), 0.4 (the fiducial value that skirts the edge of the distribution), and 0.35 (captures almost all stars).
+With a $\dqccFe=0.15$, which roughly matches the slope of the low-Ia sequence at intermediate metallicity, we choose $\qccFe=0.5$ (passes through the center of the low-Ia density), 0.4 (skirts the edge of the distribution), 0.3 (captures almost all stars)
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMg.pdf}
+    \caption{Minimum [Fe/Mg] value attainable for $\qccFe$ and $\dqccFe$ assumptions.
+Left: For $\dqccFe=0$ with $\qccFe=0.5$, 0.45, 0.4, and 0.3 (light to dark purple).
+Right: For $\dqccFe=0.15$ with $\qccFe=0.5$, 0.4, 0.35 (light to dark orange).}
+    \label{fig:qccFe_FeMg}
+\end{figure*}
+
+We repeat the optimization of the few-process model with $K=2$ and these $\qccFe$ assumptions, as described in Section~\ref{sec:model}.
+In Figure~\ref{fig:qccFe_FeMgpred}, we plot the predicted abundance distributions (including APOGEE noise), as in the second column of Figures~\ref{fig:all_param1} and ~\ref{fig:all_param2}.
+We do not plot the predictions for the fiducial model ($\qccFe=0.4$, $\dqccFe=0.0$), as these have been shown in Section~\ref{subsec:preds}.
+Both models with $\qccFe=0.5$ fail to reproduce the shape and width of the low-Ia abundance distribution.
+They instead predict a much thinner sequence that is flat for $\dqccFe=0.0$ or slightly inclined for $\dqccFe=0.15$.
+The model with $\qccFe=0.45$ and $\dqccFe=0.0$ is better, but still predicts a low-Ia abundance distribution that is too thin, flat, and dense.
+The other four models ($\qccFe=0.35$ and $\qccFe=0.4$ with $\dqccFe=0.0$ and $\dqccFe=0.15$) predict an abundance distribution that strongly resembles the observed.
+There are minor differences at the low [Fe/Mg] and low-metallicity end, but it is difficult to tell by eye which model is best.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMgpred.pdf}
+    \caption{Predicted [Fe/Mg] vs.
+[Mg/H] abundance distributions for models with $\dqccFe=0.0$ (top row) and $\dqccFe=0.15$ (bottom row).
+The $\qccFe$ value increase from left to right from 0.35 to 0.5.
+$\qccFe$ and $\dqccFe$ parameters are listed in each panel.}
+    \label{fig:qccFe_FeMgpred}
+\end{figure*}
+
+To better assess the models' goodness of fit, we calculate the average $\chi^2$ value per star for each case and plot the results in Figure~\ref{fig:qccFe_chi2}.
+The models with $\qccFe$ of 0.5 or 0.45, regardless of $\dqccFe$, have an average $\chi^2$ per star $>90$ while the models with $\qccFe$ of 0.4 and 0.35 have an average $\chi^2$ per star $< 55$.
+In both the metallicity independent and metalicity dependent models, the models with $\qccFe=0.4$ have the lowest average $\chi^2$ per star, by 0.13 and 0.8 respectively.
+Of the seven models explored here, the case with $\qccFe=0.4$ and $\dqccFe=0.15$ has the lowest average $\chi^2$ per star of 54.47, indicating that the stellar abundances are best fit by a metallicity dependent CCSN process.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_chi2.pdf}
+    \caption{Average $\chi^2$ per star for few-process models with a range of $\qccFe$ and $\dqccFe$ values. \ejg{Maybe this should just be a table.}}
+    \label{fig:qccFe_chi2}
+\end{figure*}
+
+Though the $\qccFe= 0.4$ and 0.35 are similar in terms of their goodness of fit, their nucleosynthesis implications are more significant.
+In Figure~\ref{fig:qccFe_fcc}, we plot the median value of $\fcc$ (Equation~\ref{eq:fcc}) for the low-Ia population (as defined in W22 \ejg{need to add this definition}) at solar metallicity ($-0.05 < \mgh < 0.05$).
+We only show the $\fcc$ values for the models with $\dqccFe=0.0$ as the solar metallicity $\fcc$ values for the models with $\dqccFe=0.15$ are almost identical for matching values of $\qccFe$.
+
+In Figure~\ref{fig:qccFe_fcc}, we find that the choice of $\qccFe$ has little impact on the $\fcc$ of elements dominated by CCSN enrichment (e.g.
+O, S, Al, K).
+As the delayed contribution increases, the elemental $\fcc$ values decrease more significantly with decreasing $\qccFe$.
+The choice of $\qccFe$ most impacts the $\fcc$ values for Na, Cr, Fe, Mn, and Ce, with the $\fcc$ for Mn decreasing from 0.42 for $\qccFe=0.5$ to 0.22 for $\qccFe=0.35$.
+Because the $\qccFe$ value sets the ``pure CCSN'' plateau, a lower $\qccFe$ model implies a lower $\fcc$ value.
+
+While the high $\qccFe$ model can likely be ruled out due to poorness of fit, the true $\qccFe$ value and its metallicity dependence are unknown.
+It is therefore important not to over-interpret the specific $\fcc$ values of a given model, or to include error bars based on a range of reasonable $\qccFe$ assumptions.
+The $\fcc$ parameter can provide qualitative descriptions of which elements have more or less prompt/delayed enrichment, but the exact values are uncertain by up to XXX\%
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_fcc.pdf}
+    \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for few-process models with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.
+\ejg{Add legend!}}
+    \label{fig:qccFe_fcc}
+\end{figure*}
+
+\ejg{Maybe a run where we turn down the regularization on qcc Fe and see what it picks? Update: tried this and it failed to converge}
+
+\subsection{Increasing to $K=4$} \label{subsec:k=4}
 
 \section{Application to a Broader Data Sample} \label{sec:results_broad}
+
+\subsection{Testing Sample}
+
+\ejg{I think this should be moved to the end for an entire section on the testing sample.}
+
+Beyond the training sample presented above, we are also interested in the Few-Process model's implications for a wider sample of data.
+In Section X, we argue that the Few-Process model produces high signal-to-noise abundance labels, as it uses all elements for all stars to learn the process parameters.
+These high SNR labels are useful for XYZ and allow us to understand what the abundance patterns \textit{would} look like if our model assumptions are correct.
+To provide the community with a large catalog of such labels, we apply the fiducial Few-Process model to the APOGEE RC and RGB sample, defined by the following cuts:
+\itemsep0em
+\begin{itemize}
+    \item \texttt{STAR\_BAD} = 0
+    \item \texttt{NO\_ASPCAP\_RESULT} = 0
+    \item \texttt{EXTRATARG} = 0
+    \item $\logg =  0 - 3.5$ dex
+    \item $\teff = 3200-6000$ K
+    \item $\mgh > -0.75$
+\end{itemize}
+with the upper $\teff$ limit and $\logg$ used as RGB classifiers in \citet{jonsson2020}.
+Our full sample includes 227,601 stars.
+We again only analyze [X/Mg] abundances for stars where the [X/Fe] value is unflagged, most drastically reducing the sample size to 195,117 for Ce.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Figures/xmg_test.pdf}
+    \caption{Stellar abundance distributions for our expanded RGB and RC sample.
+The number in the top right corner indicates the number of stars used in the analysis of that element.
+Elements are ordered by atomic number.
+No zero-point offsets have been applied.}
+    \label{fig:exp_xmg}
+\end{figure*}
+
+We plot the distribution of abundances in [X/Mg] vs.
+[Mg/H] for the testing sample in Figure~\ref{fig:exp_xmg}.
+The expansion of the data sample does introduce abundance systematics that our training sample sought to exclude.
+As discussed in \citet{jonsson2020} and \citet{griffith2021a}, APOGEE DR16 and DR17 suffer from poorly understood abundance artifacts, such as a ``finger'' in [$\alpha$/M] and low-[X/Fe] banding in elements such as Al and Ni.
+In our expanded data set, we observe potential abundance artifacts in Na, Al, K, Cr, Co, and Ce, as well as larger scatter for all elements.
 
@@
     \item Why this version of the 2 process model is more flexible than W22
+    \item two dimensional doesn't mean there are two processes, things are just getting mixed down to two dimensions  - maybe two d because radius and age, if true then our labels should predict age and radius
+    \item our 2 dimentionality is not defined by the bimodality like W22 is
+    \item why k=2 is a good fit to this data, all the different ways we could get K=2 - young open clusters don't fit the model is a blow against the view
 \end{itemize}

### 2023-06-03 Paper/main.tex
Lots and lots of content

--- 2023-01-24 Paper/main.tex
@@
 \newcommand{\mgfe}[0]{[{\rm Mg/Fe}]}
-\newcommand{\Acc}{A_{\rm cc}}
-\newcommand{\AIa}{A_{\rm Ia}} 
-\newcommand{\RIa}{R_{\rm Ia}^X}
-\newcommand{\aIa}{\alpha_{\rm Ia}}
-\newcommand{\acc}{\alpha_{\rm cc}}
 \newcommand{\afe}[0]{[\alpha/{\rm Fe}]}
@@
 \newcommand{\feh}[0]{[{\rm Fe/H}]}
-\newcommand{\pIa}{p_{\rm Ia}^{\rm X}}
-\newcommand{\pcc}{p_{\rm cc}^{\rm X}}
-\newcommand{\fcc}{f_{\rm cc}}
 \newcommand{\xfe}{[{\rm X}/{\rm Fe}]}
-\newcommand{\pIasun}{p_{\rm Ia, \odot}^{\rm X}}
-\newcommand{\pccsun}{p_{\rm cc, \odot}^{\rm X}}
+\newcommand{\xh}{[{\rm X}/{\rm H}]}
+
 \newcommand{\logg}{\log(g)}
@@
 \newcommand{\MZAMS}{M_{\rm ZAMS}}
-\newcommand{\Msun}{M_{\odot}}
-\newcommand{\qIax}{q_{\rm Ia}^{\rm X}}
-\newcommand{\qccx}{q_{\rm cc}^{\rm X}}
-\newcommand{\qagbx}{q_{\rm AGB}^{\rm X}}
-\newcommand{\qIa}{q_{\rm Ia}}
-\newcommand{\qcc}{q_{\rm cc}}
-\newcommand{\qagb}{q_{\rm AGB}}
-\newcommand{\Aagb}{A_{\rm AGB}}
-\newcommand{\eumg}{[{\rm Eu}/{\rm Mg}]} 
-\newcommand{\mgmn}{[{\rm Mg}/{\rm Mn}]} 
-\newcommand{\alfe}{[{\rm Al}/{\rm Fe}]} 
-\newcommand{\omg}{[{\rm O}/{\rm Mg}]} 
-\newcommand{\xo}{[{\rm X}/{\rm O}]} 
-\newcommand{\xh}{[{\rm X}/{\rm H}]} 
-\newcommand{\angstrom}{\textup{\AA}}
-\newcommand{\ejg}[1]{\textcolor{red}{EJG: #1}}
+
+\newcommand{\qcc}{q_{{\rm CC,}j}^{Z}}
+\newcommand{\qccFe}{q_{{\rm CC, Fe}}^{Z}}
+\newcommand{\dqccFe}{dq_{{\rm CC, Fe}}^{Z}/dZ}
+\newcommand{\qIa}{q_{{\rm Ia,}j}^{Z}}
+\newcommand{\qIaFe}{q_{{\rm Ia,Fe}}^{Z}}
+\newcommand{\Acc}{A^{\rm CC}_{i}}
+\newcommand{\AIa}{A^{\rm Ia}_{i}}
+\newcommand{\fcc}{f_{{\rm CC}, ij}}
+
+\newcommand{\ejg}[1]{\textcolor{red}{EJG says: #1}}
+\newcommand{\hogg}[1]{\textcolor{blue}{Hogg says: #1}}
 
@@
 
-\newcommand{\name}{\textsl{Foo}} % Hogg's just making this up; change it!!
+% text macros
+\newcommand{\name}{\textsl{KPM}} 
 \newcommand{\documentname}{\textsl{Article}}
 
-\shorttitle{data-driven few-process model for nucleosynthesis}
-\shortauthors{griffith and hogg}
+% typesetting stuff
+\shorttitle{a data-driven model for nucleosynthesis}
+\shortauthors{Griffith \& Hogg}
 \addtolength{\topmargin}{-0.4in} % trust in Hogg
@@
 \setlength{\parindent}{1.6em}
+\renewcommand{\twocolumngrid}{} % once again
 \renewcommand{\paragraph}[1]{\bigskip\par\noindent{\textbf{#1}}~---}
 \sloppy\sloppypar\raggedbottom\frenchspacing % Trust Hogg
+
+%\linespread{1.8}
 
@@
 
-\title{\name: A data-driven few-process model for nucleosynthesis}
+\title{\name: A flexible and data-driven $K$-process model for nucleosynthesis}
 
@@
 
-% \author[0000-0001-7775-7261]{David H. Weinberg}
-% \affiliation{The Department of Astronomy and Center of Cosmology and AstroParticle Physics, The Ohio State University, Columbus, OH 43210, USA}
-% \affiliation{The Institute for Advanced Study, Princeton, NJ, 08540, USA}
-
 \begin{abstract}\noindent % trust Hogg
-Testing
-
 Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
-We analyze YYY abundance ratios (ratioed to Mg) for XXXX stars from APOGEE DR17 with a flexible two-process model, in which all element process amplitudes are free parameters.
-The two-process model describes each element abundance of each star as the vector sum of a CCSN and SNIa process.
-Prior work derives process amplitudes from median observed high-Ia and low-Ia abundance trends; we relax these assumptions and simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
-We compare fit parameters from this new method to those derived from prior work [that the two methods produce similar results but with XXX differences and identify similar outlier stars??].
-Our flexible method---dubbed \name---tests the validity of the standard two-process assumptions, such as Mg being a pure CCSN element, and that Solar abundances are generated by a roughly half-half combination of CCSN and SNIa processes.
-We find [that the assumptions of prior work are generally confirmed??].
-We capitalize on the flexibility to explore the addition of a third process, agnostic about its origin.
-The third process most improves [X elements? most significant for X elements?].
-Most importantly, \name{} can be extended to populations at very low metallicity, and populations without two clear abundance sequences, such as the LMC/SMC, Sagittarius, and Gaia-Enceladus (??), making it a general diagnostic for enrichment; in principle, it can also be used to constrain fundamental nucleosynthetic parameters.
+We analyze the abundances of 14 elements in [X/Mg] vs. [Mg/H] space for 48,659 stars from APOGEE DR17 with a flexible, data-driven $K$-process model---dubbed \name.
+In the fiducial model, where $K=2$, each elemental abundance of each star is described as the vector sum of a prompt (CCSN-like) and delayed (SNIa-like) process.
+While prior work derives process vector components from median observed high-Ia and low-Ia abundance trends, we relax these assumptions and simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
+We find that our flexible method is able to recover the observed abundance bimodality and that this bimodality is visible to higher [Mg/H] in process amplitude space than in abundance space.
+We compare fit parameters and statistics from this new method to those from prior work, finding that the two methods produce similar results, but that \name{} better predicts stellar abundances, especially for C+N and Mn.
+We test the validity of the standard two-process model assumptions, such as that Fe is generated by a roughly half-half combination of prompt and delayed sources.
+We find that the assumptions of prior works are generally confirmed, but that the inferred fractional contributions from each process are strongly dependent upon Fe assumptions.
+We also explore third and fourth processes, calibrated to Ce and Mn, respectively.
+The additional processes improve the model's ability to predict the stellar abundances, demonstrating the model's ability to extend beyond $K=2$.
+\name{} enables future research to study the disk's two-dimensionallity, investigate age-abundance label correlations, fit non-bimodal abundance distributions with a multi-component nucleosynthetic model, and much more.
+\ejg{Add something about code availability.}
 \end{abstract}
@@
 
-\section*{}\clearpage
-HOGG SAY: Here are some things to do or think about:
-\begin{itemize}
-  \item Should we think of this as a 2-process model or as a $K$-process model, where $K$ is often 2? I'm leaning towards $K$.
-  \item \ejg{I like the K-process model. (This is named $N$-Process model in W22)}
-  \item What are we going to do in terms of interpreting the results? These process vectors aren't exactly yields; they are something way more complicated, right?
-  \item \ejg{Interpret in terms of $\fcc$. Can also make inferences about the metalicity dependence of SNIa/CCSN enrichment to given elements based on how $\qcc$ and $\qIa$ evolve with time.}
-\end{itemize}
-
 \section{Introduction}\label{sec:intro}
 
-After hydrogen, helium, lithium, and beryllium, essentially all other naturally occurring elements are made in stars, and the collisions of stars.
-We are literally made of star stuff.
-Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed (for most elements) record of the element abundances in the gas from which the star formed (though see \ejg{Add citations}).
+After hydrogen, helium, lithium, and beryllium, all other naturally occurring elements are made in the stars, and the collisions of stars.
+Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed record of the element abundances in the gas from which the star formed \citep[though see e.g.,][]{pinsonneault2001, oh2018, souto2019, vincenzo2021b}.
 These birth abundances were set by a combination of nucleosynthetic processes involved in making heavy atomic nuclei, and astrophysical processes involved in delivering atoms from stellar interiors to star-formation sites \citep[e.g.,][]{johnsonja2020}.
-Thus nuclear physics and a wide swath of astrophysics are critically intertwined in our understanding of stellar surface abundances.
-That's important, and motivates a lot of theoretical, experimental, and observational work in nuclear physics and astrophysics.
+Thus nuclear physics and a wide swath of astrophysics are critically intertwined in our understanding of stellar surface abundances, motivating theoretical, experimental, and observational work.
 
@@
 In this \documentname{}, we build a purely data-driven model for the surface element abundances observed in stars.
-We treat each star as being a linear combination of two nucleosynthetic processes, one of which is primarily responsible for the $\alpha$-element Mg \citep[core collapse supernovae (CCSN), e.g.][]{andrews2017}, and one of which is primarily \emph{not} (Type-Ia supernovae (SNIa)).
-Beyond that up-front assumption, we try to be agnostic about how the elements are produced.
+We treat each star as being a linear combination of nucleosynthetic processes, beginning with one that is primarily responsible for the $\alpha$-element Mg \citep[prompt enrichment, such as core collapse supernovae or CCSN, e.g.,][]{andrews2017}, and one that is primarily \emph{not} responsible for Mg (delayed enrichment, such as Type-Ia supernovae or SNIa).
+Beyond these up-front assumption, we try to be agnostic about how the elements are produced.
 
-We build upon the work of \citet[][hereafter G22]{griffith2019, griffith2022} and \citet[][hereafter W22]{weinberg2019, weinberg2022}, who used the bimodality in [Mg/Fe] vs.
-[Fe/H] \citep[e.g.,][]{fuhrmann1998, bensby2003, adibekyan2012} to separate stars into populations with high and low SNIa enrichment.
+We build upon the work of \citet[][hereafter G22]{griffith2019, griffith2022} and \citet[][hereafter W19, W22]{weinberg2019, weinberg2022}, who used the bimodality in [Mg/Fe] vs.
+[Fe/H]\footnote{Where $[{\rm X}/{\rm Y}] = \log({\rm X}/{\rm Y}) - \log({\rm X}/{\rm Y})_{\odot}$ and $({\rm X}/{\rm Y})_{\odot}$ is the solar abundance ratio.} \citep[e.g.,][]{fuhrmann1998, bensby2003, adibekyan2012} to separate stars into populations with high and low SNIa enrichment.
 Using the median [X/Mg] vs.
@@
 [Mg/H] space are largely insensitive to aspects of chemical evolution, such as outflows and variations in star formation history \citep{weinberg2019}, the population abundance trends are set by the nucleosynthetic processes and can be used to empirically constrain Galactic enrichment.
-To fit the two-process model to survey data, G22 and W22 assume that Mg is purely produced by CCSN, Fe is produced in equal amounts by CCSN and SNIa, and that the CCSN/SNIa yields of Mg and Fe are metallicity independent.
-While the first assumption is firmly grounded in nucleosynthetic theory \citep[e.g.,][]{andrews2017, rybizki2017}, the others are based on APOGEE abundance patterns and may not be realistic constraints.
 
-Beyond the two-process model, many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep{kilpatrick2017}, or atypical supernovae explosion.
+These works, as well as \citet{ting2022}, find that the Milky Way stellar abundances are well fit two components, down to residuals of 0.01 to 0.02 dex.
+Simultaneously, \citet{frankel2018} and \citet{ness2022} have found that disk abundances are also well described by a two component model of birth radius and age.
+Correlations between two-process model parameters and stellar ages and kinematics (W22) suggest that these two 2-dimensional models are somehow interconnected.
+\ejg{Add bit on why two processes dominate---two main channels v.s.
+mixing in the disk.}
+
+Beyond standard CCSN and SNIa enrichment many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep[e.g.,][]{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep[e.g.,][]{kilpatrick2017}, or atypical supernovae explosion \citep[e.g.,][]{nomoto2013}.
 After predicting stellar abundances from $\feh$ and $\mgfe$, \citet{ting2022} identify correlated abundance residuals that are unexplained by observational uncertainties, indicative of additional nucleosynthetic processes that standard disk CCSN and SNIa enrichment cannot explain.
 Results from G22 and W22 support this conclusion, and both works attempt to add additional processes to their models to account for non-CCSN and non-SNIa enrichment, though in a very restrictive manner.
+Other sources of abundance scatter, such as stochastic sampling of the IMF, IMF variations, and bursty star formation history could also cause deviations away from a two-process model \citep{belokurov2018, griffith2023}.
 
-\ejg{Add paragraph about how little work has been done to optimize stellar abundances to solve for enrichment processes in a more data-driven way.
-\citet{casey2019} apply a clustering algorithm to GALAH DR2 data, identifying latent factors corresponding to 6 processes.
-Difficult to interpret and breaks down with more data.}
+To date, survey abundances have not been fully exploited to create a data-driven model of nucleosynthesis.
+While works such as \citet{ting2012}, \citet{casey2019}, and \citet{ratcliffe2022} effectively use clustering algorithms to identify elements with like sources and reduce abundance dimensionality, the results are difficult to translate into a model of nucleosynthesis.
+Clustering components can be linked to nucleosynthesis sources and enrichment history, but have not yet been be used to describe the enrichment of a single star.
 
 In this work, our main innovations are to relax the assumptions made in G22 and W22, to be more agnostic about the nucleosynthetic processes, and to be more principled with the measurements or inferences from data.
-The benefit we will gain from this is better performance at fitting the data.
-The cost we might pay is a possible reduction in interpretability.
-We'll come back to all that at the end.
+In the $K$ Process Model (\name{}), we find the intersection between reliable facts about nucleosynthesis and good abundance measurements to build an edifice of Galactic enrichment.
+The parameters output by our model can be used as de-noised abundance label to sharpen relationships between abundances and stellar parameters.
+\ejg{Add more about high-quality metallicity labels?
+Hogg to edit this paragraph.}
 
-\ejg{Placeholder.
-We attempt to find the intersection between reliable facts about nucleosynthesis and good abundance measurements.
-We are trying to build an edifice of nucleosynthesis on a small number of facts.
-Because Mg is well-measured and well-understood theoretically, it's a good foundation for our model.
-We have a degeneracy with Fe because we don't have a nucleosynthesis fact.}
+This paper is organized as follows.
+In Section~\ref{sec:model} we present the assumptions and the implementation of \name{}.
+In Section~\ref{sec:data} we describe the APOGEE data sample employed in this paper.
+We apply \name{} to the APOGEE data in Section~\ref{sec:fiducial} and compare our results to those of W22 in Section~\ref{subsec:w22}.
+In Section~\ref{sec:variations} we explore variations from the fiducial model, changing our assumptions about Fe production as well as the number of model components.
+Finally, we discuss and summarize our results in Section~\ref{sec:discussion}.
 
-In Section~\ref{sec:data} we describe the APOGEE data samples fit in this paper.
-In Section~\ref{sec:model} we outline our $K$-process model, the assumptions we make, and our implementation of the optimization routine.
-We apply the data-driven $K$-process model to the W22 APOGEE sample and present our findings in Section~\ref{sec:results_W22}.
-\ejg{Add ending discussion sections...}
+\section{The $K$-Process Model}\label{sec:model}
 
-\section{Data Samples}\label{sec:data}
+As in W22 and G22, we propose that all stellar abundances can be generated by a combination of $K$ nucleosynthetic processes.
+In this picture, each element has $K$ metallicity-dependent process vector components that are shared across the full stellar sample, while each star individually has $K$ process amplitudes, which apply across all elements, such that
+\begin{equation}\label{eq:mij_k}
+    m_{ij} = \log_{10} \, \sum^K_{k=1} A_i^k \, q_{k,j}^Z ~,
+\end{equation}
+where stars are labeled by $i$ and elements are labeled by $j$.
+Each star $i$ has $K$ process amplitudes ($A^k_i$)
+and each element $j$ has $K$ process vector components ($q_{k,j}^{Z}$).
+The $m_{ij}$ value is the model expected logarithmic abundance of element $j$ in star $i$. In this model, we put forth the following set of assumptions:
 
-In this paper, we employ stellar abundances from APOGEE DR17 \citep{abdurrouf2022}, part of SDSS-IV \citep{majewski2017}.
+\paragraph{1. $K$ processes}
+All elements on the periodic table are produced by a combination of nucleosynthetic processes such as CCSN, SNIa, AGB stars, and merging neutron stars \citep{johnsonja2020}.
+The majority of $\alpha$, light odd-Z, and Fe-peak elements (the elements observed by APOGEE) are dominantly produced by $K=2$ sources, with one being a prompt process or mix of prompt processes, and one being a delayed process or a mix of delayed processes.
+This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful data-driven models (e.g., G22, W22, \citealp{ting2022}).
+In this paper we therefore assume that $K \geq 2$, though \name{} could be implemented with $K=1$.
+\hogg{This assumption says too much; we could dial this back.}
+
+\paragraph{2. Linearity}
+At every metallicity, the (X/H) abundances of a star can be expressed as a linear combination of $K$ processes.
+These processes themselves will depend on metallicity, but a linear sum is sufficient to explain all element abundances at any overall metallicity.
+Because yields depend on stellar masses and progenitor structure, and because different stars can get to their metallicities by different histories, this assumption must be at least slightly wrong in detail.
+
+\paragraph{3. Non-negativity}
+All process vector components for all elements are non-negative and all process amplitudes are non-negative.
+This assumption implies that the elements considered here are only produced, and not ever destroyed, by the $K$ processes (relative to hydrogen).
+This makes the model similar to a non-negative matrix factorization (\citealt{nnmf} \ejg{Hogg add citation}).
+In \name{}, this assumption is enforced by requiring that the process vector components and amplitudes are always greater than or equal to zero, such that
+\begin{equation} \label{eq:constraint_zero}
+    q_{k,j}^Z \geq 0 \; \forall \; Z,k,j \quad \text{and} \quad A_i^k \geq 0 \; \forall \; k,i ~.
+\end{equation}
+
+\paragraph{4. Mg production}
+All Mg is produced in a prompt process and no other processes contribute to its production.
+This is substantiated by theoretical yields where Mg is purely produced by prompt CCSN \citep[e.g.,][]{anderson2019, rybizki2017}.
+This assumption (along with non-negativity) breaks a set of symmetries in the process space and makes the processes quasi-interpretable in terms of nucleosynthesis sources.
+Because such a prompt process is likely dominated by CCSN \citep[e.g.,][]{andrews2017}, we label the first process with ``CC''.
+
+In \name{}, this assumption is enforced by fixing the Mg process vector components such that
+\begin{equation}\label{eq:qcc_mg_solar}
+    q_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1, \quad q_{k>1,{\rm Mg}}^{\,Z_{\odot}} = 0
+\end{equation}
+at solar metallicity and 
+\begin{equation}\label{eq:qcc_mg_z}
+    q_{{\rm CC, Mg}}^{\,Z} = q_{{\rm CC, Mg}}^{\,Z_{\odot}}, \quad q_{k>1, {\rm Mg}}^{\,Z} = q_{k>1, {\rm Mg}}^{\,Z_{\odot}}
+\end{equation}
+at all other metallicities.
+
+\paragraph{5. Fe production}
+Fe is produced through a combination of a prompt and delayed process.
+Because the delayed process is likely dominated by SNIa \citep[e.g.,][]{andrews2017}, we label the delayed process with ``Ia''\footnote{While other enrichment channels with similar timescales may be included in the respective processes, the ``CC'' and ``Ia'' naming convention conforms to the choices in W22 and G22, and avoids the possible confusion of process numbers (1 and 2) with supernovae type (II and Ia).}.
+While the prompt process constraint (Mg) is grounded in nucleosynthesis theory, there is no equivalent nucleosynthesis fact to constrain the delayed process.
+To break model degeneracies, we also fix the Fe process vector components such that
+
+\begin{equation}\label{eq:qcc_fe_solar}
+    q_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.4, \quad q_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 1 - q_{{\rm CC, Fe}}^{\,Z_{\odot}} \quad q_{k>2,{\rm Fe}}^{\,Z_{\odot}} = 0
+\end{equation}
+at solar metallicity and 
+\begin{equation}\label{eq:qcc_fe_z}
+    q_{{\rm CC, Fe}}^{\,Z} = q_{{\rm CC, Fe}}^{\,Z_{\odot}},  \quad 
+    q_{{\rm Ia, Fe}}^{\,Z} = q_{{\rm Ia, Fe}}^{\,Z_{\odot}} \quad 
+    q_{k>2, {\rm Fe}}^{\,Z} = q_{k>2, {\rm Fe}}^{\,Z_{\odot}}
+\end{equation}
+at all other metallicities.
+This assumption places a star with purely prompt enrichment on the low-metallicity $\mgfe$ plateau near 0.4 dex, in agreement with APOGEE observations but in contention with recent results from \citet{conroy2022} which places the $\mgfe$ plateau near 0.6 dex.
+We explore the impact of different $\qccFe$ assumptions in Section~\ref{subsec:qccFe}.
+
+\paragraph{6. Metallicity dependence}
+We permit the process vector components for all elements other than Mg and Fe to float as a function of metallicity.
+The variation is parameterized by a linear spline in log-process space, attached to a set of variable control points.
+We assume that a particular set of hard-coded knots are sufficient to capture the metallicity dependence.
+\hogg{This could be mentioned in passing in the discussion where you talk about model improvements.}
+
+\paragraph{7. APOGEE abundances and uncertainties}
+We assume that the APOGEE abundances and uncertainties can be used for this project.
+This is not the same as assuming that they are correct, but rather that it is possible and useful to build an interpretable model to explain them.
+We describe the potential data systematics in Section~\ref{sec:data}.
+The APOGEE errors are likely slightly underestimated for some element measurements, so we add softening parameter $Q$ to inflate the errors (see Equation~\ref{eq:inflate_ivar}).
+\hogg{Make this more positive about apogee}
+
+\paragraph{8. Robust likelihood function}
+The observed value of [X/H] can be described as the $K$ process expectation plus observational noise and/or other sources of intrinsic abundance scatter that are not included in this model:
+\begin{equation} \label{eq:xh}
+    \xh_{ij} = m_{ij} + \text{noise} ~,
+\end{equation}
+where $m_{ij}$ is the expectation value given in Equation \ref{eq:mij_k} for star $i$ and element $j$.
+The expression in Equation \ref{eq:xh} can be thought of as the key assumption underlying our likelihood function.
+In detail the (negative two times the) log likelihood function is given by a chi-squared ($\chi^2$) objective
+\begin{equation}
+    \chi^2 = \sum_{ij} \, \frac{1}{\sigma_{ij}^2} \, (\xh_{ij} - m_{ij})^2 + Q ~,
+\end{equation}
+where $1/\sigma_ij^2$ is the (robust; see below) inverse variance on measurement $ij$,
+and $Q$ is a light regularization that depends on the parameters.
+
+Because we don't want to be too drawn or influenced by outlier points, we don't use the observed errors $\sigma_{{\rm obs},ij}$ in the likelihood, but instead we soften them in the spirit of iteratively reweighted least squares (HOGG CITE):
+\begin{equation}\label{eq:inflate_ivar}
+    \frac{1}{\sigma_{ij}^2} = \frac{Q^2/\sigma_{{\rm obs},ij}^2}{Q^2 + (\xh_{ij} - m_{ij})^2 /\sigma_{{\rm obs},ij}^2 },    
+\end{equation}
+where $Q$ is a softening parameter, which is set to $Q=5$.
+
+\paragraph{9. Implementation and optimization} 
+With the above assumptions in place, the likelihood function can be optimized to a set of stellar abundances.
+The model is initialized at the Mg and Fe process vector components from Equations~\ref{eq:qcc_mg_solar} --~\ref{eq:qcc_fe_z}.
+It subsequently optimizes the process amplitudes (dubbed the $A$-step) using only Mg and Fe at fixed process vector components, and then optimizes the process vector components (dubbed the $q$-step) for all elements at fixed process amplitudes.
+The $A$-step and $q$-step are alternated, repeating 48 rounds of optimization and updating the best-fit parameters when the objective function improves.
+We find few differences in the best-fit parameters when we decrease the number of iterations to 32, indicating that the model quickly finds a good solution.
+In detail the optimizations are performed with a nonlinear $\chi^2$ minimization algorithm (Gauss--Newton nonlinear least-squares) from \texttt{jaxopt}\footnote{\url{https://jaxopt.github.io/}}.
+
+\bigskip
+\name{} mirrors the two-proccess model from prior work (G22, W22) but, unless otherwise noted, the assumptions weaker, there is a likelihood function in play, and the implementation is more general.
+In particular, we don't assume anything about the relationships between the process vector components and the morphologies of observed element-abundance ratio diagrams.
+
+\section{Data}\label{sec:data}
+
+In this paper, we employ stellar abundances from APOGEE DR17 \citep{abdurrouf2022}, part of the SDSS-IV \citep{majewski2017}.
 The APOGEE survey obtains high-resolution ($R\sim22,500$) near-infrared (IR) observations \citep{wilson2019} for stars in the Galactic disk, halo, bulge, and nearby satellites/streams.
 Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile.
-Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and parameters are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline][]{holtzman2015, garcia2016}.
+Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and abundances are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline;][]{holtzman2015, garcia2016}.
 See \citet[][DR16]{jonsson2020} and Holtzman et al.
-(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citep{zasowski2013, zasowski2017, santana2021} for a discussion of survey targeting.
-\ejg{Is the DR17 paper out yet?}
+(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017} and \citet{santana2021} for a discussion of survey targeting.
 
-APOGEE DR17 reports stellar parameters including $\teff$ and $\logg$ as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, Ti, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
+APOGEE DR17 reports stellar parameters, including $\teff$ and $\logg$, as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, \ion{Ti}{1}, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
 Among these elements and ions, some are measured more precisely than others.
 We exclude Ti from our analysis as there are large differences between the abundances derived from the \ion{Ti}{1} and \ion{Ti}{2} lines \citep{jonsson2020}.
-We also exclude P, as the P abundances are measured from a few very weak spectra features, and the abundance distribution displays strong artifacts \citep{jonsson2020}.
-Among the remaining elements, we note the following concerns:
+We also exclude P and V, as the P abundances are measured from a few very weak spectra features and V abundances are one of the least precise and least accurate labels \citep{jonsson2020}.
+Both P and V display strong abundance artifacts and large scatter.
+Among the remaining elements, we note the following concerns: weak Na spectral features, large abundances scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, strong unaccounted for NLTE effects on Mn abundances, and large abundance scatter in Co and Ce---both derived from one line.
+Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
+For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
+
+For our stellar sample, we select a subset of APOGEE DR17 stars with the goal of minimizing statistical errors from poor observations and systematic errors from abundance trends with $\teff$ and/or $\logg$ while preserving a sufficient number of stars to conduct a meaningful statistical analysis across the Galactic disk.
+To remove poor quality data points, we require ASPCAP flags \texttt{STAR\_BAD} and \texttt{NO\_ASPCAP\_RESULT} equal zero.
+We only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}.
+In addition to these quality cuts, we apply the following sample selection:
 \begin{itemize}
 \itemsep0em
-    \item Na - Spectral features are weak, one of the least precise elements in APOGEE (but matches optical data pretty well)
-    \item S - Large abundance scatter in observations and no verification with optical data
-    \item Cr - Significant systematic artifacts at super solar metallicity \citep{griffith2021a}
-    \item Mn - Strong NLTE effects exist that are not taken into account
-    \item Co - Abundance derived from one line, causing larger abundance scatter
-    \item Ce - Abundance derived from one line. DR17 is the first time Ce abundances have been included in APOGEE data products. 
-    \item Al,  V, and Mn require large offsets to place solar metallicity stars at solar [X/Fe].
+    \item $\mgh > -0.75$
+    \item S/N $\geq 200$
+    \item $\logg = 1-3$ dex
+    \item $\teff = 4000-5200$ K.
 \end{itemize}
-\ejg{Will want to condense list for paper. Add a short description of some abundance systematics that we see re \citet{jonsson2020} and \citet{griffith2021a}}.
+To eliminate red clump (RC) stars, which show abundance variations from the RGB sample \citep{vincenzo2021a}, we cross-match with and remove stars that appear in the APOGEE RC VAC \citep{bovy2014}.
+These cuts result in a sample of 48,659 stars.
 
-In this paper, we will explore two subsamples of APOGEE DR17 data: (1) the W22 sample, optimized to minimize statistical and systematic errors while probing a large portion of the Galactic disk, and (2) a sample with less stringent cuts, but better coverage of the low-metallicity ([Fe/H] $< -0.5$) disk.
-
-\subsection{The W22 Sample}
-
-W22 select a subset of APOGEE DR17 stars with the goal of minimizing statistical errors from poor observations and systematic errors from abundance trends with $\teff$ and/or $\logg$ while preserving a sufficient number of stars to conduct a meaningful statistical analysis across the Galactic disk.
-To remove poor quality data points, W22 require ASPCAP flags \texttt{STAR\_BAD} \texttt{NO\_ASPCAP\_RESULT} equal zero and remove all stars with \texttt{FE\_H\_FLAG} or \texttt{MG\_FE\_FLAG} set.
-They only include stars from the main survey sample (\texttt{EXTRATARG} = 0), and use named abundances (\texttt{X\_FE}), as recommended by \citet{jonsson2020}.
-In addition to these quality cute, W22 apply the following sample selection cuts:
-\begin{itemize}
-\itemsep0em
-    \item $R=3-13$ kpc, $|Z| \leq 2$ kpc (distances from \citet{leung2019})
-    \item $-0.75 \leq \mgh \leq 0.45$
-    \item S/N $\geq 200$ for $\mgh > -0.5$ and S/N $\geq 100$ for $\mgh < -0.5$
-    \item $\logg = 1-2.5$ dex
-    \item $\teff = 4000-4600$ K
-\end{itemize}
-By selecting stars from a small range of $\logg$ and $\teff$, they eliminate the red clump stars and minimize stellar parameter-dependent abundance trends \citep[see][]{griffith2021a}.
-The cuts result in a sample of 34,410 stars.
-
-W22 present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, and Ce.
-While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
-W22 consider C+N as an element in their analysis, taking [(C+N)/H] to be
+We present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, Mn, Co, and Ce.
+In the analysis of each element, X, we drop stars with \texttt{X\_FE\_FLAG} (maximum of $\sim 700$ for Ce).
+While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge-up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
+As in W22, we consider C+N as an element, taking [(C+N)/H] to be
 \begin{equation}
@@
 using logarithmic solar abundances for C (8.39) and N (7.78) from \citet{grevesse2007}.
+We further adopt the error on the [C/Fe] abundance as the error on [C+N/Fe], since C typically dominates in the abundance ratio.
 
-\ejg{W22 use X/Fe error from APOGEE and don't convert it to X/Mg....Use C/Fe error for the C+N value because the ratio is mostly C... Need error discussion here and in next section.}
+We plot the distributions of all abundances in [X/Mg] vs. [Mg/H] for our sample in the first column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
 
-In the analysis of each element, X, stars with \texttt{X\_FE\_FLAG} are dropped (maximum of $\sim 560$ for Ce).
-We plot the distribution of abundances in [X/Mg] vs.
-[Mg/H] in Figure~\ref{fig:w22_xmg}.
-All elemental abundances have zero-point offsets applied and have been de-trended for correlations with $\teff$, as in W22 (see their Table 1).
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/all_param1.pdf}
+    \caption{Abundance distributions and \name{} parameters for C+N, $\alpha$, and light odd-$Z$ elements.
+First column: observed abundance distributions in [X/Mg] vs.
+[Mg/H].
+Second column: The predicted [X/Mg] vs.
+[Mg/H] abundance distribution of the fiducial plus estimated noise.
+Third column: process vector components $\qcc$ (purple) and $\qIa$ (orange) from this work (G23, solid, dark lines) and W22 (light, dashed lines).
+Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial model.
+We plot the median $\fcc$ values of the low-Ia (orange square) and high-Ia (purple circle) populations in the solar metallicity bin from W22 for comparison.}
+    \label{fig:all_param1}
+\end{figure*}
 
-\begin{figure}[htb!]
+\begin{figure*}[htb!]
     \centering
-    \includegraphics[width=\textwidth]{Figures/W22_xmg.pdf}
-    \caption{W22 stellar abundance distributions. The number in the top right corner indicates the number of stars used in the analysis of that element. Elements are ordered by atomic number.}
-    \label{fig:w22_xmg}
-\end{figure}
+    \includegraphics[width=\textwidth]{Paper/Figures/all_param2.pdf}
+    \caption{Same as Figure~\ref{fig:all_param1}, but for Fe-peak elements and Ce.}
+    \label{fig:all_param2}
+\end{figure*}
 
-\subsection{Our Sample}
+\section{The Fiducial Model} \label{sec:fiducial}
 
-\ejg{Not sure if this should go here or after we discuss the success of the K-process model on W22 data...}
+We fit the APOGEE sample with our fiducial model of $K=2$, such that
+\begin{equation}\label{eq:m_ij}
+    m_{ij} = \log_{10}(A_i^{\rm CC} \, q_{{\rm CC},j}^Z + A_i^{\rm Ia} \, q_{{\rm Ia},j}^Z)
+\end{equation}
+with the assumptions from SEction~\ref{sec:model}.
+This fit produces process vector components $\qcc$ and $\qIa$ as a function of $\mgh$ for each element and process amplitudes $\Acc$ and $\AIa$ for each star.
+From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted $K=2$ process abundances.
 
-While the W22 sample presented above is a good first test case of \name, we are interested in the behavior of our model when applied to a wider sample of data, in particular extending the metalicity range to lower values of [Mg/H].
-To construct this sample, we apply the same quality cuts as taken by W22 (\texttt{STAR\_BAD} = 0, \texttt{NO\_ASPCAP\_RESULT} = 0, \texttt{FE\_H\_FLAG} = 0, \texttt{MG\_FE\_FLAG} = 0, and (\texttt{EXTRATARG} = 0).
-We add a cut for stars with the \texttt{ROTATION\_WARNING} flag set.
-We take the following sample selection cuts:
-\itemsep0em
-\begin{itemize}
-    \item S/N $\geq 100$
-    \item $0 < \logg < 2.5$ dex
-    \item $\teff = 4000-4600$ K
-\end{itemize}
-We make no cuts on the Galactic location, including stars from across the Galactic disk and halo, and make no cuts on the [Mg/H] values of our sample.
-The wider $\logg$ ranges expand the sample of giants.
-We select stars in the same small $\teff$ range as W22 to exclude the red clump \citep{vincenzo2021} and cool stars that show abundance artifacts \citep{jonsson2020}.
-Our final sample includes 51,386 stars and extends to [Mg/H]=-2.2.
-As in W22, we only analyze [X/Mg] abundances for stars where the [X/Fe] value is unflagged.
-This has a minimal effect for most elements but reduces the sample size to 49,851 for Ce.
+\subsection{Process Parameters and Fractional Contributions} \label{subsec:parameters}
 
-\ejg{Plus a magnitude cut as a proxy for distance? Right now I have H < 12, but I don't think that the cut impacts the global trends much...}
+We plot the process vector components as a function of $\mgh$ in the third column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
+The process vector components inform us about the relative contribution of prompt and delayed processes to the formation of the elements, as well as the metallicity dependence of the enrichment.
+By definition, $\qccFe=0.4$ at all metallicities.
+For Fe only, we also require $\qccFe + \qIaFe = 1$, implying $\qIaFe=0.6$.
+No such constraints are placed on any other element.
 
-\begin{figure}[htb!]
+In the fourth column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}, we plot the distribution of fractional contributions from the prompt process ($\fcc$) to each element, where
+\begin{equation}\label{eq:fcc}
+    \fcc = \frac{\Acc \, \qcc}{\Acc \, \qcc + \AIa \, \qIa}.
+\end{equation}
+We generally find that the distributions are bimodal, like the observed abundance patterns, as the high-Ia and low-Ia populations have differing fractional contributions from prompt and delayed sources.
+
+We find that the $\alpha$-elements (O, Si, S, Ca) are best fit with $\qcc$ and $\fcc > 0.5$ at all metallicities.
+This is in agreement with theoretical prediction that $\alpha$-elements are dominated by prompt CCSN production \citep[e.g.][]{andrews2017}.
+O, a Mg-like element theoretically purely produced in prompt CCSN, shows $\fcc$ near 1 from $\mgh=-0.75$ to solar.
+At supersolar $\mgh$, the delayed process contributes to O production, driving the $\fcc$ value down to $\sim 0.8$ at $\mgh=0.4$.
+S behaves like O, with almost entirely prompt production up to solar metallicity, after which delayed enrichment contributes more significantly.
+Conversely, we find that Si and Ca are best fit with prompt and delayed enrichment at all metallicities, though the prompt process always dominates.
+For Si, the delayed process appear to increase linearly with $\mgh$, while the Ca delayed enrichment increases from $\mgh$ of $-0.75$ to $-0.1$ and then decreases from $\mgh$ of $-0.1$ to $0.5$.
+
+The process vector components of light odd-$Z$ elements Al and K resemble those of the $\alpha$-elements, such as S.
+Both exhibit $\qcc$ and $\fcc$ near 1 through solar metallicity, with an increase in $\qIa$ and downturn in $\fcc$ at supersolar metallicities (especially for K).
+The behavior of the Na process vector components is more complex, with peaks and troughs in $\qIa$.
+We find that Na has the strongest contributions from the delayed process of all $\alpha$ and light odd-$Z$ elements, with $\qIa \gtrsim 0.5$ at almost all values of $\mgh$ and $\fcc < 0.3$ at $\mgh > 0$.
+The strong delayed contribution to Na is in agreement with findings of W22 and G22, and in tension with theoretical yields \citep[e.g.][]{andrews2017, rybizki2017}.
+
+Unlike $\alpha$ and light odd-$Z$ elements whose delayed production is dominated by SNIa, C and N are thought to be promptly produced in CCSN with additional delayed enrichment from AGB stars \citep[e.g.][]{andrews2017}.
+We find that the prompt and delayed processes both contribute significantly, and nearly equally, across our stellar sample.
+Though theoretical N yields from AGB stars have a strong metallicity dependence \citep{karakas2010, ventura2013, cristallo2015, johnson2022}, we observe only a slight positive metallicity dependence in $\qcc$ and a shallow dip in $\qIa$.
+We find a population of stars with $\fcc$ near 0.9 and a population near 0.4.
+
+The Fe-peak elements (Cr, Mn, Fe, Co, Ni) are thought to be produced through prompt CCSN production and delayed SNIa production \citep[e.g.][]{andrews2017}.
+By construction, $\qccFe=0.4$ and $\qIaFe=0.6$ at all metallicities.
+This produces a bimodal distribution in $\fcc$ similar to that observed in abundances space.
+Because of our choice of $\qccFe$, only a few stars have $\fcc=1$ (see Section~\ref{subsec:qccFe}).
+We instead observe a population with $\fcc$ near 0.8 and a population near 0.4.
+The process vector components and $\fcc$ distribution for Cr and Ni strongly resemble those of Fe.
+All three elements have even atomic numbers.
+At supersolar metallicity, we find that the prompt process dominates Cr production, resulting in an upturn in $\fcc$.
+Conversely, Ni displays a dominant, and increasing, delayed proccess vector component at supersolar metallicities.
+The process vector components for Mn and Co (odd atomic numbers) show a complex metallicity dependence, more resembling that of Na.
+Both elements display a strong delayed process, with the Mn $\qIa > 0.5$ at all metallicities and $> 1$ for $\mgh > 0.1$.
+Mn is the only element for which $\fcc$ decreases to 0 for $\mgh \gtrsim 0.2$.
+
+Finally, we find that the delayed process dominates Ce production at intermediate metallicity, with $\qIa$ increasing up to $\mgh \approx -0.2$ and then decreasing to nearly 0 at $\mgh \approx 0.3$.
+The Ce $\fcc$ values are clustered near 0.25 around $\mgh$ of 0.2, then increase such that the abundances are almost entirely dominated by prompt enrichment at high metallicity.
+
+In addition to process vector components, each star is fit with a prompt and delayed process amplitude, $\Acc$ and $\AIa$ respectively.
+All elemental abundance are used in the calculation of these amplitudes, so they can be interpreted as ``de-noised'' abundance labels.
+The value of $\Acc$ traces the metallicity (specifically $\mgh$) while the ratio of $\AIa/\Acc$ traces the $\femg$ abundance.
+In the left panel of Figure~\ref{fig:As} we plot the distribution of $\AIa/\Acc$ vs.
+$\Acc$.
+We find a bimodal distribution, similar to the Tinsley-Wallerstein diagram ($\mgfe$ vs.
+$\feh$, \citealp{wallerstein1962, tinsley1979, tinsley1980}), as was found in W22 and G22.
+We stress that the presence of the abundance bimodality was not fed into our model, and yet it is recovered in the best-fit process amplitudes.
+The stars with larger $\AIa/\Acc$ values correspond to the high-Ia population, and those with low $\AIa/\Acc$ correspond to the low-Ia population.
+While in the Tinsley-Wallerstain diagram the two populations blend together at high-metallicity, they are more distinguishable in amplitude space.
+To further show this, we plot $\AIa/\Acc$ vs.
+$\mgh$ in the right panel of Figure~\ref{fig:As}.
+The high-Ia and low-Ia populations are clearly seperable through $\mgh$ of 0.4.
+
+\begin{figure*}[htb!]
     \centering
-    \includegraphics[width=\textwidth]{Figures/xmg.pdf}
-    \caption{Stellar abundance distributions for our wider stellar sample.
-The number in the top right corner indicates the number of stars used in the analysis of that element.
-Elements are ordered by atomic number.}
-    \label{fig:w22_xmg}
-\end{figure}
+    \includegraphics[width=.9\textwidth]{Paper/Figures/As.pdf}
+    \caption{Left: distribution of $\AIa/\Acc$ vs.
+$\Acc$ for the fiducial model.
+Right: distribution of $\AIa/\Acc$ vs.
+$\mgh$.
+In both panels we can clearly see the bimodality to high values of $\Acc$ and $\mgh$.}
+    \label{fig:As}
+\end{figure*}
 
-The expansion of the data sample does introduce abundance systematics that the W22 selection sought to exclude.
-As discussed in \citet{jonsson2020} and \citet{griffith2021a}, APGOEE DR16 and DR17 suffer from poorly understood abundance artifacts, such as a ``finger'' in [$\alpha$/M] and low-[X/Fe] banding in elements such as Al and Ni.
-In our expanded data set, we observe potential abundance artifacts in Al, K, V, and Cr.
-\ejg{Add more here.
-Stricter temperature cut helped to remove the artifacts...}
+With the optimized process parameters in hand, we can use Equation~\ref{eq:xh} to calculate predicted abundances for the fiducial model---the abundances our stellar population would have if the model assumptions are correct and only one prompt and one delayed process contribute.
+To simulate observational noise, we add an error drawn from a Gaussian distribution with $\sigma$ equal to the reported error on each abundance for each star.
+In Figure~\ref{fig:all_param1} and~\ref{fig:all_param2} we plot the predicted abundances plus estimated noise in the second columns.
+These distributions can be compared the the observed abundance distribution in the first columns.
 
-\ejg{Should check the spatial distribution of the final sample. Need to decide if we will also apply zero point offsets}
+Overall, the fiducial model successfully reproduces the observed abundance distributions.
+It is capable of capturing metalicity dependences and bimodality.
+The predicted abundances plus estimated noise are not, however, able to reproduce the observed abundance scatter.
+This is especially noticeable at low-metallicity for C+N, Na, Al, K, Co, and Ce.
+For these elements the scatter in the observed abundance distribution is much larger than in the predicted distribution, suggesting that either the $K=2$ model is insufficient or that the APOGEE scatter is underestimated.
 
-\ejg{Also need to add discussion that almost all stars below [Mg/H] of -0.75 appear chemically accreted...}
+\subsection{Comparing to W22}\label{subsec:w22}
 
-\section{Methods and Models}\label{sec:model}
+As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, \name{} is based upon the two-process model developed in W19 and W22, but with increased flexibility and no forced dependence upon the [Fe/Mg] vs.
+[Fe/H] bimodality or population abundance trends.
+Further, the \name{} utilizes all stellar abundances in the optimization of $\Acc$ and $\AIa$, where as only Mg and Fe are used in W19 and only Mg, O, Si, Ca, Fe, and Ni in W22.
 
-We model each star as the sum of a CCSN and SNIa process vector (constant for all elements) and CCSN/SNIa amplitude such that
+In the fiducial model, we adopt $K=2$, as in W22, but assume $\qccFe = 0.4$, 0.1 dex lower than the $\qccFe$ value assumed in W22.
+In practice, this moves the implied ``pure'' CCSN enrichment plateau from $\femg=-0.3$ to $\femg=-0.4$ (though the W22 plateau value is determined \textit{after} they apply a global offset of +0.05 to all $\femg$ abundances).
+Because our model is non-negative, it requires a lower $\qccFe$ to correctly model the stars on the $\femg$ plateau, where as W22 assigns stars with $\femg < -0.3$ negative $\AIa$ values.
 
-\begin{equation}
-    m_{ij} = \log_{10}(A_i^{\rm CC} \vec{q}_{{\rm CC}, j}^{\,Z} + A_i^{\rm Ia} \vec{q}_{{\rm Ia}, j}^{\,Z}) 
+While our stellar samples and model assumptions differ, we plot the W22 $\qcc$ and $\qIa$ vector components as well as the W22 solar metallicity $\fcc$ values in of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2} for comparison with our fiducial model.
+We generally observe similar behavior between \name{} and W22.
+Our $\qIa$ vector components tend to be $\sim 0.1$ greater than those of W22 for elements with significant delayed contributions because of our differing $\qccFe$ assumptions.
+The metallicity dependencies agree for most elements, with small variations at the high-$\mgh$ end for O, Al, K, and Ce.
+We also see good agreement between the \name{} and W22 solar metallicity $\fcc$ values, with the W22 points slightly offset to larger values for elements with significant delayed contributions.
+
+To compare the accuracy of the models' abilities to reproduce the observed abundances, we identify a subset of $\sim 23,000$ stars in both our sample and the W22 sample.
+We calculate the predicted abundances for each star under \name{} and the two-process model, then determine the $\chi^2$ value of the fits for each star (summing over the elements) and for each element (summing over the stars).
+We plot the cumulative stellar $\log(\chi^2)$ distribution and the total $\chi^2$ for each element in the right and left panels, respectively, of Figure~\ref{fig:comp_w22}.
+It is important to note that in the calculation of the W22 model residuals, we do not apply the temperature corrections discussed in Section 5.1 of W22.
+We find that, overall, the $\log(\chi^2)$ decreases between the W22 two-process model and our $K$-process model, an indication that we better predict the stellar abundances.
+When looking at each element individually, we find that we better predict C+N, Na, K, Ni, Mn, Co, and Ce, with major improvements to C+N and Mn.
+Our fiducial model is significantly worse at predicting Mg, Ca, and Fe than the W22 model, three of the six elements that W22 employ to fit the process amplitudes.
+Because \name{} uses all elements in its optimization, Mg, Ca, and Fe are effectively de-weighted relative to the W22 model, while C+N and Mn influence the model parameters.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/comp_w22.pdf}
+    \caption{Left: cumulative distribution of $\log \chi^2$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line). Right: $\chi^2$ per element for the same model fits. }
+    \label{fig:comp_w22}
+\end{figure*}
+
+We note that our fiducial model is fit to a stellar sample that spans a wider range of $\teff$ and $\logg$ than the W22 sample.
+If we repeat our analysis on the W22 stellar sample with $\qccFe=0.5$ we almost perfectly recover the W22 process vector components, with small deviations at $\mgh>0.1$, and more substantially improve upon the stellar and elemental $\chi^2$ values.
+Most notably, \name{} is better able to predict the abundances of stars with $\mgh>0$, where the high-Ia and low-Ia sequences blend together and the W22 categorization of high-Ia and low-Ia stars may be incorrect.
+
+\section{Variations Away from the Fiducial Model} \label{sec:variations}
+
+\subsection{Choice of $\qccFe$} \label{subsec:qccFe}
+
+While \name{} is flexible, it still requires assumptions to break model degeneracies (see Section~\ref{sec:model}).
+Specifically, it requires an element with ``known'' $\qcc$ and an element with known $\qIa$ to constrain each process.
+\ejg{Hogg edit this paragraph.} For the prompt process, we ground our assumption in the nucleosynthetic theory that Mg is a pure CCSN element \citep[e.g.,][]{andrews2017}.
+Unfortunately there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
+In order to regularize the delayed process, we choose to fix the Fe process vector components, making unsubstantiated assumptions about Fe enrichment.
+
+In the fiducial model, we choose $\qccFe = 0.4$ as this parameter choice is able to reproduce the observed [Fe/Mg] vs.
+[Mg/H] abundance distribution, as discussed in Section~\ref{subsec:parameters}.
+This choice impacts the predicted abundances as well as the implied $\fcc$ values of each star.
+Because our model is non-negative, the choice of $\qccFe$ sets the minimum [Fe/Mg] value attainable by our model ($\log_{10}(\qccFe)$).
+In this section, we explore the implications of different $\qccFe$ assumptions, varying the zero point and metallicity dependence ($\dqccFe$).
+In Figure~\ref{fig:qccFe_FeMg}, we plot the minimum [Fe/Mg] as a function of $\mgh$ for the $\qccFe$ and $\dqccFe$ parameters we explore.
+With a $\dqccFe=0.0$, we choose $\qccFe=0.5$ (the W22 value), 0.45 (approximate plateau value at $\mgh=-0.75$), 0.4 (the fiducial value that skirts the edge of the distribution), and 0.35 (captures almost all stars).
+With a $\dqccFe=0.15$, which roughly matches the slope of the low-Ia sequence at intermediate metallicity, we choose $\qccFe=0.5$ (passes through the center of the low-Ia density), 0.4 (skirts the edge of the distribution), and 0.35 (captures almost all stars).
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMg.pdf}
+    \caption{Minimum [Fe/Mg] value attainable for $\qccFe$ and $\dqccFe$ assumptions.
+Left: For $\dqccFe=0$ with $\qccFe=0.5$, 0.45, 0.4, and 0.35 (light to dark purple).
+Right: For $\dqccFe=0.15$ with $\qccFe=0.5$, 0.4, 0.35 (light to dark orange).}
+    \label{fig:qccFe_FeMg}
+\end{figure*}
+
+We repeat the optimization of the \name{} with $K=2$ and these $\qccFe$ assumptions.
+In Figure~\ref{fig:qccFe_FeMgpred}, we plot the resulting predicted abundance distributions plus estimated noise.
+We do not plot the prediction for the fiducial model ($\qccFe=0.4$, $\dqccFe=0.0$), as this is shown in Figure~\ref{fig:all_param2}.
+Both models with $\qccFe=0.5$ fail to reproduce the shape and width of the low-Ia abundance distribution.
+They instead predict a much thinner sequence that is flat for $\dqccFe=0.0$ or slightly inclined for $\dqccFe=0.15$.
+The model with $\qccFe=0.45$ and $\dqccFe=0.0$ is better, but still predicts a low-Ia abundance distribution that is too thin, flat, and dense.
+The other four models ($\qccFe=0.35$ and $\qccFe=0.4$ with $\dqccFe=0.0$ and $\dqccFe=0.15$) predict an abundance distribution that strongly resembles the observed.
+There are minor differences in the low [Fe/Mg] and low [Mg/H] region, but it is difficult to tell by eye which model is best.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMgpred.pdf}
+    \caption{Predicted [Fe/Mg] vs.
+[Mg/H] abundance distributions plus estimated noise for models with $\dqccFe=0.0$ (top row) and $\dqccFe=0.15$ (bottom row).
+The $\qccFe$ value increase from left to right from 0.35 to 0.5.
+$\qccFe$ and $\dqccFe$ parameters are listed in each panel.}
+    \label{fig:qccFe_FeMgpred}
+\end{figure*}
+
+To better assess the goodness of fit of each model, we calculate the average $\chi^2$ value per star.
+The models with $\qccFe$ of 0.5 and 0.45, regardless of $\dqccFe$, have an average $\chi^2$ per star $>90$ while the models with $\qccFe$ of 0.4 and 0.35 have an average $\chi^2$ per star $< 55$.
+In both the metallicity independent and metalicity dependent cases, the models with $\qccFe=0.4$ have the lowest average $\chi^2$ per star, at 54.54 and 54.47, respectively, though the models with $\qccFe=0.35$ have a $\chi^2$ that is only greater by $\sim0.1$.
+Of the seven models explored here, the case with $\qccFe=0.4$ and $\dqccFe=0.15$ has the lowest average $\chi^2$ per star, indicating that the Fe abundances are best fit by a metallicity dependent prompt process.
+
+Though the $\qccFe= 0.4$ and 0.35 models are similar in terms of their goodness of fit, their nucleosynthesis implications are more significant.
+In Figure~\ref{fig:qccFe_fcc}, we plot the median value of $\fcc$ (Equation~\ref{eq:fcc}) for the low-Ia population at solar metallicity ($-0.05 < \mgh < 0.05$), where low-Ia stars are defined by
+\begin{equation}\label{eq:lowIa}
+\begin{cases}
+\mgfe > 0.12 - 0.13 \, \feh,    & \feh<0 \cr
+\mgfe > 0.12,               & \feh>0, \cr
+\end{cases}
 \end{equation}
+as in W19, W22, and G22.
+We only show the median $\fcc$ values for the models with $\dqccFe=0.0$ as the solar metallicity median $\fcc$ values for the metallicity dependent models are almost identical for matching values of $\qccFe$.
+We find that the choice of $\qccFe$ has little impact on the median $\fcc$ values of elements dominated by CCSN enrichment (e.g.
+O, S, Al, K).
+As the delayed contribution increases, the median elemental $\fcc$ values decrease more significantly with decreasing $\qccFe$.
+The choice of $\qccFe$ most impacts the median $\fcc$ values for Na, Cr, Fe, Mn, and Ce, with the median $\fcc$ for Mn decreasing from 0.42 for $\qccFe=0.5$ to 0.22 for $\qccFe=0.35$.
+Because the $\qccFe$ value sets the prompt enrichment plateau, a lower $\qccFe$ model implies a lower $\fcc$ value.
 
-where the observed value of $\xh$ can be described as the model plus observational noise and/or contributions from an additional non-CCSN/SNIa process:
+While the high $\qccFe$ model can likely be ruled out due to poorness of fit, the true $\qccFe$ value and its metallicity dependence are unknown.
+It is therefore important not to over-interpret the specific $\fcc$ values of a given model.
+The $\fcc$ parameter can provide qualitative descriptions of which elements have more or less prompt/delayed enrichment, but the exact values are uncertain.
 
-\begin{equation}
-    \xh_{ij} = m_{ij} + \text{noise}.
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_fcc.pdf}
+    \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for \name{} with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.}
+    \label{fig:qccFe_fcc}
+\end{figure*}
+
+\subsection{Increasing the Number of Processes} \label{subsec:k=4}
+
+In our fiducial model, we adopt $K=2$ with the two processes representing prompt, CCSN-like enrichment and delayed, SNIa-like enrichment.
+While a $K=2$ model can well describe the stellar abundances (e.g., Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}), the abundance residuals cannot be explained by observational noise alone and hold information about the intrinsic variations from a $K=2$ model (G22, W22, \citealp{ting2022}).
+Potential sources of such scatter include metallicity-dependent SN yields with a bursty star formation history, environmental variations in the IMF, stochastic sampling of the IMF, and more than two distinct processes (e.g., AGB stars, merging neutron stars, and unique classes of SNIa) with different time delays for enrichment \citep[e.g.][]{belokurov2022, griffith2023}.
+
+In this section, we will explore the impact of adding additional processes to our model, increasing from $K=2$ to $K=4$.
+Our goal is to demonstrate the potential of using \name{} to capture more of the observed abundance diversity.
+Because \name{} is sensitive to enrichment with different time delays, adding components could be interpreted as adding sources with distinct enrichment time scales.
+For example, if AGB stars and SNIa enrich with the \textit{same} time delay, the model would fit both sources in one delayed component.
+If AGB and SNIa enrich with \textit{different} delay times, a third component should pick up delayed AGB enrichment not captured by the original delayed process.
+Indeed, evidence of a distinct AGB-like process is identified in G22 and W22, where correlated residuals are used to expand the two-process model.
+However, both works add components in a restrictive manner that requires choosing which elements to assign to 3rd and/or 4th processes and that does not allow for the original two processes to vary.
+
+We take a more flexible approach, allowing the model to identify the elements best-fit with additional components and modify the $K=2$ process parameters.
+Ultimately, such a method could be used to identify elements with more than two enrichment channels, but we will refrain from over-interpretation here.
+Our model now includes four components, such that
+\begin{equation}\label{eq:mij_4}
+    m_{ij} = \log_{10}(\Acc\,\qcc + \AIa\,\qIa + A_{i}^{3}\,q_{3, j}^{Z} + A_{i}^{4}\,q_{4, j}^{Z}),
 \end{equation}
+where $q_{3, j}^{Z}$ and $q_{4, j}^{Z}$ are the third and fourth process vector components and $ A_{i}^3$ and $A_{i}^4$ are the third and fourth process amplitudes.
+The model, however, does require some regularization to converge.
+As in the $K=2$ case where we assume that Mg is a pure CCSN element and fix the $\qccFe$ and $\qIaFe$ values, we need elements to regulate of our 3rd and 4th processes.
+We choose Ce and Mn, two elements with larger residuals that likely have additional nucleosynthetic sources---Ce from AGB stars and Mn from unique classes of SNIa \citep[e.g.][]{gallino1998, reyes2020, gronow2021}.
+We initialize the $K=4$ model at the $K=2$ model values of $\qcc$, $\qIa$, $\Acc$, and $\AIa$ with the added constraints that
+\begin{equation}\label{eq:q3_z}
+    q_{{\rm 3, Mg}}^{\,Z} = 0, \quad 
+    q_{{\rm 3, Fe}}^{\,Z} = 0,  \quad 
+    q_{{\rm 3, Mn}}^{\,Z} = 0, \quad 
+    q_{{\rm 3, Ce}}^{\,Z} = 1 \quad 
+\end{equation}
+and 
+\begin{equation}\label{eq:q4_z}
+    q_{{\rm 4, Mg}}^{\,Z} = 0, \quad 
+    q_{{\rm 4, Fe}}^{\,Z} = 0,  \quad 
+    q_{{\rm 4, Mn}}^{\,Z} = 1, \quad 
+    q_{{\rm 4, Ce}}^{\,Z} = 0. \quad 
+\end{equation}
+We first fit the $A$-step to only Mg, Fe, Mn, and Ce, and then conduct 32 iterations of the $q$-step and $A$-step, as described in Section~\ref{sec:model}.
+We again inflate the according to Equation~\ref{eq:inflate_ivar} with $Q=5$.
 
-We fit this model to the data with a chi-squared ($\chi^2$) minimization such that
+The model converges upon a set of process vector components and amplitudes that can be combined with Equation~\ref{eq:mij_4} to predict the stellar abundances and calculate the fractional contribution from each process.
+The model parameters themselves are less directly interpretable, as we set the third and fourth process vector components for Ce and Mn to an arbitrary value with no metallicity dependence, so we do not show them here.
+We calculate $\fcc$, $f_{{\rm Ia}, ij}$, $f_{3, ij}$, and $f_{4, ij}$ for each abundance of each star where
+\begin{equation}\label{eq:fX}
+    f_{k, ij} = \frac{A_{i}^{k} \, q_{k,j}^Z}{\Acc\,\qcc + \AIa\,\qIa + A_{i}^{3}\,q_{3, j}^{Z} + A_{i}^{4}\,q_{4, j}^{Z}}.
+\end{equation}
+We find that the third process, regularized to Ce, contributes minorly to O, Si, S, Al, and K and more significantly to Ca, Na, Cr, and Ce.
+The fourth process, regularized to Mn, contributes minorly to K and more significantly to S, C+N, Na, Cr, Ni, Mn, and Co.
+These best-fit element groupings resemble but are not identical to the elements selected for additional components in W22, where the third process included Ca, Na, Al, K, Cr, and Ce and the fourth process included Ni, V, Mn, and Co.
 
-\begin{equation}
-    \chi^2 = \sum_{i=1}^{N} (\xh_{ij} - m_{ij})^{\rm T} c_j^{-1} (\xh_{ij} - m_{ij}) + \text{regularization}~,
+In the fourth column of Figure~\ref{fig:all_paramK}, we plot the median $f_{K, ij}$ as a function of $\mgh$ of the low-Ia population (Equation~\ref{eq:lowIa}) for a subset of elements with significant contributions from the third and/or fourth processes.
+We include median $\fcc$ and $f_{{\rm Ia},ij}$ from the $K=2$ model for comparison.
+We see that the third process contributes significantly to Ca, Na, Cr, and Ce at low metallicity, with decreasing contribution up to $\mgh\approx0.1$.
+The fractional contribution from the $K=2$ prompt and delayed processes to these elements decreases under the $K=4$ model, with median $\fcc$ decreasing more substantially than $f_{{\rm Ia}, ij}$.
+The fourth process behaves in a similar manner but with elements C+N, Na, Cr, Ni, Mn, and Co.
+We find that the addition of a fourth process decreases $\fcc$ and $f_{\rm Ia}$ values by roughly equal amounts at low metallicities.
+The fractional contribution from the third and fourth process is nearly identical in the high-Ia population, though the median $\fcc$ and $f_{{\rm Ia}, ij}$ values vary more significantly (as seen in Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}).
+
+Adding model components increases the abundance diversity that \name{} can achieve.
+In the left-most columns of Figure~\ref{fig:all_paramK}, we plot the $\xmg$ v.s.
+$\mgh$ distributions for the observed stellar sample, the $K=2$ model predictions, and the $K=4$ model predictions for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
+We note that the predicted abundances do \textit{not} have noise added (unlike Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}).
+Comparing the predicted abundances from the $K=2$ and $K=4$ process models, we see that the $K=4$ process model is better able to capture the observed abundance distribution than the $K=2$ model.
+Specifically, it better captures the scatter in the low metallicity end of the low-Ia population.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/all_param_k4.pdf}
+    \caption{Left: [X/Mg] vs.
+[Mg/H] abundance distributions for the observed sample (first column), $K=2$ model (second column) and $K=4$ model (third column) for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
+Right: median fractional contribution from each process for the $K=4$ (solid lines) and $K=2$ (dashed lines) models to the low-Ia population as a function of $\mgh$.
+We plot the median $\fcc$ in light purple, $f_{{\rm Ia}, ij}$ in dark purple, $f_{3, ij}$ in light orange, and $f_{4, ij}$ in dark orange as well as a dotted grey line at 0 for reference.}
+    \label{fig:all_paramK}
+\end{figure*}
+
+The improved ability of the $K=4$ model to capture the abundance diversity of our stellar sample is also clear in the fit statistics.
+In Figure~\ref{fig:comp_Ks}, we plot the cumulative $\log(\chi^2)$ distributions for the fits to each star and the total $\chi^2$ for each element for the fiducial $K=2$ model and the $K=4$ model.
+We see that the cumulative $\log(\chi^2)$ distribution decreases with the increase in model components.
+We also find that the $\chi^2$ per element is lower for all elements in the $K=4$ model.
+Significant improvements to Ca, C+N, Mn, and Ce are likely due to the additional third and fourth components capturing abundance patterns that the original prompt and delayed processes could not.
+Notably, we also see a significant improvement in the Fe fit, even though we require $q_{\rm 3,Fe}^{Z} = q_{\rm 4,Fe}^{Z} = 0$.
+Because all elements influence the $K=2$ model fit, the fiducial model was likely pulled away from the best solution for Fe to accommodate another element, like Mn.
+With the additional components able to account for the non-Fe-like enrichment, the original two processes are better able to capture the Fe enrichment.
+
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/comp_Ks.pdf}
+    \caption{Left: cumulative distribution of $\log \chi^2$ for the $K=2$ model (solid dark purple line) and our the $K=4$ model (dotted light purple line).
+Right: $\chi^2$ per element for the same model fits.}
+    \label{fig:comp_Ks}
+\end{figure*}
+
+Through this investigation, we find that \name{} is extendable to $K>2$ processes.
+Adding components improves the model's ability to capture the observed abundance diversity.
+We will not interpret these results in terms of nucleosynthesis here, but provide a discussion of the future science that \name{} and the $K=4$ model enable below.
+
+\section{Discussion}\label{sec:discussion}
+
+In this paper, we present \name{}, a flexible and data-driven model of for nucleosynthesis.
+\name{} describes stellar abundances as the sum of $K$ components, where each component is the product of a metallicity-dependent process vector component (fit to each element) and a process amplitude (fit to each star).
+Combined with a likelihood function and a set of assumptions (Section~\ref{sec:model}) that make the processes interpretable in terms of nucleosynthetic sources, the best-fit \name{} parameters can be used to calculate fractional contributions from each process as well as a full suite of predicted $K$ process abundances.
+
+We fit \name{} with $K=2$ to 15 abundances labels for 48,659 RGB stars in APOGEE DR17, selecting a population that minimizes statistical and systematic errors while spanning an [Mg/H] of -0.8 to 0.5.
+In the $K=2$ model, the first process, fixed to Mg, represents prompt CCSN-like enrichment, and the second process, fixed to Fe, represents delayed SNIa-like enrichment---but other nucleosynthetic sources with similar time delays may be mixed into each.
+Overall, we find that $K=2$ is a good fit to the data and that the model successfully recovers the global abundance patterns in the Milky Way.
+While \name{} does not rely on $\femg$ vs.
+$\mgh$ bimodality or median abundance trends, it is able to recover the observed bimodal abundance distribution.
+Further, the fit parameters $\Acc$ and $\AIa$ act as ``denoised'' abundance labels, and reveal a clearer signature of bimodality at high-metallicity in $\AIa/\Acc$ vs.
+$\mgh$ space than in $\femg$ vs.
+$\mgh$.
+This suggests that the $KPM$ fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are condensing information from 15 elements into two variables.
+
+To test the assumptions of the fiducial model, we explore the impact of varying the fixed value of $\qccFe$.
+We find that high values of $\qccFe$ (0.5 and 0.45) are not able to reproduce the observed [Fe/Mg] vs [Mg/H] abundance distribution, regardless of the process vector component's metallicity dependence, and that values $\qccFe = 0.4$ and 0.35 with $\dqccFe = 0$ or 0.15 produces similarly successful fits.
+While predicted abundance distributions appear similar for these models, the implied fractional contribution from the prompt process is strongly dependent upon the Fe assumption for elements with substantial delayed enrichment.
+Through this exploration, we conclude that the quantitative nucleosynthetic interpretation of \name{} is dependent upon the input assumptions, and that there is inherent uncertainty in the $\fcc$ values.
+
+Finally, we expand \name{} from $K=2$ to $K=4$, regularizing the third and fourth processes to Ce and Mn.
+KPM builds off of the original model, such that the $K=4$ model starts at the $K=2$ solution and then finds the best-fit parameters for $K=4$, altering the original solution and allowing all elements (except Mg and Fe) to have contributions from additional processes.
+We find that S, Ca, C+N, Na, Cr, Mn, Co, Ni, and Ce are best fit with a third and/or fourth component, with such processes contributing most significantly at low metallicity.
+The $K=4$ model improves the ability of \name{} to fit the abundances of all elements but especially improves predictions of Ca, C+N, Fe, Mn, and Ce.
+This successful implementation of a $K=4$ model shows that \name{} can be extended to $K>2$, and it has potential future use in constraining enrichment beyond a single prompt and delayed process---critical to understanding enrichment from AGB stars, merging neutron stars, and rarer novae.
+
+\name{} is based upon the two-process model developed in W19 and W22.
+While the two models are identical in format for the $K=2$ case, the model assumptions, parameter derivations, and implementations differ.
+The W22 two-process model derives process vector components from median abundance trends, reliant upon $\mgfe$ vs.
+$\mgh$ bimodality, and fits process amplitudes to a subset of $2-6$ $\alpha$ and Fe-peak elements.
+\name{}, on the other hand, employs a likelihood function fit to all stars and all elements to derive both process amplitudes and vector components.
+Our more data-driven implementation results in the improved ability to predict stellar abundances.
+Notably, \name{} can better predict C+N and Mn abundances than the W22 two-process model, since all elements are used to constrain the fits.
+The most significant improvement to the original two-process model, though, is in \name{}'s flexibility.
+The flexible implementation of the model allows us to easily vary the assumptions, such as $\qccFe$, and increase the number of model components to study the impact of our assumptions on the results and push the interpretation of \name{} beyond standard CCSN and SNIa nucleosynthesis in a less restrictive manner than W22 and G22.
+
+However, \name{} is not without its own faults.
+The assumptions listed in Section~\ref{sec:model} may incorrectly skew our results and the model could benefit from improvements in implementation.
+While assumptions (4) and (5) on Mg and Fe production are flexible, \name{} requires that both elements have fixed process vector components.
+If our assumptions are incorrect and, for instance, Mg is not a pure prompt element or (in the $K=4$ case)  Fe has contributions from multiple delayed sources, our nucleosynthetic interpretation of \name{} may be incorrect.
+Additionally, assumption (7) states that the APOGEE data products can be used for this project, but that we inflate abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
+If the APOGEE errors are correct, this assumption could pull the model away from a solution that favors true outlier points.
+In future \name{} implementation, the development of a more robust method to justifiably de-weighting outlier stars from the global fits would be beneficial.
+Finally, \name{} fits process vector components along a spline with 11 knots (assumption 6).
+As this method fits a polynomial between each knot, it can result in sharp features at the knot locations in metallicity regions with few points or large scatter.
+Fitting process vector components with a continuous function would be more ideal, though Appendix C.1 in G22 suggests that this change will have minimal impact on the results.
+\ejg{Hogg add a bit about expanding to a more general latent-variable model?}
+
+Beyond improvements to the underlying model assumptions and implementation, \name{} needs to include parameter uncertainty.
+While the model delivers process vector components and amplitudes, which can be used to calculate $f_{K, ij}$ and $K$ process predicted abundances, the current implementation does not return errors on any variable.
+The best method to derive such errors has not been explored, but one could use the likelihood function or bootstrapping.
+These methods will encapsulate the uncertainty on process parameters from the APOGEE abundance errors but will not capture the uncertainty due to model assumptions, such as $\qccFe$ (Section~\ref{subsec:qccFe}).
+
+While such future changes will improve the model, the current form of \name{} and its data products can support ongoing research and will enable new science.
+Most immediately, \name{} provides high signal-to-noise abundance labels, $\Acc$ and $\AIa$, as well as de-noised stellar abundances ($m_{ij}$).
+$\Acc$ and $\AIa$, in particular, are powerful tracers of nucleosynthesis.
+\ejg{Hogg add a bit about overall $\alpha$/M indicators.} In Section~\ref{subsec:parameters}, we showed that the high-Ia and low-Ia populations are more clearly defined in $\AIa/\Acc$ vs.
+[Mg/H] than in [Fe/Mg] vs/ [Mg/H].
+In amplitude space, the low-Ia population can be re-defined as
+\begin{equation}\label{eq:lowIa new}
+\begin{cases}
+\AIa/\Acc < 0.35 ,    & \mgh<-0.2 \cr
+\AIa/\Acc < 0.5 + 0.7 \, \mgh,  & -0.2\geq\mgh<0.1, \cr
+\AIa/\Acc < 0.57 ,    & \mgh\geq0.1 \,. \cr
+\end{cases}
 \end{equation}
-where $c_j^{-1}$ is a matrix of the inverse variance squared,
-\begin{equation}
-    c^{-1} = \begin{bmatrix}
-\frac{1}{\sigma_j^2} & 0 & ...\\
-0 & \frac{1}{\sigma_j^2} & ... \\
-0 & 0 & ... 
-\end{bmatrix}
-\end{equation}
-$N$ stars, such that $1 \leq i \leq N$, and ``regularization'' stands in for some additional penalization terms that we will describe below.
+Compared to Equation~\ref{eq:lowIa} (W19, W22), this new definition re-classifies 647 stars as high-Ia and 224 stars as low-Ia.
+We show the location of these stars in $\AIa/\Acc$ vs.
+[Mg/H] and [Mg/Fe] vs.
+[Fe/H] in Figure~\ref{fig:pop_divis}.
+Many of the re-classified stars are at $\feh>-0.1$.
+When dividing in [Mg/Fe], it is difficult to correctly separate the populations at high metallicity, as they are blended together.
+Our new definition also re-classifies many stars near [Fe/H] of -0.3 as high-Ia, suggesting that the W19 and W22 high-Ia definition has too shallow a slope.
+While only $\sim 2\%$ of stars are re-classified under the new definition, we suggest that Equation~\ref{eq:lowIa new} be used to chemically define the low-Ia and high-Ia populations if \name{} fits are available, especially if studying stars with $\feh > -0.1$.
+Beyond improving the definition of high-Ia and low-Ia populations, the \name{} parameters and predicted abundances could be used in any current analysis that strives to show trends with abundance labels.
+We predict that trends of stellar parameters with [X/H] will be clearer when comparing to $[\text{X}/\text{H}]_{\rm pred}$, $\Acc$, or $\AIa$.
 
-$M$ elements, such that $1 \leq j \leq M$ where $j \in \{ \text{Mg, O, Si, S, Ca, CN, Na, Al, K, Cr, Fe, Ni, V, Mn, Co, Ce} \}$, the elements in APGOEE DR17 and used in \citet{weinberg2022}.
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=.9\textwidth]{Paper/Figures/pop_divis.pdf}
+    \caption{Left: distribution of stars in $\AIa/\Acc$ vs.
+[Mg/H] where the black dashed line is the dividing line between the high-Ia and low-Ia populations (Equation~\ref{eq:lowIa new}).
+Stars that are re-classified as high-Ia are shown in purple (647 stars) and stars that are re-classified as low-Ia are shown in orange (224 stars).
+Right: Same as left, but in [Mg/Fe] vs.
+[Fe/H] space.
+The high-Ia and low-Ia populations have been labeled in both panels for clarity.
+    \label{fig:pop_divis}}
+\end{figure*}
 
-\subsection{Assumptions}\label{subsec:assumptions}
+Such analysis with \name{} parameters will be useful in studying nucleosynthesis, dynamics, disk formation, stellar ages, and much more.
+However, in this paper we only present fits for a small population with restricted stellar parameters, relative to the full APOGEE sample.
+\ejg{Add some discussion about the data products that are available for the sample in this paper and the availability of our code....} While \name{} could be fit to the full APOGEE sample, systematic abundance effects with $\teff$ and $\logg$, as well as other abundance artifacts \citep[e.g.,][]{jonsson2020, griffith2021a}, cause the abundance trends to differ across the Hertzsprung-Russell diagram.
+The best-fit \name{} parameters for the giants would differ from those for the dwarfs.
+If such systematics could be accounted for (see Sit et al.
+in prep) we could fit the full APOGEE stellar sample with \name{}, or train \name{} on a subset of high signal-to-noise stars and apply the fits to the full sample.
+This potential future analysis could reveal additional information about the nucleosynthetic history of our Galaxy and would provide higher signal-to-noise abundance labels for the full sample.
 
-Some of the assumptions that go into the two-process model \name{} are the following:
+The success of the two-process model (W19, W22) and \name{} with $K=2$ suggests that the disk is largely two-dimensional (2D).
+In this paper, we have focused on a 2D nucleosynetheic model, with the two dimensions representing prompt CCSN-like enrichment and delayed SNIa-like enrichment.
+However, another 2D class of theoretical models for the Milky Way exist, describing stars in terms of birth radius and birth date \citep[e.g.,][]{frankel2018, ness2022}.
+Are these two 2D models related?
+If they are, then the nucleosynthetic parameters from \name{} ($\AIa$ and $\Acc$) should predict asteroseismic ages (or masses), up to unpredictable aspects of mass transfer, as well as the guiding radius, up to unpredictable aspects of radial migration.
+While a deeper study of the implications of the disk's two-dimensionality is outside the scope of this work, we show the relationship between age and process amplitudes in Figure~\ref{fig:age}.
+Here we see a clear gradient in age with $\Acc$ and $\AIa/\Acc$ (as in G22 and W22), though outlier stars are scattered throughout.
+We predict that the \name{} parameters will be better age diagnostics than APOGEE abundances, and that age outliers may be mass transfer objects.
 
-\paragraph{Two processes}
-HOGG whatever.
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=.6\textwidth]{Paper/Figures/AIaAcc_age.pdf}
+    \caption{$\AIa/\Acc$ vs. $\Acc$ distribution for stars in the APOKASC sample. Each point is colored by the star's log(Age), with younger stars in black and older stars in yellow.
+    \label{fig:age}}
+\end{figure*}
 
-\paragraph{Linearity}
-At every metallicity, the abundances of a star can be expressed as a linear combination of two processes.
-These processes themselves might depend on metallicity, but a linear sum is sufficient to explain all element abundances.
-Because of dependences of yields on detailed abundances, and because different stars can get to their metallicities by different histories, this assumption must be slightly wrong in detail.
+Finally, because of the flexibility of \name{}, new scientific applications are enabled that were not feasible before.
+Because \name{} does not rely on [Mg/Fe] vs.
+[Fe/H] bimodality, non-bimodal population can now be fit with a multi-component nucleosynthetic model.
+\name{} could be applied to the low metallicity disk, halo, Gaia Enceladus Sausage, Nebula Majora, Nebula Minora\footnote{Historically referred to as the LMC and SMC.}, other Milky Way satellites, and more.
+\name{} can also be easily extended to $K>2$ in a much less restricted way than the two-process model.
+While a $K=2$ model well describes the global abundance patterns, intrinsic residual scatter on the scale of 0.01 to 0.02 dex remains (\citealp{ting2022}, W22, G22).
+This scatter could be signatures of enrichment from non-CCSN/SNIa sources, stochastic sampling of the IMF, environmental IMF variations, or metallicity-dependent SN yields with a bursty star formation history \citep[e.g.][]{belokurov2022, griffith2023}.
+While it is difficult to identify non-CCSN or SNIa enrichment in the APOGEE data alone, where only C+N and Ce are likely to have significant contributions from other sources, there may be signatures in other surveys with better coverage of heavier elements.
+Applying a $K>2$ model to GALAH \citep{buder2021}, or an overlapping sample of APOGEE and GALAH stars \citep{nandakumar2022}, could prove more successful.
 
-\paragraph{Non-negativity}
-All process amplitudes for all elements are non-negative (elements heavier than XXX are only produced, not ever destroyed, by the two processes),
-and all stars are made of a non-negative sum of the two non-negative processes.
-This makes the model similar to a non-negative matrix factorization (\citealt{nnmf}).
-
-\paragraph{Magnesium is a core-collapse element only}
-All magnesium is produced in the core-collapse (CC) process, and none in the type-Ia (Ia) process.
-This breaks (something like) a rotational symmetry in the process space, and makes the processes interpretable in terms of supernova types.
-
-\paragraph{Metallicity dependence}
-The fact that all magnesium is produced in the CC process is an assumption that is independent of metallicity.
-All other process vectors are permitted to float as a function of metallicity.
-The only exceptions are the magnesium level in the CC process and the iron level in the Ia process, but these constraints are just model normalizations; they don't restrict the overall model freedom, which is about abundance ratios.
-
-\paragraph{\textsl{APOGEE} abundances}
-We are assuming that the \textsl{APOGEE} abundances can be used for this project.
-This is not quite the same as assuming that they are correct.
-It is more like assuming that it is possible and useful to build an interpretable 2-process model to explain them.
-EMILY: WE NEED A DATA SECTION that explains how we put together the data and which data we used.
-
-\bigskip
-These assumptions (above) mirror the assumptions of prior work (\citealt{griffith2022}; \citealt{weinberg2022}) but they are weaker.
-In particular, they don't assume anything about the relationships between the processes and the morphologies of observed element-abundance ratio diagrams.
-In addition to the above assumptions, which are about nucleosynthesis, there are assumptions about the data:
-
-\paragraph{Measurement uncertainties}
-HOGG
-
-\paragraph{Likelihood function}
-HOGG
-
-\subsection{Constraints and Regularizations}\label{subsec:regularizations}
-
-Some of the assumptions in our model directly translate to constraints and regularization.
-
-We always enforce that the process vectors and amplitudes are greater than zero:
-\begin{equation}
-    \vec{q}_{{\rm CC}, j}^{\,Z}, \, \vec{q}_{{\rm Ia}, j}^{\,Z} \geq 0 \quad \forall \; j
-\end{equation}
-
-\begin{equation}
-    A_i^{\rm CC}, \, A_i^{\rm Ia} \geq 0 \quad \forall \; i.
-\end{equation}
-
-We will start with the constraints from \citet{weinberg2022} as well:
-
-\begin{equation}
-    \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1 \quad \vec{q}_{{\rm Ia, Mg}}^{\,Z_{\odot}} = 0 \quad 
-    \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.5 \quad \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 0.5 
-\end{equation}
-
-\begin{equation}
-    \vec{q}_{{\rm CC, Mg}}^{\,Z} = \vec{q}_{{\rm CC, Mg}}^{\,Z_{\odot}} \quad 
-    \vec{q}_{{\rm CC, Fe}}^{\,Z} = \vec{q}_{{\rm CC, Fe}}^{\,Z_{\odot}}  \quad 
-    \vec{q}_{{\rm Ia, Fe}}^{\,Z} = \vec{q}_{{\rm Ia, Fe}}^{\,Z_{\odot}} 
-\end{equation}
-
-\begin{equation}
-    \vec{q}_{{\rm CC}, j}^{\,Z_{\odot}} + \vec{q}_{{\rm Ia}, j}^{\,Z_{\odot}} = 1 \quad \forall \; j
-\end{equation}
-
-\section{Experiments and Results}
-
-\section{Discussion}
-
-\begin{itemize}
-    \item What is the connection between this model and latent variable models of machine learning
-    \item Casual inferences - which abundances are caused by the Mg abundance and which are not (statistician perspective)
-
-\end{itemize}
-
-\section{Summary}
+\ejg{Some concluding statement about the tons of future science that KPM can do and how readers can access it.}
 
@@
 It is a pleasure to thank
-  Soledad Villar (JHU)
-for valuable discussions.
-This project benefited enormously from the Python package \texttt{jax} \citep{jax}.
+  Melissa Ness (Columbia),
+  Adrian Price-Whelan (Flatiron),
+  Tawny Sit (OSU),
+  Soledad Villar (JHU),
+  David Weinberg (OSU),
+  CU Boulder Research Computing services and staff,
+  and the Astronomical Data group at the Flatiron Institute
+for valuable discussions and help.
 E.J.G. is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.
 
-% \software{Matplotlib \citep{hunter2007}, NumPy \citep{harris2020}, Pandas \citep{pandasa, pandasb}, Astropy \citep{astropy2013, astropy2018, astropy2022}, astroNN \citep{bovy2017}, EXOFASTv2 \citep{eastman2013, eastman2019}, iSpec \citep{blanco2014, blanco2019}, MOOG \citep{sneden1973}, galpy \citep{bovy2015, mackereth2018}}, jax \citep{jax}
+Funding for the Sloan Digital Sky Survey V has been provided by the Alfred P.
+Sloan Foundation, the Heising-Simons Foundation, the National Science Foundation, and the Participating Institutions.
+SDSS acknowledges support and resources from the Center for High-Performance Computing at the University of Utah.
+The SDSS web site is \url{www.sdss.org}.
+
+SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions of the SDSS Collaboration, including the Carnegie Institution for Science, Chilean National Time Allocation Committee (CNTAC) ratified researchers, the Gotham Participation Group, Harvard University, Heidelberg University, The Johns Hopkins University, L’Ecole polytechnique f\'{e}d\'{e}rale de Lausanne (EPFL), Leibniz-Institut f{\"u}r Astrophysik Potsdam (AIP), Max-Planck-Institut f{\"u}r Astronomie (MPIA Heidelberg), Max-Planck-Institut f{\"u}r Extraterrestrische Physik (MPE), Nanjing University, National Astronomical Observatories of China (NAOC), New Mexico State University, The Ohio State University, Pennsylvania State University, Smithsonian Astrophysical Observatory, Space Telescope Science Institute (STScI), the Stellar Astrophysics Participation Group, Universidad Nacional Aut\'{o}noma de M\'{e}xico, University of Arizona, University of Colorado Boulder, University of Illinois at Urbana-Champaign, University of Toronto, University of Utah, University of Virginia, Yale University, and Yunnan University.
+
+\software{matplotlib \citep{hunter2007}, NumPy \citep{harris2020}, pandas \citep{pandasa, pandasb}, astropy \citep{astropy2013, astropy2018, astropy2022}, and jax \citep{jax}.}
+
+\facilities{Sloan, Kepler}
 

### 2023-06-04 Paper/main.tex
removed half of the Hoggs

@@
 \shortauthors{Griffith \& Hogg}
-\addtolength{\topmargin}{-0.4in} % trust in Hogg
-\addtolength{\textheight}{0.7in} % trust in Hogg
+\addtolength{\topmargin}{-0.4in} % trust the process
+\addtolength{\textheight}{0.7in}
 \setlength{\parindent}{1.6em}
-\renewcommand{\twocolumngrid}{} % once again
+\renewcommand{\twocolumngrid}{} % trust the process
 \renewcommand{\paragraph}[1]{\bigskip\par\noindent{\textbf{#1}}~---}
-\sloppy\sloppypar\raggedbottom\frenchspacing % Trust Hogg
+\sloppy\sloppypar\raggedbottom\frenchspacing % trust the process
 
@@
 
-\begin{abstract}\noindent % trust Hogg
+\begin{abstract}\noindent % trust
 Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
@@
 In the $K$ Process Model (\name{}), we find the intersection between reliable facts about nucleosynthesis and good abundance measurements to build an edifice of Galactic enrichment.
-The parameters output by our model can be used as de-noised abundance label to sharpen relationships between abundances and stellar parameters.
-\ejg{Add more about high-quality metallicity labels?
-Hogg to edit this paragraph.}
+The model is hierarchical, in that it learns some parameters (process vectors) that are shared across all stars, but different for each element, and some parameters (process amplitudes) that are shared across all elements, but different for each star.
+The parameters output by our model can thus be used as de-noised abundance labels; these will sharpen relationships between abundances and stellar parameters (including birth location and time).
 
@@
 This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful data-driven models (e.g., G22, W22, \citealp{ting2022}).
-In this paper we therefore assume that $K \geq 2$, though \name{} could be implemented with $K=1$.
-\hogg{This assumption says too much; we could dial this back.}
+In this paper we therefore assume that $K \geq 2$, though \name{} could in principle be implemented with $K=1$.
 
 \paragraph{2. Linearity}
-At every metallicity, the (X/H) abundances of a star can be expressed as a linear combination of $K$ processes.
+At every metallicity, the (linear) $(X/H)$ abundances of a star can be expressed as a linear combination of $K$ processes.
 These processes themselves will depend on metallicity, but a linear sum is sufficient to explain all element abundances at any overall metallicity.
@@
 We describe the potential data systematics in Section~\ref{sec:data}.
-The APOGEE errors are likely slightly underestimated for some element measurements, so we add softening parameter $Q$ to inflate the errors (see Equation~\ref{eq:inflate_ivar}).
-\hogg{Make this more positive about apogee}
+The APOGEE errors may be slightly underestimated for some element measurements, so we add a softening parameter $Q$ to inflate the uncertainties on abundance-outlier stars (see Equation~\ref{eq:inflate_ivar}).
 
@@
 
-While \name{} is flexible, it still requires assumptions to break model degeneracies (see Section~\ref{sec:model}).
-Specifically, it requires an element with ``known'' $\qcc$ and an element with known $\qIa$ to constrain each process.
-\ejg{Hogg edit this paragraph.} For the prompt process, we ground our assumption in the nucleosynthetic theory that Mg is a pure CCSN element \citep[e.g.,][]{andrews2017}.
+While \name{} is flexible, we still include some quantitative assumptions, which we make to break exact model degeneracies (see Section~\ref{sec:model}).
+Specifically, for each process, we choose one element to assign a ``known'' process vector element at all metallicities.
+These are Mg and Fe in the 2-process case.
+Specifically, for the prompt process, we ground our assumption in the nucleosynthetic theory that Mg is a pure CCSN element \citep[e.g.,][]{andrews2017}.
 Unfortunately there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
-In order to regularize the delayed process, we choose to fix the Fe process vector components, making unsubstantiated assumptions about Fe enrichment.
+In order to break an exact degeneracy between the prompt and delayed processes, we choose to fix the Fe process vector components, making unsubstantiated assumptions about Fe enrichment.
 
@@
 $\mgh$.
-This suggests that the $KPM$ fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are condensing information from 15 elements into two variables.
+This suggests that the \name{} fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are condensing information from 15 elements into two variables.
 
@@
 Finally, we expand \name{} from $K=2$ to $K=4$, regularizing the third and fourth processes to Ce and Mn.
-KPM builds off of the original model, such that the $K=4$ model starts at the $K=2$ solution and then finds the best-fit parameters for $K=4$, altering the original solution and allowing all elements (except Mg and Fe) to have contributions from additional processes.
+\name{} builds off of the original model, such that the $K=4$ model starts at the $K=2$ solution and then finds the best-fit parameters for $K=4$, altering the original solution and allowing all elements (except Mg and Fe) to have contributions from additional processes.
 We find that S, Ca, C+N, Na, Cr, Mn, Co, Ni, and Ce are best fit with a third and/or fourth component, with such processes contributing most significantly at low metallicity.
@@
 
-\ejg{Some concluding statement about the tons of future science that KPM can do and how readers can access it.}
+\ejg{Some concluding statement about the tons of future science that \name{} can do and how readers can access it.}
 

### 2023-06-17 Paper/main.tex
various content and references

@@
+% This document is part of the KPM project
+% Copyright 2023 the authors.
+% ------------------------------------------------------------------
+
+% to-do items
+% -----------
+% - Look at all latex warnings on the build
+
 \documentclass[modern]{aastex631}
 \usepackage{amsmath}
+\usepackage{microtype}
 \usepackage{soul}
@@
 \newcommand{\xh}{[{\rm X}/{\rm H}]}
-
 \newcommand{\logg}{\log(g)}
@@
 \newcommand{\MZAMS}{M_{\rm ZAMS}}
-
 \newcommand{\qcc}{q_{{\rm CC,}j}^{Z}}
@@
 
-After hydrogen, helium, lithium, and beryllium, all other naturally occurring elements are made in the stars, and the collisions of stars.
+After hydrogen, helium, lithium, and beryllium, all other naturally occurring elements are made in stars, supernovae, and the collisions of stars.
 Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed record of the element abundances in the gas from which the star formed \citep[though see e.g.,][]{pinsonneault2001, oh2018, souto2019, vincenzo2021b}.
@@
 This assumption implies that the elements considered here are only produced, and not ever destroyed, by the $K$ processes (relative to hydrogen).
-This makes the model similar to a non-negative matrix factorization (\citealt{nnmf} \ejg{Hogg add citation}).
+This makes the model similar to a non-negative matrix factorization (\citealt{nnmf, nnmf2}).
 In \name{}, this assumption is enforced by requiring that the process vector components and amplitudes are always greater than or equal to zero, such that
@@
 
-Because we don't want to be too drawn or influenced by outlier points, we don't use the observed errors $\sigma_{{\rm obs},ij}$ in the likelihood, but instead we soften them in the spirit of iteratively reweighted least squares (HOGG CITE):
+Because we don't want to be too drawn or influenced by outlier points, we don't use the observed errors $\sigma_{{\rm obs},ij}$ in the likelihood, but instead we soften them in the spirit of iteratively reweighted least squares (\citealt{irls}):
 \begin{equation}\label{eq:inflate_ivar}
@@
 
-\bibliography{sample631}{}
+\bibliography{kpm}{}
 \bibliographystyle{aasjournal}

### 2023-06-18 Paper/main.tex
small hogg changes

@@
 We assume that a particular set of hard-coded knots are sufficient to capture the metallicity dependence.
-\hogg{This could be mentioned in passing in the discussion where you talk about model improvements.}
 
@@
 If the APOGEE errors are correct, this assumption could pull the model away from a solution that favors true outlier points.
-In future \name{} implementation, the development of a more robust method to justifiably de-weighting outlier stars from the global fits would be beneficial.
-Finally, \name{} fits process vector components along a spline with 11 knots (assumption 6).
+In future \name{} implementation, the development of a more robust method to justifiably down-weight outlier stars from the global fits would be beneficial.
+Finally, \name{} fits process vector components along a spline with 11 knots (assumption 6), and those knots have fixed locations in metallicity.
 As this method fits a polynomial between each knot, it can result in sharp features at the knot locations in metallicity regions with few points or large scatter.
-Fitting process vector components with a continuous function would be more ideal, though Appendix C.1 in G22 suggests that this change will have minimal impact on the results.
-\ejg{Hogg add a bit about expanding to a more general latent-variable model?}
+Fitting process vector components with a differentiable function might be more reasonable, though results shown in Appendix C.1 in G22 suggests that this change might have minimal impact on the results.
+In general this model for the metallicity-dependence of the yields is very rigid; a better model could both have more flexibility and be smoother.
 
@@
 Most immediately, \name{} provides high signal-to-noise abundance labels, $\Acc$ and $\AIa$, as well as de-noised stellar abundances ($m_{ij}$).
-$\Acc$ and $\AIa$, in particular, are powerful tracers of nucleosynthesis.
-\ejg{Hogg add a bit about overall $\alpha$/M indicators.} In Section~\ref{subsec:parameters}, we showed that the high-Ia and low-Ia populations are more clearly defined in $\AIa/\Acc$ vs.
+The best-fit values of $\Acc$ and $\AIa$, in particular, are powerful tracers of nucleosynthesis.
+They show a bimodality at all metallicities, as do the de-noised abundances. \hogg{EJG: Is this true? I just wrote it.}
+And---because the model is a maximum-likelihood model---they represent information-theory optimal combined measures of alpha  and iron abundances.
+That is, these data-driven amplitudes could replace more theory-driven measures of the relative contributions of core-collapse and Ia enrichment channels.
+
+In Section~\ref{subsec:parameters}, we showed that the high-Ia and low-Ia populations are more clearly defined in $\AIa/\Acc$ vs.
 [Mg/H] than in [Fe/Mg] vs/ [Mg/H].

### 2023-06-27 Paper/main.tex
incorporating comments from readers

@@
 \newcommand{\AIa}{A^{\rm Ia}_{i}}
-\newcommand{\fcc}{f_{{\rm CC}, ij}}
+\newcommand{\fcc}{f_{ij}^{\rm CC}}
+
+\newcommand{\qccX}[1]{q_{{\rm CC, #1}}^{Z}}
+\newcommand{\qIaX}[1]{q_{{\rm Ia, #1}}^{Z}}
+\newcommand{\fccX}[1]{f_{i, {\rm #1}}^{\rm CC}}
 
 \newcommand{\ejg}[1]{\textcolor{red}{EJG says: #1}}
+\newcommand{\add}[1]{\textcolor{teal}{#1}}
+
 \newcommand{\hogg}[1]{\textcolor{blue}{Hogg says: #1}}
@@
 
+\author{Julianne Dalcanton}
+\author{Sten Hasselquist}
+\author{Bridget Ratcilffe}
+\author{Melissa Ness}
+\author{David Weinberg}
+
 \begin{abstract}\noindent % trust
-Stellar surface abundances look like they are produced by two dominant processes, one prompt and one delayed.
-We analyze the abundances of 14 elements in [X/Mg] vs. [Mg/H] space for 48,659 stars from APOGEE DR17 with a flexible, data-driven $K$-process model---dubbed \name.
-In the fiducial model, where $K=2$, each elemental abundance of each star is described as the vector sum of a prompt (CCSN-like) and delayed (SNIa-like) process.
-While prior work derives process vector components from median observed high-Ia and low-Ia abundance trends, we relax these assumptions and simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
+\add{The origin of the surface abundance patterns of Milky Way stellar populations can be explained by two dominant processes,} one prompt and one delayed.
+\add{While two components can well describe the stellar abundance trends, elements are known to be produced by more than two sources.}
+We analyze the abundances of 14 elements relative to Mg for 48,659 stars from APOGEE DR17 with a flexible, data-driven $K$-process model---dubbed \name.
+In the fiducial model, where $K=2$, each elemental abundance of each star is described as the vector sum of a prompt and delayed process.
+%While prior work derives the relative importance of \add{the prompt and delayed processes in the production of various elements} from median observed abundance trends, we relax these assumptions and 
+%We simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
 We find that our flexible method is able to recover the observed abundance bimodality and that this bimodality is visible to higher [Mg/H] in process amplitude space than in abundance space.
-We compare fit parameters and statistics from this new method to those from prior work, finding that the two methods produce similar results, but that \name{} better predicts stellar abundances, especially for C+N and Mn.
-We test the validity of the standard two-process model assumptions, such as that Fe is generated by a roughly half-half combination of prompt and delayed sources.
-We find that the assumptions of prior works are generally confirmed, but that the inferred fractional contributions from each process are strongly dependent upon Fe assumptions.
-We also explore third and fourth processes, calibrated to Ce and Mn, respectively.
-The additional processes improve the model's ability to predict the stellar abundances, demonstrating the model's ability to extend beyond $K=2$.
-\name{} enables future research to study the disk's two-dimensionallity, investigate age-abundance label correlations, fit non-bimodal abundance distributions with a multi-component nucleosynthetic model, and much more.
-\ejg{Add something about code availability.}
+We compare fit parameters and statistics from this new method to those from \citet{weinberg2022}, finding that the two methods produce similar results, but that \name{} better predicts stellar abundances, especially for C+N and Mn.
+%We test the validity of the standard two-process model assumptions, such as that in the sun Fe is generated by a roughly half-half combination of prompt and delayed sources.
+%We find that the assumptions of prior works are generally confirmed, but that the inferred fractional contributions from each process are strongly dependent upon Fe assumptions.
+\add{We explore the impact of our assumptions about the origin of Fe, needed to break the rotational symmetry of the model, constraining the parameter space that is able to reproduce the observed abundance distribution and finding that the inferred fractional contribution from each process are dependent upon our choice.}
+Finally, we add a third and fourth process, calibrated to Ce and Mn, respectively.
+The additional processes \add{give the model more freedom} and improve the model's ability to predict the stellar abundances, \add{as expected}, but demonstrates the model's ability to extend beyond $K=2$.
+\name{} enables future research to study the disk's abundance dimensionallity, investigate age-abundance label correlations, fit non-bimodal abundance distributions with a multi-component nucleosynthetic model, and much more.
+\ejg{Hogg: try to shorten the abstract. I made some changes but still need to cut like 25 more words.} 
 \end{abstract}
@@
 After hydrogen, helium, lithium, and beryllium, all other naturally occurring elements are made in stars, supernovae, and the collisions of stars.
-Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed record of the element abundances in the gas from which the star formed \citep[though see e.g.,][]{pinsonneault2001, oh2018, souto2019, vincenzo2021b}.
+Stellar surface abundances---the abundances measured by taking a spectrum of a stellar photosphere---are thought to deliver a relatively unprocessed record of the element abundances in the gas from which the star formed \citep[though see, e.g.,][]{pinsonneault2001, oh2018, souto2019, vincenzo2021b}.
 These birth abundances were set by a combination of nucleosynthetic processes involved in making heavy atomic nuclei, and astrophysical processes involved in delivering atoms from stellar interiors to star-formation sites \citep[e.g.,][]{johnsonja2020}.
@@
 
-At the present day, stellar surface abundances are not very well explained by \textsl{ab initio}, physics-driven models.
-Yields vary from set to set, as they are dependent on progenitor properties and explosion assumptions \citep[e.g.,][]{rybizki2017, griffith2021b}. 
-The wide parameter space of progenitor and supernovae models coupled with uncertainties in reaction rates and explosion physics hinder the creation of an accurate nucleosynthetic model from theory alone.
+At the present day, stellar surface abundances are not very well explained by purely \textsl{ab initio}, physics-driven models.
+Theoretical yields vary from set to set, as they are dependent on progenitor properties and explosion assumptions \citep[e.g.,][]{rybizki2017, blancato2019, buck2021, griffith2021b}. 
+The wide parameter space of progenitor and supernova models coupled with uncertainties in reaction rates and explosion physics hinder the creation of an accurate nucleosynthetic model from theory alone.
 In the long run, it is incumbent upon us to understand these issues and correct the assumptions or calculations underlying our nucleosynthetic and astrophysical models.
@@
 In this \documentname{}, we build a purely data-driven model for the surface element abundances observed in stars.
-We treat each star as being a linear combination of nucleosynthetic processes, beginning with one that is primarily responsible for the $\alpha$-element Mg \citep[prompt enrichment, such as core collapse supernovae or CCSN, e.g.,][]{andrews2017}, and one that is primarily \emph{not} responsible for Mg (delayed enrichment, such as Type-Ia supernovae or SNIa).
-Beyond these up-front assumption, we try to be agnostic about how the elements are produced.
+We treat each star as being a linear combination of nucleosynthetic processes, beginning with one that is primarily responsible for the $\alpha$-element Mg \citep[prompt enrichment, such as core-collapse supernovae or CCSN, e.g.,][]{andrews2017}, and one that is primarily \emph{not} responsible for Mg (delayed enrichment, such as Type-Ia supernovae or SNIa).
+Beyond these up-front assumptions, we try to be agnostic about how the elements are produced.
 
@@
 Using the median [X/Mg] vs.
-[Mg/H] abundance trends, these works explain data from the \textsl{GALAH}\footnote{GALAH = GALactic Archaeology with HERMES.} and SDSS-IV \textsl{APOGEE}\footnote{APOGEE = Apache Point Observatory Galactic Evolution Experiment, part of the Sloan Digital Sky Survey} surveys, respectively, with a two-process model.
+[Mg/H] abundance trends, these works explain data from the GALAH\footnote{GALAH = GALactic Archaeology with HERMES.} and SDSS-IV APOGEE\footnote{APOGEE = Apache Point Observatory Galactic Evolution Experiment, part of the Sloan Digital Sky Survey} surveys, respectively, with a two-process model.
 Because the median abundance trends in [X/Mg] vs.
@@
 
-These works, as well as \citet{ting2022}, find that the Milky Way stellar abundances are well fit two components, down to residuals of 0.01 to 0.02 dex.
-Simultaneously, \citet{frankel2018} and \citet{ness2022} have found that disk abundances are also well described by a two component model of birth radius and age.
-Correlations between two-process model parameters and stellar ages and kinematics (W22) suggest that these two 2-dimensional models are somehow interconnected.
-\ejg{Add bit on why two processes dominate---two main channels v.s.
-mixing in the disk.}
+These works, as well as \citet{ting2022} and \citet{ratcliffe2023}, find that the Milky Way stellar abundances are well fit by two components, \add{grounded in [Fe/H] and [Mg/Fe],} down to residuals of 0.01 to 0.02 dex.
+Simultaneously, \citet{frankel2018} and \citet{ness2022} have found that disk abundances are also well described by a two-component model of birth radius and age.
+Correlations between two-process model parameters and stellar ages and kinematics (W22) \add{as well as the success of a two-component model of [Fe/H] and age in predicting APOGEE abundances \citep{ness2019}} suggest that these two 2-dimensional models are somehow interconnected.
 
-Beyond standard CCSN and SNIa enrichment many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep[e.g.,][]{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep[e.g.,][]{kilpatrick2017}, or atypical supernovae explosion \citep[e.g.,][]{nomoto2013}.
+Beyond standard CCSN and SNIa enrichment, many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep[e.g.,][]{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep[e.g.,][]{kilpatrick2017}, or atypical supernova explosions \citep[e.g.,][]{nomoto2013}.
 After predicting stellar abundances from $\feh$ and $\mgfe$, \citet{ting2022} identify correlated abundance residuals that are unexplained by observational uncertainties, indicative of additional nucleosynthetic processes that standard disk CCSN and SNIa enrichment cannot explain.
 Results from G22 and W22 support this conclusion, and both works attempt to add additional processes to their models to account for non-CCSN and non-SNIa enrichment, though in a very restrictive manner.
-Other sources of abundance scatter, such as stochastic sampling of the IMF, IMF variations, and bursty star formation history could also cause deviations away from a two-process model \citep{belokurov2018, griffith2023}.
+Other sources of abundance scatter, such as stochastic sampling of the Initial Mass Function (IMF), IMF variations, and bursty star formation history could also cause deviations away from a two-process model \citep{belokurov2018, griffith2023}.
 
 To date, survey abundances have not been fully exploited to create a data-driven model of nucleosynthesis.
-While works such as \citet{ting2012}, \citet{casey2019}, and \citet{ratcliffe2022} effectively use clustering algorithms to identify elements with like sources and reduce abundance dimensionality, the results are difficult to translate into a model of nucleosynthesis.
-Clustering components can be linked to nucleosynthesis sources and enrichment history, but have not yet been be used to describe the enrichment of a single star.
+While works such as \citet{ting2012}, \citet{casey2019}, and \citet{ratcliffe2020} effectively use clustering algorithms to identify elements with like sources and reduce abundance dimensionality, the results are difficult to translate into a model of nucleosynthesis.
+Clustering components can be linked to nucleosynthesis sources and enrichment history, but have not yet been used to describe the enrichment of a single star.
 
@@
 The parameters output by our model can thus be used as de-noised abundance labels; these will sharpen relationships between abundances and stellar parameters (including birth location and time).
+\add{Our main contribution is to construct a data-driven model for nucleosynthesis that has good statistical properties, only enforcing constraints to break rotational degeneracies.
+All other \name{} parameters are set by the data with no fixed normalization.}
+% Had said some of this in the sentences before...
+%The process parameters are derived Uses a hierarchical statistical model so it combines abundances into K process amplitudes for each star and denoised predicted abundances of each star, and metallicity-dependent effective yields for the processes.
 
@@
 As in W22 and G22, we propose that all stellar abundances can be generated by a combination of $K$ nucleosynthetic processes.
-In this picture, each element has $K$ metallicity-dependent process vector components that are shared across the full stellar sample, while each star individually has $K$ process amplitudes, which apply across all elements, such that
+In this picture, each element has $K$ metallicity-dependent process vector components that are shared across the full stellar sample, while each star individually has $K$ process amplitudes, \add{which apply across all elements, such that the expected logarithmic abundance of element $j$ in star $i$ ($m_{ij}$) is defined as:}
 \begin{equation}\label{eq:mij_k}
-    m_{ij} = \log_{10} \, \sum^K_{k=1} A_i^k \, q_{k,j}^Z ~,
+    m_{ij} = \log_{10} \, \sum^K_{k=1} A_i^k \, q_{k,j}^Z ~.
 \end{equation}
-where stars are labeled by $i$ and elements are labeled by $j$.
 Each star $i$ has $K$ process amplitudes ($A^k_i$)
-and each element $j$ has $K$ process vector components ($q_{k,j}^{Z}$).
-The $m_{ij}$ value is the model expected logarithmic abundance of element $j$ in star $i$. In this model, we put forth the following set of assumptions:
+and each element $j$ has $K$ \add{metallicity dependent} process vector components ($q_{k,j}^{Z}$). 
+\add{The $Z$ superscript denotes the dependence of the process vectors on metallicity, $Z$, taken to be [Mg/H].}
+The $m_{ij}$ value is the model expected logarithmic abundance of element $j$ \add{relative to Hydrogen in star $i$, such that the observed abundance can be expressed}
+\begin{equation}\label{eq:xh}
+    [\text{X}_j/\text{H}]_i = m_{ij} + \text{noise},
+\end{equation}
+\add{where ``noise'' represents observational noise and/or other sources of intrinsic abundance scatter that are not included in this model.}
+
+\add{For example, in the $K=2$ case for a star ($i=40$) with a O abundance of $[\text{O}/\text{H}] =0.155$ and $\mgh = 0.122$, \name{} fits $q_{\text{CC,O}}^{\mgh=0.12} = 0.91$ and $q_{\text{Ia,O}}^{\mgh=0.12} = 0.13$.
+This indicates that at $\mgh = 0.12$, stellar O is dominantly produced by the prompt (CCSN) process.
+For this star, \name{} also derives $A_{40}^{\rm CC} = 1.3$ and $A_{40}^{\rm Ia} = 1.2$ from the abundances of all 15 elements.
+Summing the products of the corresponding process vector component and process amplitude, we find $m_{40,\text{O}} = \log_{10} ( 1.36 ) = 0.135$.
+\name{} predicts the star's O abundance to 0.02 dex, the typical scale of observational noise on [O/H] in APOGEE.
+For more detailed examples from a similar model, see Section 2 of W22.}
+\ejg{Hogg let me know what you think.
+We don't introduce the CC and Ia notation until later in this section so I think if it stays it needs more clarification.
+I lean towards just sending people to Section 2 and Figures 2 and 3 of W22.
+}
+
+In \name{}, we put forth the following set of assumptions:
 
@@
 The majority of $\alpha$, light odd-Z, and Fe-peak elements (the elements observed by APOGEE) are dominantly produced by $K=2$ sources, with one being a prompt process or mix of prompt processes, and one being a delayed process or a mix of delayed processes.
-This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful data-driven models (e.g., G22, W22, \citealp{ting2022}).
+This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful data-driven models (e.g., \citealp{ness2019}, G22, W22, \citealp{ting2022, ratcliffe2023}).
 In this paper we therefore assume that $K \geq 2$, though \name{} could in principle be implemented with $K=1$.
@@
 \begin{equation}\label{eq:qcc_mg_solar}
-    q_{{\rm CC, Mg}}^{\,Z_{\odot}} = 1, \quad q_{k>1,{\rm Mg}}^{\,Z_{\odot}} = 0
+    q_{{\rm CC, Mg}}^{\,Z} = 1, \quad q_{k>1,{\rm Mg}}^{\,Z} = 0
 \end{equation}
-at solar metallicity and 
-\begin{equation}\label{eq:qcc_mg_z}
-    q_{{\rm CC, Mg}}^{\,Z} = q_{{\rm CC, Mg}}^{\,Z_{\odot}}, \quad q_{k>1, {\rm Mg}}^{\,Z} = q_{k>1, {\rm Mg}}^{\,Z_{\odot}}
-\end{equation}
-at all other metallicities.
+at all metallicities.
 
@@
 Fe is produced through a combination of a prompt and delayed process.
-Because the delayed process is likely dominated by SNIa \citep[e.g.,][]{andrews2017}, we label the delayed process with ``Ia''\footnote{While other enrichment channels with similar timescales may be included in the respective processes, the ``CC'' and ``Ia'' naming convention conforms to the choices in W22 and G22, and avoids the possible confusion of process numbers (1 and 2) with supernovae type (II and Ia).}.
+Because the delayed process is likely dominated by SNIa \citep[e.g.,][]{andrews2017}, we label the delayed process with ``Ia''\footnote{While other enrichment channels with similar timescales may be included in the respective processes, the ``CC'' and ``Ia'' naming convention conforms to the choices in W22 and G22, and avoids the possible confusion of process numbers (1 and 2) with supernova type (II and Ia).}.
 While the prompt process constraint (Mg) is grounded in nucleosynthesis theory, there is no equivalent nucleosynthesis fact to constrain the delayed process.
@@
 \begin{equation}\label{eq:qcc_fe_solar}
-    q_{{\rm CC, Fe}}^{\,Z_{\odot}} = 0.4, \quad q_{{\rm Ia, Fe}}^{\,Z_{\odot}} = 1 - q_{{\rm CC, Fe}}^{\,Z_{\odot}} \quad q_{k>2,{\rm Fe}}^{\,Z_{\odot}} = 0
+    q_{{\rm CC, Fe}}^{\,Z} = 0.4, \quad q_{{\rm Ia, Fe}}^{\,Z} = 1 - q_{{\rm CC, Fe}}^{\,Z} \quad q_{k>2,{\rm Fe}}^{\,Z} = 0
 \end{equation}
-at solar metallicity and 
-\begin{equation}\label{eq:qcc_fe_z}
-    q_{{\rm CC, Fe}}^{\,Z} = q_{{\rm CC, Fe}}^{\,Z_{\odot}},  \quad 
-    q_{{\rm Ia, Fe}}^{\,Z} = q_{{\rm Ia, Fe}}^{\,Z_{\odot}} \quad 
-    q_{k>2, {\rm Fe}}^{\,Z} = q_{k>2, {\rm Fe}}^{\,Z_{\odot}}
-\end{equation}
-at all other metallicities.
-This assumption places a star with purely prompt enrichment on the low-metallicity $\mgfe$ plateau near 0.4 dex, in agreement with APOGEE observations but in contention with recent results from \citet{conroy2022} which places the $\mgfe$ plateau near 0.6 dex.
+at all metallicities. 
+This assumption places a star with purely prompt enrichment on the low-metallicity $\mgfe$ plateau near 0.4 dex, in agreement with APOGEE observations but in contention with recent results from \citet{conroy2022} which place the $\mgfe$ plateau near 0.6 dex.
 We explore the impact of different $\qccFe$ assumptions in Section~\ref{subsec:qccFe}.
@@
 We describe the potential data systematics in Section~\ref{sec:data}.
-The APOGEE errors may be slightly underestimated for some element measurements, so we add a softening parameter $Q$ to inflate the uncertainties on abundance-outlier stars (see Equation~\ref{eq:inflate_ivar}).
+\add{For our purposes, we care merely about the statistical observational errors rather than systematics that arise from imperfect modeling of the spectra such as NLTE effects, though differential systematics across the sample can artificially add abundance scatter.
+The actual derived values of $q_{k,j}^{Z}$ will be affected by systematic offsets in the abundances.
+We add a softening parameter $Q$ (Equation~\ref{eq:inflate_ivar}) to allow for the possibility that APOGEE observational errors are underestimated or that there is intrinsic scatter around the \name{} predictions.}
+% The APOGEE errors may be slightly underestimated for some element measurements, so we add a softening parameter $Q$ to inflate the uncertainties on abundance-outlier stars (see Equations~\ref{eq:chi2} and ~\ref{eq:inflate_ivar}).
 
 \paragraph{8. Robust likelihood function}
-The observed value of [X/H] can be described as the $K$ process expectation plus observational noise and/or other sources of intrinsic abundance scatter that are not included in this model:
-\begin{equation} \label{eq:xh}
-    \xh_{ij} = m_{ij} + \text{noise} ~,
+The observed value of [X/H] can be described as the $K$ process expected value plus observational noise and/or other sources of intrinsic abundance scatter, \add{as described by Equation~\ref{eq:xh}.}
+The expression in this equation can be thought of as the key assumption underlying our likelihood function.
+In detail the (negative two times the) log likelihood function is given by a chi-squared ($\chi^2$) objective
+\begin{equation}\label{eq:chi2}
+    \chi^2 = \sum_{ij}\frac{1}{\sigma_{ij}^2} \, (\xh_{ij} - m_{ij})^2 ~,
 \end{equation}
-where $m_{ij}$ is the expectation value given in Equation \ref{eq:mij_k} for star $i$ and element $j$.
-The expression in Equation \ref{eq:xh} can be thought of as the key assumption underlying our likelihood function.
-In detail the (negative two times the) log likelihood function is given by a chi-squared ($\chi^2$) objective
-\begin{equation}
-    \chi^2 = \sum_{ij} \, \frac{1}{\sigma_{ij}^2} \, (\xh_{ij} - m_{ij})^2 + Q ~,
-\end{equation}
-where $1/\sigma_ij^2$ is the (robust; see below) inverse variance on measurement $ij$,
-and $Q$ is a light regularization that depends on the parameters.
+where $1/\sigma_{ij}^2$ is the (robust; see below) inverse variance on measurement $ij$.
 
@@
 \end{equation}
-where $Q$ is a softening parameter, which is set to $Q=5$.
+where $Q$ is a softening parameter.
+\add{Our results are largely insensitive to the choice of $Q$ (e.g., $1 < Q < 10$), so we choose to set $Q=5$.
+Very small values (e.g., $Q=.1$) will erase some of the abundance structure and produce poorer fits.}
 
@@
 It subsequently optimizes the process amplitudes (dubbed the $A$-step) using only Mg and Fe at fixed process vector components, and then optimizes the process vector components (dubbed the $q$-step) for all elements at fixed process amplitudes.
-The $A$-step and $q$-step are alternated, repeating 48 rounds of optimization and updating the best-fit parameters when the objective function improves.
+The $A$-step and $q$-step are alternated, repeating 48 rounds of optimization, \add{in the $K=2$ case,} and updating the best-fit parameters when the objective function improves.
 We find few differences in the best-fit parameters when we decrease the number of iterations to 32, indicating that the model quickly finds a good solution.
@@
 \bigskip
-\name{} mirrors the two-proccess model from prior work (G22, W22) but, unless otherwise noted, the assumptions weaker, there is a likelihood function in play, and the implementation is more general.
+\name{} mirrors the two-proccess model from prior work (G22, W22) but, unless otherwise noted, the assumptions are weaker, there is a likelihood function in play, and the implementation is more general.
 In particular, we don't assume anything about the relationships between the process vector components and the morphologies of observed element-abundance ratio diagrams.
@@
 The APOGEE survey obtains high-resolution ($R\sim22,500$) near-infrared (IR) observations \citep{wilson2019} for stars in the Galactic disk, halo, bulge, and nearby satellites/streams.
-Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Companas Observatory in Chile.
+Observations are taken with two nearly identical spectrographs on the 2.5m Sloan Foundation telescope \citep{wilson2019} at Apache Point Observatory in New Mexico and the 2.5m du Pont Telescope \citep{bowen1973} at the Las Campanas Observatory in Chile.
 Spectral data are reduced and calibrated with the APOGEE data processing pipeline \citep{nidever2015}, after which stellar parameters and abundances are calculated with ASPCAP \citep[APOGEE Stellar Parameter and Chemical Abundance Pipeline;][]{holtzman2015, garcia2016}.
 See \citet[][DR16]{jonsson2020} and Holtzman et al.
-(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017} and \citet{santana2021} for a discussion of survey targeting.
+(in prep., DR17) for a more detailed description of APOGEE data reduction and analysis, and \citet{zasowski2013, zasowski2017}, \citet{beaton2021}, and \citet{santana2021} for a discussion of survey targeting.
 
@@
 Both P and V display strong abundance artifacts and large scatter.
-Among the remaining elements, we note the following concerns: weak Na spectral features, large abundances scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, strong unaccounted for NLTE effects on Mn abundances, and large abundance scatter in Co and Ce---both derived from one line.
+Among the remaining elements, we note the following concerns: weak Na spectral features, large abundance scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, potentially strong unaccounted-for NLTE effects on Mn abundances \citep{bergemann2019}, and large abundance scatter in Co and Ce---both derived from one line.
 Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
-For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
+\ejg{Comments that this is not correct and more Ce lines are used, but the DR17 paper isn't out yet.
+Sten to help.} For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
 
@@
 \end{itemize}
-To eliminate red clump (RC) stars, which show abundance variations from the RGB sample \citep{vincenzo2021a}, we cross-match with and remove stars that appear in the APOGEE RC VAC \citep{bovy2014}.
-These cuts result in a sample of 48,659 stars.
+To eliminate red clump (RC) stars, which show abundance variations from the RGB sample \citep{vincenzo2021a}, we cross-match with and remove stars that appear in the APOGEE DR17 RC VAC\footnote{\url{https://www.sdss4.org/dr17/data_access/value-added-catalogs/?vac_id=apogee-red-clump-(rc)-catalog}} \citep{bovy2014}.
 
-We present abundance for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, Mn, Co, and Ce.
-In the analysis of each element, X, we drop stars with \texttt{X\_FE\_FLAG} (maximum of $\sim 700$ for Ce).
+These cuts result in a sample of 48,659 stars \add{that span the Galactic disk.
+We plot their $Z$ vs.
+$R$ distribution, as well as the distributions of distances and eccentricities in Figure~\ref{fig:star_dist}, taking distances and kinematics from \citep{queiroz2023}.
+While our stellar sample extends from Galactic center, to the outer disk, to the halo, the majority of our stars ($75\%$) are within 3.5 kpc of the sun.
+Further, $94\%$ of our stellar sample has an eccentricity less than 0.4, indicative of \textit{in situ} origin.
+In this paper, we assume that the KPM fits will be consistent across the Galactic disk, as the median high-Ia and low-Ia [X/Mg] vs.
+[Mg/H] abundance tends are insensitive to Galactic location (W19, \citealp{griffith2021a}.}
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/star_sample.pdf}
+    \caption{\add{Left: distribution of our stellar sample in $Z$ (kpc) vs.
+$R$ (kpc).
+Center: distribution of distances (kpc).
+Right: distribution of eccentricity.
+Our stellar sample spans the Galactic disk, but the majority of our stars are within 3.5 kpc of the sun.}}
+    \label{fig:star_dist}
+\end{figure*}
+
+We present abundances for Mg, O, Si, S, Ca, C+N, Na, Al, K, Cr, Fe, Ni, Mn, Co, and Ce.
+In the analysis of each element, X, we drop stars with \texttt{X\_FE\_FLAG}.
+Ce has the most problematic abundances, with $\sim 700$ flagged stars.
 While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge-up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
@@
 [Mg/H] abundance distribution of the fiducial plus estimated noise.
-Third column: process vector components $\qcc$ (purple) and $\qIa$ (orange) from this work (G23, solid, dark lines) and W22 (light, dashed lines).
-Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial model.
+\add{By comparing the first two columns we can evaluate the success of \name{} in reproducing the observed abundance distributions.} Third column: process vector components $\qcc$ (thin, purple) and $\qIa$ (thick, orange) from this work (G23, solid, dark lines) and W22 (light, dashed lines).
+\add{Overall offsets between the solid and dashed lines are driven largely by our normalization that places the [Mg/Fe] plateau at $+0.4$, rather than $+0.3$ in W22.} Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial model.
 We plot the median $\fcc$ values of the low-Ia (orange square) and high-Ia (purple circle) populations in the solar metallicity bin from W22 for comparison.}
@@
 \end{equation}
-with the assumptions from SEction~\ref{sec:model}.
+with the assumptions from Section~\ref{sec:model}.
 This fit produces process vector components $\qcc$ and $\qIa$ as a function of $\mgh$ for each element and process amplitudes $\Acc$ and $\AIa$ for each star.
-From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted $K=2$ process abundances.
+From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted $K=2$ process abundances, \add{shown in the second column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}}.
 
@@
 By definition, $\qccFe=0.4$ at all metallicities.
-For Fe only, we also require $\qccFe + \qIaFe = 1$, implying $\qIaFe=0.6$.
-No such constraints are placed on any other element.
+For \add{Mg and} Fe, we also require $\qcc + \qIa = 1$, implying $\qIaFe=0.6$.
+No such constraints are placed on other elements.
+\add{We note that \name{} differs from the previous two-process models in this regard, as G22 and W22 require that the process vectors for all elements sum to 1 at solar metallicity.}
 
@@
 This is in agreement with theoretical prediction that $\alpha$-elements are dominated by prompt CCSN production \citep[e.g.][]{andrews2017}.
-O, a Mg-like element theoretically purely produced in prompt CCSN, shows $\fcc$ near 1 from $\mgh=-0.75$ to solar.
-At supersolar $\mgh$, the delayed process contributes to O production, driving the $\fcc$ value down to $\sim 0.8$ at $\mgh=0.4$.
+O, a Mg-like element theoretically purely produced in prompt CCSN, shows $\fccX{O}$ near 1 from $\mgh=-0.75$ to solar.
+At supersolar $\mgh$, the delayed process contributes to O production, driving the $\fccX{O}$ value down to $\sim 0.8$ at $\mgh=0.4$.
 S behaves like O, with almost entirely prompt production up to solar metallicity, after which delayed enrichment contributes more significantly.
 Conversely, we find that Si and Ca are best fit with prompt and delayed enrichment at all metallicities, though the prompt process always dominates.
-For Si, the delayed process appear to increase linearly with $\mgh$, while the Ca delayed enrichment increases from $\mgh$ of $-0.75$ to $-0.1$ and then decreases from $\mgh$ of $-0.1$ to $0.5$.
+For Si, the delayed process appears to increase linearly with $\mgh$, while the Ca delayed enrichment increases from $\mgh$ of $-0.75$ to $-0.1$ and then decreases from $\mgh$ of $-0.1$ to $0.5$.
 
@@
 Both exhibit $\qcc$ and $\fcc$ near 1 through solar metallicity, with an increase in $\qIa$ and downturn in $\fcc$ at supersolar metallicities (especially for K).
-The behavior of the Na process vector components is more complex, with peaks and troughs in $\qIa$.
-We find that Na has the strongest contributions from the delayed process of all $\alpha$ and light odd-$Z$ elements, with $\qIa \gtrsim 0.5$ at almost all values of $\mgh$ and $\fcc < 0.3$ at $\mgh > 0$.
+The behavior of the Na process vector components is more complex, with peaks and troughs in $\qIaX{Na}$.
+We find that Na has the strongest contributions from the delayed process of all $\alpha$ and light odd-$Z$ elements, with $\qIaX{Na} \gtrsim 0.5$ at almost all values of $\mgh$ and $\fccX{Na} < 0.3$ at $\mgh > 0$.
 The strong delayed contribution to Na is in agreement with findings of W22 and G22, and in tension with theoretical yields \citep[e.g.][]{andrews2017, rybizki2017}.
@@
 We find that the prompt and delayed processes both contribute significantly, and nearly equally, across our stellar sample.
-Though theoretical N yields from AGB stars have a strong metallicity dependence \citep{karakas2010, ventura2013, cristallo2015, johnson2022}, we observe only a slight positive metallicity dependence in $\qcc$ and a shallow dip in $\qIa$.
-We find a population of stars with $\fcc$ near 0.9 and a population near 0.4.
+Though theoretical N yields from AGB stars have a strong metallicity dependence \citep{karakas2010, ventura2013, cristallo2015, johnson2022}, we observe only a slight positive metallicity dependence in $\qccX{C+N}$ and a shallow dip in $\qIaX{C+N}$.
+We find a population of stars with $\fccX{C+N}$ near 0.9 and a population near 0.4.
 
@@
 By construction, $\qccFe=0.4$ and $\qIaFe=0.6$ at all metallicities.
-This produces a bimodal distribution in $\fcc$ similar to that observed in abundances space.
-Because of our choice of $\qccFe$, only a few stars have $\fcc=1$ (see Section~\ref{subsec:qccFe}).
-We instead observe a population with $\fcc$ near 0.8 and a population near 0.4.
-The process vector components and $\fcc$ distribution for Cr and Ni strongly resemble those of Fe.
+This produces a bimodal distribution in $\fcc$ similar to that observed in abundance space.
+Because of our choice of $\qccFe$, only a few stars have $\fccX{Fe}=1$ (see Section~\ref{subsec:qccFe}).
+We instead observe a population with $\fccX{Fe}$ near 0.8 and a population near 0.4.
+The process vector components and $\fccX{Fe}$ distribution for Cr and Ni strongly resemble those of Fe.
 All three elements have even atomic numbers.
 At supersolar metallicity, we find that the prompt process dominates Cr production, resulting in an upturn in $\fcc$.
-Conversely, Ni displays a dominant, and increasing, delayed proccess vector component at supersolar metallicities.
+Conversely, Ni displays a dominant, and increasing, delayed process vector component at supersolar metallicities.
 The process vector components for Mn and Co (odd atomic numbers) show a complex metallicity dependence, more resembling that of Na.
-Both elements display a strong delayed process, with the Mn $\qIa > 0.5$ at all metallicities and $> 1$ for $\mgh > 0.1$.
-Mn is the only element for which $\fcc$ decreases to 0 for $\mgh \gtrsim 0.2$.
+Both elements display a strong delayed process, with the $\qIaX{Mn} > 0.5$ at all metallicities and $> 1$ for $\mgh > 0.1$.
+Mn is the only element for which $\fccX{Mn}$ decreases to 0 for $\mgh \gtrsim 0.2$.
 
-Finally, we find that the delayed process dominates Ce production at intermediate metallicity, with $\qIa$ increasing up to $\mgh \approx -0.2$ and then decreasing to nearly 0 at $\mgh \approx 0.3$.
-The Ce $\fcc$ values are clustered near 0.25 around $\mgh$ of 0.2, then increase such that the abundances are almost entirely dominated by prompt enrichment at high metallicity.
+Finally, we find that the delayed process dominates Ce production at intermediate metallicity, with $\qIaX{Ce}$ increasing up to $\mgh \approx -0.2$ and then decreasing to nearly 0 at $\mgh \approx 0.3$.
+The $\fccX{Ce}$ values are clustered near 0.25 around $\mgh$ of 0.2, then increase such that the abundances are almost entirely dominated by prompt enrichment at high metallicity.
 
 In addition to process vector components, each star is fit with a prompt and delayed process amplitude, $\Acc$ and $\AIa$ respectively.
-All elemental abundance are used in the calculation of these amplitudes, so they can be interpreted as ``de-noised'' abundance labels.
+All elemental abundances are used in the calculation of these amplitudes, so they can be interpreted as ``de-noised'' abundance labels \add{that suppress observational scatter by averaging over elements via the data-driven model}.
 The value of $\Acc$ traces the metallicity (specifically $\mgh$) while the ratio of $\AIa/\Acc$ traces the $\femg$ abundance.
@@
 The stars with larger $\AIa/\Acc$ values correspond to the high-Ia population, and those with low $\AIa/\Acc$ correspond to the low-Ia population.
-While in the Tinsley-Wallerstain diagram the two populations blend together at high-metallicity, they are more distinguishable in amplitude space.
-To further show this, we plot $\AIa/\Acc$ vs.
-$\mgh$ in the right panel of Figure~\ref{fig:As}.
-The high-Ia and low-Ia populations are clearly seperable through $\mgh$ of 0.4.
+While in the Tinsley-Wallerstein diagram the two populations blend together at high-metallicity, they are more distinguishable in amplitude space.
+We plot $\AIa/\Acc$ vs.
+$\mgh$ in the center panel of Figure~\ref{fig:As}.
+The high-Ia and low-Ia populations are clearly separable through $\mgh$ of 0.4.
+\add{This is further shown through the $\AIa/\Acc$ distributions in the right panel of Figure~\ref{fig:As} for [Mg/H] bins of $-0.75$ to $-0.425$, $-0.425$ to $-0.1$, $-0.1$ to 0.225, and 0.225 to 0.55.
+The three lowest metallicity bins display a bimodal distribution and the highest metallicity bin is dominated by high-Ia stars.}
 
@@
     \centering
-    \includegraphics[width=.9\textwidth]{Paper/Figures/As.pdf}
+    \includegraphics[width=\textwidth]{Paper/Figures/As.pdf}
     \caption{Left: distribution of $\AIa/\Acc$ vs.
 $\Acc$ for the fiducial model.
-Right: distribution of $\AIa/\Acc$ vs.
+\add{This plot is similar to a [Fe/Mg] vs.
+[Mg/H] distribution where $\AIa/\Acc$ is a proxy for [Fe/Mg] and $\Acc$ is a proxy for [Mg/H].
+Note that $\Acc = 1$ corresponds to $\mgh = 0$}.
+Center: distribution of $\AIa/\Acc$ vs.
 $\mgh$.
-In both panels we can clearly see the bimodality to high values of $\Acc$ and $\mgh$.}
+In the left and center panels, we can clearly see the bimodality to high values of $\Acc$ and $\mgh$.
+\add{Right: distribution of $\AIa/\Acc$ for ranges of [Mg/H] with metallicity bin increasing from top to bottom.
+[Mg/H] bins are of width 0.325 dex and span $-0.75$ to 0.55.}}
     \label{fig:As}
@@
 In Figure~\ref{fig:all_param1} and~\ref{fig:all_param2} we plot the predicted abundances plus estimated noise in the second columns.
-These distributions can be compared the the observed abundance distribution in the first columns.
+These distributions can be compared to the observed abundance distribution in the first columns.
 
@@
 This is especially noticeable at low-metallicity for C+N, Na, Al, K, Co, and Ce.
-For these elements the scatter in the observed abundance distribution is much larger than in the predicted distribution, suggesting that either the $K=2$ model is insufficient or that the APOGEE scatter is underestimated.
+For these elements the scatter in the observed abundance distribution is much larger than in the predicted distribution, suggesting that either APOGEE observational scatter is underestimated or that the $K=2$ model is insufficient--\add{a likely case for elements produced by AGB stars, such as C+N and Ce }.
 
@@
 
-As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, \name{} is based upon the two-process model developed in W19 and W22, but with increased flexibility and no forced dependence upon the [Fe/Mg] vs.
+As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, \name{} is based upon the two-process model developed in W19 and W22, but with increased flexibility, \add{minimal normalization}, and no forced dependence upon the [Fe/Mg] vs.
 [Fe/H] bimodality or population abundance trends.
-Further, the \name{} utilizes all stellar abundances in the optimization of $\Acc$ and $\AIa$, where as only Mg and Fe are used in W19 and only Mg, O, Si, Ca, Fe, and Ni in W22.
+Further, the \name{} utilizes all stellar abundances in the optimization of $\Acc$ and $\AIa$, whereas only Mg and Fe are used in W19 and only Mg, O, Si, Ca, Fe, and Ni in W22.
 
@@
 In practice, this moves the implied ``pure'' CCSN enrichment plateau from $\femg=-0.3$ to $\femg=-0.4$ (though the W22 plateau value is determined \textit{after} they apply a global offset of +0.05 to all $\femg$ abundances).
-Because our model is non-negative, it requires a lower $\qccFe$ to correctly model the stars on the $\femg$ plateau, where as W22 assigns stars with $\femg < -0.3$ negative $\AIa$ values.
+Because our model is non-negative, it requires a lower $\qccFe$ to correctly model the stars on the $\femg$ plateau, whereas W22 assigns stars with $\femg < -0.3$ negative $\AIa$ values.
 
-While our stellar samples and model assumptions differ, we plot the W22 $\qcc$ and $\qIa$ vector components as well as the W22 solar metallicity $\fcc$ values in of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2} for comparison with our fiducial model.
+While our stellar samples and model assumptions differ, we plot the W22 $\qcc$ and $\qIa$ vector components as well as the W22 solar metallicity $\fcc$ values of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2} for comparison with our fiducial model.
 We generally observe similar behavior between \name{} and W22.
@@
 It is important to note that in the calculation of the W22 model residuals, we do not apply the temperature corrections discussed in Section 5.1 of W22.
-We find that, overall, the $\log(\chi^2)$ decreases between the W22 two-process model and our $K$-process model, an indication that we better predict the stellar abundances.
+
+We find that, overall, the $\chi^2$ decreases between the W22 two-process model and our $K$-process model, an indication that we better predict all of a star's abundances.
 When looking at each element individually, we find that we better predict C+N, Na, K, Ni, Mn, Co, and Ce, with major improvements to C+N and Mn.
@@
 Because \name{} uses all elements in its optimization, Mg, Ca, and Fe are effectively de-weighted relative to the W22 model, while C+N and Mn influence the model parameters.
+\add{If we re-fit \name{} using only the Mg, O, Si, Ca, Fe, and Ni abundances in the $A$-step (as in W22), we find that \name{} and the two-process model predict the abundances of all elements but Mn with similar accuracy, and that the two-process model better predicts Mn.
+Our fiducial model's success in predicting C+N and Mn is likely attributable to the inclusion of the elements in the $A$-step.
+The choice to include all elements or a subset of elements in the fits should be considered when implementing \name{}.
+If searching for stars with anomalous abundances of element X relative to the expected abundances of other elements, one may want to exclude X from the $A$-step.}
 
@@
     \includegraphics[width=\textwidth]{Paper/Figures/comp_w22.pdf}
-    \caption{Left: cumulative distribution of $\log \chi^2$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line). Right: $\chi^2$ per element for the same model fits. }
+    \caption{Left: cumulative distribution of $\log \chi^2$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line).
+Right: $\chi^2$ per element for the same model fits with elements ordered by atomic number.
+\add{Overall, our model has a smaller cumulative $\chi^2$ than the previous two-process model and better predicts the abundances of C+N, Na, K, Mn, Co, Ni, and Ce.}}
     \label{fig:comp_w22}
@@
 
-\subsection{Choice of $\qccFe$} \label{subsec:qccFe}
+\subsection{\add{Impact of Fe Process Assumptions}} \label{subsec:qccFe}
 
@@
 Specifically, for each process, we choose one element to assign a ``known'' process vector element at all metallicities.
-These are Mg and Fe in the 2-process case.
+These are Mg and Fe in the $K=2$ case.
 Specifically, for the prompt process, we ground our assumption in the nucleosynthetic theory that Mg is a pure CCSN element \citep[e.g.,][]{andrews2017}.
-Unfortunately there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
-In order to break an exact degeneracy between the prompt and delayed processes, we choose to fix the Fe process vector components, making unsubstantiated assumptions about Fe enrichment.
+Unfortunately, there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
+In order to break an exact degeneracy between the prompt and delayed processes, we choose to fix the Fe process vector components, \add{which effectively makes assumptions about the exact fractional contribution of CCSN and SNIa (or prompt and delayed processes) to Fe enrichment.}
 
@@
 We repeat the optimization of the \name{} with $K=2$ and these $\qccFe$ assumptions.
-In Figure~\ref{fig:qccFe_FeMgpred}, we plot the resulting predicted abundance distributions plus estimated noise.
+In Figure~\ref{fig:qccFe_FeMgpred}, we plot the resulting predicted abundance distributions plus estimated noise \add{alongside the observed distribution}.
 We do not plot the prediction for the fiducial model ($\qccFe=0.4$, $\dqccFe=0.0$), as this is shown in Figure~\ref{fig:all_param2}.
@@
     \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMgpred.pdf}
-    \caption{Predicted [Fe/Mg] vs.
-[Mg/H] abundance distributions plus estimated noise for models with $\dqccFe=0.0$ (top row) and $\dqccFe=0.15$ (bottom row).
+    \caption{\add{Top: observed [Fe/Mg] vs.
+[Mg/H] abundance distribution.} Bottom: predicted [Fe/Mg] vs.
+[Mg/H] abundance distributions plus estimated noise for models with $\dqccFe=0.0$ (middle row) and $\dqccFe=0.15$ (bottom row).
 The $\qccFe$ value increase from left to right from 0.35 to 0.5.
-$\qccFe$ and $\dqccFe$ parameters are listed in each panel.}
+\add{Note that the center panels have different $\qccFe$ values (middle: 0.45, bottom: 0.4) and that the predicted abundance distribution for $\qccFe=0.4$ and $\dqccFe=0.0$ can be found in Figure~\ref{fig:all_param2}}.
+The $\qccFe$ and $\dqccFe$ parameters are listed in each panel.
+\add{By comparing the lower panels to the observed distribution (top) we can evaluate the success or failure of each model; the low-Ia population is most sensitive to the Fe assumptions.} \ejg{Looks brown???}}
     \label{fig:qccFe_FeMgpred}
@@
 Of the seven models explored here, the case with $\qccFe=0.4$ and $\dqccFe=0.15$ has the lowest average $\chi^2$ per star, indicating that the Fe abundances are best fit by a metallicity dependent prompt process.
+\add{Introducing this metallicity dependence subtly changes the shape of the predicted low-Ia distribution in a way that achieves better agreement with APOGEE observations.}
 
-Though the $\qccFe= 0.4$ and 0.35 models are similar in terms of their goodness of fit, their nucleosynthesis implications are more significant.
+Though the $\qccFe= 0.4$ and 0.35 models are similar in terms of their goodness of fit, their nucleosynthesis implications are different.
 In Figure~\ref{fig:qccFe_fcc}, we plot the median value of $\fcc$ (Equation~\ref{eq:fcc}) for the low-Ia population at solar metallicity ($-0.05 < \mgh < 0.05$), where low-Ia stars are defined by
@@
     \includegraphics[width=\textwidth]{Paper/Figures/qccFe_fcc.pdf}
-    \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for \name{} with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.}
+    \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for \name{} with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.
+\add{Elements are ordered by atomic number.
+The median $\fcc$ changes most dramatically for elements with strong delayed contributions.}}
     \label{fig:qccFe_fcc}
@@
 In our fiducial model, we adopt $K=2$ with the two processes representing prompt, CCSN-like enrichment and delayed, SNIa-like enrichment.
-While a $K=2$ model can well describe the stellar abundances (e.g., Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}), the abundance residuals cannot be explained by observational noise alone and hold information about the intrinsic variations from a $K=2$ model (G22, W22, \citealp{ting2022}).
+While a $K=2$ model can well describe the stellar abundances (e.g., Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}), the abundance residuals cannot be explained by observational noise alone and hold information about the intrinsic variations from a $K=2$ model (\citealp{ness2019} G22, W22, \citealp{ting2022, ratcliffe2023}).
 Potential sources of such scatter include metallicity-dependent SN yields with a bursty star formation history, environmental variations in the IMF, stochastic sampling of the IMF, and more than two distinct processes (e.g., AGB stars, merging neutron stars, and unique classes of SNIa) with different time delays for enrichment \citep[e.g.][]{belokurov2022, griffith2023}.
+\add{Note that the existence of many enrichment channels is not in itself sufficient for producing scatter around a $K=2$ model (or even a $K=1$ model); one needs star-to-star variation in the relative amplitude of these channels.
+For example, in a fully mixed one-zone model, all abundances depend only on time, even if many enrichment channels contribute.}
 
-In this section, we will explore the impact of adding additional processes to our model, increasing from $K=2$ to $K=4$.
+In this Section, we will explore the impact of adding additional processes to our model, increasing from $K=2$ to $K=4$.
 Our goal is to demonstrate the potential of using \name{} to capture more of the observed abundance diversity.
@@
 We take a more flexible approach, allowing the model to identify the elements best-fit with additional components and modify the $K=2$ process parameters.
-Ultimately, such a method could be used to identify elements with more than two enrichment channels, but we will refrain from over-interpretation here.
+Ultimately, such a method could be used to identify elements with more than two enrichment channels, \add{but our data set may not be capable of doing so robustly}.
 Our model now includes four components, such that
@@
 The model, however, does require some regularization to converge.
-As in the $K=2$ case where we assume that Mg is a pure CCSN element and fix the $\qccFe$ and $\qIaFe$ values, we need elements to regulate of our 3rd and 4th processes.
-We choose Ce and Mn, two elements with larger residuals that likely have additional nucleosynthetic sources---Ce from AGB stars and Mn from unique classes of SNIa \citep[e.g.][]{gallino1998, reyes2020, gronow2021}.
-We initialize the $K=4$ model at the $K=2$ model values of $\qcc$, $\qIa$, $\Acc$, and $\AIa$ with the added constraints that
+As in the $K=2$ case where we assume that Mg is a pure CCSN element and fix the $\qccFe$ and $\qIaFe$ values, we need elements to regulate our 3rd and 4th processes.
+We choose Ce and Mn, two elements with larger residuals that likely have additional nucleosynthetic sources---Ce from AGB stars and Mn from distinct classes of SNIa \citep[e.g.][]{gallino1998, reyes2020, gronow2021}.
+\ejg{why do we choose these and what happens if we choose others?} We initialize the $K=4$ model at the $K=2$ model values of $\qcc$, $\qIa$, $\Acc$, and $\AIa$ with the added constraints that
 \begin{equation}\label{eq:q3_z}
@@
     q_{{\rm 4, Mn}}^{\,Z} = 1, \quad 
-    q_{{\rm 4, Ce}}^{\,Z} = 0. \quad 
+    q_{{\rm 4, Ce}}^{\,Z} = 0 \quad 
 \end{equation}
+at all metallicities.
 We first fit the $A$-step to only Mg, Fe, Mn, and Ce, and then conduct 32 iterations of the $q$-step and $A$-step, as described in Section~\ref{sec:model}.
-We again inflate the according to Equation~\ref{eq:inflate_ivar} with $Q=5$.
+We again inflate the scatter according to Equation~\ref{eq:inflate_ivar} with $Q=5$.
 
@@
 The model parameters themselves are less directly interpretable, as we set the third and fourth process vector components for Ce and Mn to an arbitrary value with no metallicity dependence, so we do not show them here.
-We calculate $\fcc$, $f_{{\rm Ia}, ij}$, $f_{3, ij}$, and $f_{4, ij}$ for each abundance of each star where
+\ejg{Weinberg says this is a cop-out and we should add something about the vectors...} We calculate $\fcc$, $f_{{\rm Ia}, ij}$, $f_{3, ij}$, and $f_{4, ij}$ for each abundance of each star where
 \begin{equation}\label{eq:fX}
@@
 \end{equation}
-We find that the third process, regularized to Ce, contributes minorly to O, Si, S, Al, and K and more significantly to Ca, Na, Cr, and Ce.
-The fourth process, regularized to Mn, contributes minorly to K and more significantly to S, C+N, Na, Cr, Ni, Mn, and Co.
+We find that the third process, regularized to Ce, contributes at a low level to O, Si, S, Al, and K and more significantly to Ca, Na, Cr, and Ce.
+The fourth process, regularized to Mn, contributes at a low level to K and more significantly to S, C+N, Na, Cr, Ni, Mn, and Co.
 These best-fit element groupings resemble but are not identical to the elements selected for additional components in W22, where the third process included Ca, Na, Al, K, Cr, and Ce and the fourth process included Ni, V, Mn, and Co.
@@
 Adding model components increases the abundance diversity that \name{} can achieve.
-In the left-most columns of Figure~\ref{fig:all_paramK}, we plot the $\xmg$ v.s.
+\ejg{Clarify what abundance diversity means and how significant the improvement is.
+Rewrite so that we don't invalidate that two processes are sufficient to describe abundance features.} In the left-most columns of Figure~\ref{fig:all_paramK}, we plot the $\xmg$ v.s.
 $\mgh$ distributions for the observed stellar sample, the $K=2$ model predictions, and the $K=4$ model predictions for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
-We note that the predicted abundances do \textit{not} have noise added (unlike Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}).
+We note that the predicted abundances do \textit{not} have noise added (unlike Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}) \add{to highlight the differences between the $K=2$ and $K=4$ predictions}.
 Comparing the predicted abundances from the $K=2$ and $K=4$ process models, we see that the $K=4$ process model is better able to capture the observed abundance distribution than the $K=2$ model.
 Specifically, it better captures the scatter in the low metallicity end of the low-Ia population.
+\ejg{Notes from Weinberg: Not adding the noise helps in comparing the K=2 and K=4.
+However, I don't think you can conclude from this figure that the K=4 model fits the data better because you have to add errors to make the comparison.
+I think a good diagnostic would be P(X/Mg) at a couple of specified (Mg/H) values for the data and the K=2,4 models with APOGEE errors added.}
 
@@
 [Mg/H] abundance distributions for the observed sample (first column), $K=2$ model (second column) and $K=4$ model (third column) for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
-Right: median fractional contribution from each process for the $K=4$ (solid lines) and $K=2$ (dashed lines) models to the low-Ia population as a function of $\mgh$.
+\add{Observational errors are \textit{not} added to the model predictions.} Right: median fractional contribution from each process for the $K=4$ (solid lines) and $K=2$ (dashed lines) models to the low-Ia population as a function of $\mgh$.
 We plot the median $\fcc$ in light purple, $f_{{\rm Ia}, ij}$ in dark purple, $f_{3, ij}$ in light orange, and $f_{4, ij}$ in dark orange as well as a dotted grey line at 0 for reference.}
@@
 With the additional components able to account for the non-Fe-like enrichment, the original two processes are better able to capture the Fe enrichment.
+\ejg{Weinberg comment: Better $\chi^2$ is guaranteed right because more freedom of fit?
+maybe you want to plot the distribution of $\chi^2_2 - \chi^2_4$ and show that it typically improves by more than 2.}
 
@@
     \caption{Left: cumulative distribution of $\log \chi^2$ for the $K=2$ model (solid dark purple line) and our the $K=4$ model (dotted light purple line).
-Right: $\chi^2$ per element for the same model fits.}
+Right: $\chi^2$ per element for the same model fits.
+Elements are ordered by atomic number.}
     \label{fig:comp_Ks}
@@
 
-In this paper, we present \name{}, a flexible and data-driven model of for nucleosynthesis.
+In this paper, we present \name{}, a flexible and data-driven model for inferring nucleosynthesis yields.
 \name{} describes stellar abundances as the sum of $K$ components, where each component is the product of a metallicity-dependent process vector component (fit to each element) and a process amplitude (fit to each star).
@@
 
-We fit \name{} with $K=2$ to 15 abundances labels for 48,659 RGB stars in APOGEE DR17, selecting a population that minimizes statistical and systematic errors while spanning an [Mg/H] of -0.8 to 0.5.
+We fit \name{} with $K=2$ to abundances labels for 15 elements and 48,659 RGB stars in APOGEE DR17, selecting a population that minimizes statistical and systematic errors while spanning an [Mg/H] of -0.8 to 0.5.
 In the $K=2$ model, the first process, fixed to Mg, represents prompt CCSN-like enrichment, and the second process, fixed to Fe, represents delayed SNIa-like enrichment---but other nucleosynthetic sources with similar time delays may be mixed into each.
-Overall, we find that $K=2$ is a good fit to the data and that the model successfully recovers the global abundance patterns in the Milky Way.
+\add{Under our adopted assumptions, the prompt process also contributes to Fe, but the delayed process does not contribute to Mg, in accordance with theoretical expectations for CCSN and SNIa.} Overall, we find that $K=2$ is a good fit to the data and that the model successfully recovers the global abundance patterns in the Milky Way.
 While \name{} does not rely on $\femg$ vs.
 $\mgh$ bimodality or median abundance trends, it is able to recover the observed bimodal abundance distribution.
-Further, the fit parameters $\Acc$ and $\AIa$ act as ``denoised'' abundance labels, and reveal a clearer signature of bimodality at high-metallicity in $\AIa/\Acc$ vs.
+Further, the fit parameters $\Acc$ and $\AIa$ act as ``denoised'' abundance labels, revealing a clearer signature of bimodality at high-metallicity in $\AIa/\Acc$ vs.
 $\mgh$ space than in $\femg$ vs.
@@
 This suggests that the \name{} fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are condensing information from 15 elements into two variables.
+\ejg{Hogg, BR asks if As are truly denoised or if they are just in a different dimensional space (vs.
+mij which are denoised abundances).}
 
 To test the assumptions of the fiducial model, we explore the impact of varying the fixed value of $\qccFe$.
-We find that high values of $\qccFe$ (0.5 and 0.45) are not able to reproduce the observed [Fe/Mg] vs [Mg/H] abundance distribution, regardless of the process vector component's metallicity dependence, and that values $\qccFe = 0.4$ and 0.35 with $\dqccFe = 0$ or 0.15 produces similarly successful fits.
-While predicted abundance distributions appear similar for these models, the implied fractional contribution from the prompt process is strongly dependent upon the Fe assumption for elements with substantial delayed enrichment.
+We find that high values of $\qccFe$ (0.5 and 0.45) are not able to reproduce the observed [Fe/Mg] vs [Mg/H] abundance distribution, regardless of the process vector component's metallicity dependence.
+\add{Our requirement that $\Acc$ and $\AIa$ are non-negative makes it impossible for the model to reproduce the lowest $\femg$ values in the APOGEE data.} Values $\qccFe = 0.4$ and 0.35 with $\dqccFe = 0$ or 0.15 produces similarly successful fits.
+While predicted abundance distributions appear similar for these models, the implied fractional contribution from the prompt process is dependent upon the Fe assumption for elements with substantial delayed enrichment.
 Through this exploration, we conclude that the quantitative nucleosynthetic interpretation of \name{} is dependent upon the input assumptions, and that there is inherent uncertainty in the $\fcc$ values.
@@
 We find that S, Ca, C+N, Na, Cr, Mn, Co, Ni, and Ce are best fit with a third and/or fourth component, with such processes contributing most significantly at low metallicity.
+\add{The information for constraining the $q^{Z}_{k,j}$ values for the third (fourth) process come from the star-by-star deviations of Ce (Mn) from the $K=2$ model predictions and their correlation with deviations for other elements $X_i$.
+Relative to the approach taken in W22 (Section 8), our $K=4$ model requires non-negative $q^Z_{k,j}$ and $A_i^k$ for all elements and stars, and it starts by tying the third and fourth processes to individual elements rather than groups of elements.}
 The $K=4$ model improves the ability of \name{} to fit the abundances of all elements but especially improves predictions of Ca, C+N, Fe, Mn, and Ce.
@@
 \name{}, on the other hand, employs a likelihood function fit to all stars and all elements to derive both process amplitudes and vector components.
-Our more data-driven implementation results in the improved ability to predict stellar abundances.
+Our more data-driven implementation results in the improved ability of the $K=2$ model fit to predict all of a star's abundances.
 Notably, \name{} can better predict C+N and Mn abundances than the W22 two-process model, since all elements are used to constrain the fits.
@@
 However, \name{} is not without its own faults.
-The assumptions listed in Section~\ref{sec:model} may incorrectly skew our results and the model could benefit from improvements in implementation.
+The assumptions listed in Section~\ref{sec:model} may incorrectly skew our results, and the model could benefit from improvements in implementation.
 While assumptions (4) and (5) on Mg and Fe production are flexible, \name{} requires that both elements have fixed process vector components.
 If our assumptions are incorrect and, for instance, Mg is not a pure prompt element or (in the $K=4$ case) Fe has contributions from multiple delayed sources, our nucleosynthetic interpretation of \name{} may be incorrect.
-Additionally, assumption (7) states that the APOGEE data products can be used for this project, but that we inflate abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
-If the APOGEE errors are correct, this assumption could pull the model away from a solution that favors true outlier points.
-In future \name{} implementation, the development of a more robust method to justifiably down-weight outlier stars from the global fits would be beneficial.
+\add{This becomes more challenging as $K$ increases and we have to make more assumptions to break rotational symmetries.} Additionally, assumption (7) states that the APOGEE data products can be used for this project, but that we inflate outlying-star abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
+\add{It is also possible that $Q$ is accounting for some of the real intrinsic scatter in the data and inflating the observational error on true outlier stars.} In future \name{} implementation, the development of a more robust method to justifiably down-weight outlier stars from the global fits would be beneficial.
+\add{This method should account for both non-Gaussian observational errors (e.g., from bad telluric subtraction or unlucky line blends) and physically interesting outliers (e.g., from binary mass transfer).}
 Finally, \name{} fits process vector components along a spline with 11 knots (assumption 6), and those knots have fixed locations in metallicity.
@@
 The high-Ia and low-Ia populations have been labeled in both panels for clarity.
+\add{The symbols emphasize the stars at the edge of the populations but the reclassified stars make up only $\sim 2\%$ of the total population.}
     \label{fig:pop_divis}}
@@
 
-The success of the two-process model (W19, W22) and \name{} with $K=2$ suggests that the disk is largely two-dimensional (2D).
-In this paper, we have focused on a 2D nucleosynetheic model, with the two dimensions representing prompt CCSN-like enrichment and delayed SNIa-like enrichment.
-However, another 2D class of theoretical models for the Milky Way exist, describing stars in terms of birth radius and birth date \citep[e.g.,][]{frankel2018, ness2022}.
+The success of the two-process model (W19, W22) and \name{} with $K=2$ suggests that the \add{distribution of disk stars in APGOEE abundance space} is largely two-dimensional (2D), \add{though more dimensions are required to fully explain the data (\citealp{ting2022}, W22)}.
+In this paper, we have focused on a 2D nucleosynthetic model, with the two dimensions representing prompt CCSN-like enrichment and delayed SNIa-like enrichment.
+However, another 2D class of theoretical models for the Milky Way exists, describing stars in terms of birth radius and birth date \citep[e.g.,][]{frankel2018, ness2022}.
 Are these two 2D models related?
-If they are, then the nucleosynthetic parameters from \name{} ($\AIa$ and $\Acc$) should predict asteroseismic ages (or masses), up to unpredictable aspects of mass transfer, as well as the guiding radius, up to unpredictable aspects of radial migration.
-While a deeper study of the implications of the disk's two-dimensionality is outside the scope of this work, we show the relationship between age and process amplitudes in Figure~\ref{fig:age}.
+If they are, then the nucleosynthetic parameters from \name{} ($\AIa$ and $\Acc$) should predict asteroseismic ages (or masses), up to unpredictable aspects of mass transfer, as well as the guiding center radius, up to unpredictable aspects of radial migration.
+While a deeper study of the implications of the disk's two-dimensionality is outside the scope of this work, we show the relationship between \add{asteroseismic age from the APOKASC sample \citep{pinsonneault2018}} and process amplitudes in Figure~\ref{fig:age}.
 Here we see a clear gradient in age with $\Acc$ and $\AIa/\Acc$ (as in G22 and W22), though outlier stars are scattered throughout.
@@
     \includegraphics[width=.6\textwidth]{Paper/Figures/AIaAcc_age.pdf}
-    \caption{$\AIa/\Acc$ vs. $\Acc$ distribution for stars in the APOKASC sample. Each point is colored by the star's log(Age), with younger stars in black and older stars in yellow.
+    \caption{$\AIa/\Acc$ vs.
+$\Acc$ distribution for stars in the APOKASC sample \citep{pinsonneault2018} Each point is colored by the star's asteroseismic $\log$(age), with younger stars in black and older stars in yellow.
+\add{A clear gradient with $\log$(age) and process parameters exists with young outliers scattered throughout.
+This shows that the process amplitudes constitute a good-quality age indicator.}
     \label{fig:age}}
@@
 Because \name{} does not rely on [Mg/Fe] vs.
-[Fe/H] bimodality, non-bimodal population can now be fit with a multi-component nucleosynthetic model.
-\name{} could be applied to the low metallicity disk, halo, Gaia Enceladus Sausage, Nebula Majora, Nebula Minora\footnote{Historically referred to as the LMC and SMC.}, other Milky Way satellites, and more.
+[Fe/H] bimodality, non-bimodal populations can now be fit with a multi-component nucleosynthetic model.
+\name{} could be applied to the low metallicity disk, halo, Gaia Enceladus Sausage, Nubecula Major, Nubecula Minor\footnote{Historically referred to as the LMC and SMC.}, other Milky Way satellites, and more.
 \name{} can also be easily extended to $K>2$ in a much less restricted way than the two-process model.
@@
 This scatter could be signatures of enrichment from non-CCSN/SNIa sources, stochastic sampling of the IMF, environmental IMF variations, or metallicity-dependent SN yields with a bursty star formation history \citep[e.g.][]{belokurov2022, griffith2023}.
-While it is difficult to identify non-CCSN or SNIa enrichment in the APOGEE data alone, where only C+N and Ce are likely to have significant contributions from other sources, there may be signatures in other surveys with better coverage of heavier elements.
+While it is difficult to identify non-CCSN or SNIa enrichment in the APOGEE data alone, where only C+N and Ce are expected to have significant contributions from other sources, there may be signatures in other surveys with better coverage of heavier elements.
 Applying a $K>2$ model to GALAH \citep{buder2021}, or an overlapping sample of APOGEE and GALAH stars \citep{nandakumar2022}, could prove more successful.
@@
 It is a pleasure to thank
+  Polly Frazer (NYU),
   Melissa Ness (Columbia),
@@
 for valuable discussions and help.
+
 E.J.G. is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.

### 2023-07-10 Paper/main.tex

@@
 % -----------
-% - Look at all latex warnings on the build
 
@@
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-%\received{March 1, 2021}
-%\revised{April 1, 2021}
-%\accepted{\today}
+% \received{July 10, 2023}
+% \revised{}
+% \accepted{}
 
-%\submitjournal{ApJ}
+\submitjournal{ApJ}
 
@@
 
-\title{\name: A flexible and data-driven $K$-process model for nucleosynthesis}
+\title{\name: A flexible and data-driven K-process model for nucleosynthesis}
 
@@
 \affiliation{Max-Planck-Institut f{\"u}r Astronomie, K{\"o}nigstuhl 17, D-69117 Heidelberg, Germany}
-\affiliation{Flatiron Institute, 162 Fifth Avenue, New~York,~NY 10010, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
 
-\author{Julianne Dalcanton}
-\author{Sten Hasselquist}
-\author{Bridget Ratcilffe}
-\author{Melissa Ness}
-\author{David Weinberg}
+\author{Julianne J. Dalcanton}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
+\affiliation{Department of Astronomy, Box 351580, University of Washington, Seattle, WA 98195}
 
-\begin{abstract}\noindent % trust
-\add{The origin of the surface abundance patterns of Milky Way stellar populations can be explained by two dominant processes,} one prompt and one delayed.
-\add{While two components can well describe the stellar abundance trends, elements are known to be produced by more than two sources.}
-We analyze the abundances of 14 elements relative to Mg for 48,659 stars from APOGEE DR17 with a flexible, data-driven $K$-process model---dubbed \name.
-In the fiducial model, where $K=2$, each elemental abundance of each star is described as the vector sum of a prompt and delayed process.
-%While prior work derives the relative importance of \add{the prompt and delayed processes in the production of various elements} from median observed abundance trends, we relax these assumptions and 
-%We simultaneously fit all model parameters to the data, with only minimal constraints to keep the processes interpretable.
-We find that our flexible method is able to recover the observed abundance bimodality and that this bimodality is visible to higher [Mg/H] in process amplitude space than in abundance space.
-We compare fit parameters and statistics from this new method to those from \citet{weinberg2022}, finding that the two methods produce similar results, but that \name{} better predicts stellar abundances, especially for C+N and Mn.
-%We test the validity of the standard two-process model assumptions, such as that in the sun Fe is generated by a roughly half-half combination of prompt and delayed sources.
-%We find that the assumptions of prior works are generally confirmed, but that the inferred fractional contributions from each process are strongly dependent upon Fe assumptions.
-\add{We explore the impact of our assumptions about the origin of Fe, needed to break the rotational symmetry of the model, constraining the parameter space that is able to reproduce the observed abundance distribution and finding that the inferred fractional contribution from each process are dependent upon our choice.}
-Finally, we add a third and fourth process, calibrated to Ce and Mn, respectively.
-The additional processes \add{give the model more freedom} and improve the model's ability to predict the stellar abundances, \add{as expected}, but demonstrates the model's ability to extend beyond $K=2$.
-\name{} enables future research to study the disk's abundance dimensionallity, investigate age-abundance label correlations, fit non-bimodal abundance distributions with a multi-component nucleosynthetic model, and much more.
-\ejg{Hogg: try to shorten the abstract. I made some changes but still need to cut like 25 more words.} 
+\author[0000-0001-5388-0994]{Sten Hasselquist}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+
+\author[0000-0003-1124-7378]{Bridget Ratcilffe}
+\affiliation{Leibniz-Institut f\"{u}r Astrophysik Potsdam (AIP), An der Sternwarte 16, 
+14482 Potsdam, Germany}
+
+\author[0000-0001-5082-6693]{Melissa Ness}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
+\affiliation{Department of Astronomy, Columbia University, Pupin Physics Laboratories, New York, NY 10027, USA}
+
+\author[0000-0001-7775-7261]{David H. Weinberg}
+\affiliation{The Department of Astronomy and Center of Cosmology and AstroParticle Physics, The Ohio State University, Columbus, OH 43210, USA}
+
+\begin{abstract}\noindent
+The element abundance pattern found by APOGEE and GALAH in Milky Way disk stars is close to two-dimensional, dominated by production from one prompt process and one delayed process.
+This simplicity is remarkable, since the elements are produced by a multitude of nucleosynthesis mechanisms operating in stars with a wide range of progenitor masses.
+We fit the abundances of 14 elements for 48,659 red-giant stars from APOGEE DR17 using a flexible, data-driven $K$-process model---dubbed \name.
+In our fiducial model, with $K=2$, each abundance in each star is described as the sum of a prompt and a delayed process contribution.
+We find that \name{} with $K=2$ is able to explain the abundances well, recover the observed abundance bimodality, and detect the bimodality over a greater range in metallicity than previously has been possible.
+We compare to prior work by \citet{weinberg2022}, finding that \name{} produces similar results, but that \name{} better predicts stellar abundances, especially for elements C+N and Mn and for stars at super-solar metallicities.
+The model makes assumptions, including especially that it fixes some parameters to break degeneracies and improve interpretability; we find that some of the nucleosynthetic implications are dependent upon these detailed parameter choices.
+We add a third and fourth process (to make $K=4$), finding that the additional processes give the model more freedom and improve the model's ability to predict the stellar abundances, as expected, but they don't qualitatively change the story.
+The results of \name{} have implications for the formation of the Galaxy disk, the relationship between abundances and ages, and the physics of nucleosynthesis.
 \end{abstract}
 
-\keywords{foo --- bar}
+\keywords{Nucleosynthesis (1131), Stellar abundances (1577), Galaxy chemical evolution (580), Core-collapse supernovae (304), Type Ia supernovae (1728), }
 
@@
 At the present day, stellar surface abundances are not very well explained by purely \textsl{ab initio}, physics-driven models.
-Theoretical yields vary from set to set, as they are dependent on progenitor properties and explosion assumptions \citep[e.g.,][]{rybizki2017, blancato2019, buck2021, griffith2021b}. 
+Theoretical yields vary from data set to data set, as they are dependent on progenitor properties and explosion assumptions \citep[e.g.,][]{rybizki2017, blancato2019, buck2021, griffith2021b}. 
 The wide parameter space of progenitor and supernova models coupled with uncertainties in reaction rates and explosion physics hinder the creation of an accurate nucleosynthetic model from theory alone.
@@
 Because the median abundance trends in [X/Mg] vs.
-[Mg/H] space are largely insensitive to aspects of chemical evolution, such as outflows and variations in star formation history \citep{weinberg2019}, the population abundance trends are set by the nucleosynthetic processes and can be used to empirically constrain Galactic enrichment.
+[Mg/H] space are largely insensitive to aspects of chemical evolution, such as outflows and variations in star formation history (W19), the population abundance trends are set by the nucleosynthetic processes and can be used to empirically constrain Galactic enrichment.
 
-These works, as well as \citet{ting2022} and \citet{ratcliffe2023}, find that the Milky Way stellar abundances are well fit by two components, \add{grounded in [Fe/H] and [Mg/Fe],} down to residuals of 0.01 to 0.02 dex.
+These works, as well as \citet{ting2022} and \citet{ratcliffe2023}, find that the Milky Way stellar abundances are well fit by two components, grounded in [Fe/H] and [Mg/Fe], down to residuals of 0.01 to 0.03 dex for the most precisely measured elements and 0.05 to 0.1 dex for elements (such as Na, C, and Ce) with large measurement errors.
 Simultaneously, \citet{frankel2018} and \citet{ness2022} have found that disk abundances are also well described by a two-component model of birth radius and age.
-Correlations between two-process model parameters and stellar ages and kinematics (W22) \add{as well as the success of a two-component model of [Fe/H] and age in predicting APOGEE abundances \citep{ness2019}} suggest that these two 2-dimensional models are somehow interconnected.
+Correlations between two-process model parameters and stellar ages and kinematics (W22) as well as the success of a two-component model of [Fe/H] and age in predicting APOGEE abundances \citep{ness2019} suggest that these two 2-dimensional models are somehow interconnected.
 
-Beyond standard CCSN and SNIa enrichment, many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep[e.g.,][]{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016} and merging neutron stars \citep[e.g.,][]{kilpatrick2017}, or atypical supernova explosions \citep[e.g.,][]{nomoto2013}.
+Beyond standard CCSN and SNIa enrichment, many elements have contributions from additional nucleosynthetic processes, such as the rapid ($r$) and slow ($s$) neutron capture processes \citep[e.g.,][]{arlandini1999, bisterzo2014} in asymptotic giant branch (AGB) stars \citep[e.g.,][]{simmerer2004, karakas2016}, merging neutron stars \citep[e.g.,][]{kilpatrick2017}, or atypical supernova explosions \citep[e.g.,][]{nomoto2013}.
 After predicting stellar abundances from $\feh$ and $\mgfe$, \citet{ting2022} identify correlated abundance residuals that are unexplained by observational uncertainties, indicative of additional nucleosynthetic processes that standard disk CCSN and SNIa enrichment cannot explain.
-Results from G22 and W22 support this conclusion, and both works attempt to add additional processes to their models to account for non-CCSN and non-SNIa enrichment, though in a very restrictive manner.
+Results from G22 and W22 support this conclusion, and both works attempt to add additional processes to their models to account for non-CCSN and non-SNIa enrichment, though in a restrictive manner.
 Other sources of abundance scatter, such as stochastic sampling of the Initial Mass Function (IMF), IMF variations, and bursty star formation history could also cause deviations away from a two-process model \citep{belokurov2018, griffith2023}.
@@
 The parameters output by our model can thus be used as de-noised abundance labels; these will sharpen relationships between abundances and stellar parameters (including birth location and time).
-\add{Our main contribution is to construct a data-driven model for nucleosynthesis that has good statistical properties, only enforcing constraints to break rotational degeneracies.
-All other \name{} parameters are set by the data with no fixed normalization.}
-% Had said some of this in the sentences before...
-%The process parameters are derived Uses a hierarchical statistical model so it combines abundances into K process amplitudes for each star and denoised predicted abundances of each star, and metallicity-dependent effective yields for the processes.
+Our main contribution is to construct a data-driven model for nucleosynthesis that has good statistical properties, only enforcing constraints to break rotational degeneracies.
+All other \name{} parameters are set by the data with no fixed normalization.
 
@@
 As in W22 and G22, we propose that all stellar abundances can be generated by a combination of $K$ nucleosynthetic processes.
-In this picture, each element has $K$ metallicity-dependent process vector components that are shared across the full stellar sample, while each star individually has $K$ process amplitudes, \add{which apply across all elements, such that the expected logarithmic abundance of element $j$ in star $i$ ($m_{ij}$) is defined as:}
+In this picture, each element has $K$ metallicity-dependent process vector components that are shared across the full stellar sample, while each star individually has $K$ process amplitudes, which apply across all elements, such that the expected logarithmic abundance of element $j$ relative to H in star $i$ ($m_{ij}$) is defined as:
 \begin{equation}\label{eq:mij_k}
@@
 Each star $i$ has $K$ process amplitudes ($A^k_i$)
-and each element $j$ has $K$ \add{metallicity dependent} process vector components ($q_{k,j}^{Z}$). 
-\add{The $Z$ superscript denotes the dependence of the process vectors on metallicity, $Z$, taken to be [Mg/H].}
-The $m_{ij}$ value is the model expected logarithmic abundance of element $j$ \add{relative to Hydrogen in star $i$, such that the observed abundance can be expressed}
+and each element $j$ has $K$ metallicity dependent process vector components ($q_{k,j}^{Z}$). 
+The $Z$ superscript denotes the dependence of the process vectors on metallicity, $Z$, taken to be [Mg/H].
+The observed abundance can be expressed
 \begin{equation}\label{eq:xh}
@@
 \end{equation}
-\add{where ``noise'' represents observational noise and/or other sources of intrinsic abundance scatter that are not included in this model.}
-
-\add{For example, in the $K=2$ case for a star ($i=40$) with a O abundance of $[\text{O}/\text{H}] =0.155$ and $\mgh = 0.122$, \name{} fits $q_{\text{CC,O}}^{\mgh=0.12} = 0.91$ and $q_{\text{Ia,O}}^{\mgh=0.12} = 0.13$.
-This indicates that at $\mgh = 0.12$, stellar O is dominantly produced by the prompt (CCSN) process.
-For this star, \name{} also derives $A_{40}^{\rm CC} = 1.3$ and $A_{40}^{\rm Ia} = 1.2$ from the abundances of all 15 elements.
-Summing the products of the corresponding process vector component and process amplitude, we find $m_{40,\text{O}} = \log_{10} ( 1.36 ) = 0.135$.
-\name{} predicts the star's O abundance to 0.02 dex, the typical scale of observational noise on [O/H] in APOGEE.
-For more detailed examples from a similar model, see Section 2 of W22.}
-\ejg{Hogg let me know what you think.
-We don't introduce the CC and Ia notation until later in this section so I think if it stays it needs more clarification.
-I lean towards just sending people to Section 2 and Figures 2 and 3 of W22.
-}
+where ``noise'' represents observational noise and/or other sources of intrinsic abundance scatter that are not included in this model.
+For detailed examples of a similar model with $K=2$, see Section 2 and Figures 2 and 3 of W22.
 
@@
 All elements on the periodic table are produced by a combination of nucleosynthetic processes such as CCSN, SNIa, AGB stars, and merging neutron stars \citep{johnsonja2020}.
-The majority of $\alpha$, light odd-Z, and Fe-peak elements (the elements observed by APOGEE) are dominantly produced by $K=2$ sources, with one being a prompt process or mix of prompt processes, and one being a delayed process or a mix of delayed processes.
+The majority of $\alpha$, light odd-$Z$, and Fe-peak elements (the elements observed by APOGEE) are dominantly produced by $K=2$ sources, with one being a prompt process or mix of prompt processes, and one being a delayed process or a mix of delayed processes.
 This is substantiated by theoretical yields \citep[e.g.,][]{anderson2019, rybizki2017} and past successful data-driven models (e.g., \citealp{ness2019}, G22, W22, \citealp{ting2022, ratcliffe2023}).
@@
 \paragraph{2. Linearity}
-At every metallicity, the (linear) $(X/H)$ abundances of a star can be expressed as a linear combination of $K$ processes.
+At every metallicity, the (linear) (X/H) abundances of a star can be expressed as a linear combination of $K$ processes.
 These processes themselves will depend on metallicity, but a linear sum is sufficient to explain all element abundances at any overall metallicity.
@@
 \end{equation}
-at all metallicities.
+at all metallicities. Equation~\ref{eq:qcc_mg_solar} also imposes that the Mg process is metallicity independent.
 
@@
 at all metallicities. 
-This assumption places a star with purely prompt enrichment on the low-metallicity $\mgfe$ plateau near 0.4 dex, in agreement with APOGEE observations but in contention with recent results from \citet{conroy2022} which place the $\mgfe$ plateau near 0.6 dex.
+This assumption places a star with purely prompt enrichment on the low metallicity $\mgfe$ plateau near 0.4 dex, in agreement with APOGEE observations but in contention with recent results from \citet{conroy2022} which place the $\mgfe$ plateau near 0.6 dex.
 We explore the impact of different $\qccFe$ assumptions in Section~\ref{subsec:qccFe}.
@@
 We describe the potential data systematics in Section~\ref{sec:data}.
-\add{For our purposes, we care merely about the statistical observational errors rather than systematics that arise from imperfect modeling of the spectra such as NLTE effects, though differential systematics across the sample can artificially add abundance scatter.
+For our purposes, we care mainly about the statistical observational errors rather than systematics that arise from imperfect modeling of the spectra such as NLTE effects, though differential systematics across the sample can artificially add abundance scatter.
 The actual derived values of $q_{k,j}^{Z}$ will be affected by systematic offsets in the abundances.
-We add a softening parameter $Q$ (Equation~\ref{eq:inflate_ivar}) to allow for the possibility that APOGEE observational errors are underestimated or that there is intrinsic scatter around the \name{} predictions.}
-% The APOGEE errors may be slightly underestimated for some element measurements, so we add a softening parameter $Q$ to inflate the uncertainties on abundance-outlier stars (see Equations~\ref{eq:chi2} and ~\ref{eq:inflate_ivar}).
+We add a softening parameter $Q$ (Equation~\ref{eq:inflate_ivar}) to allow for the possibility that APOGEE observational errors are underestimated or that there is intrinsic scatter around the \name{} predictions.
 
 \paragraph{8. Robust likelihood function}
-The observed value of [X/H] can be described as the $K$ process expected value plus observational noise and/or other sources of intrinsic abundance scatter, \add{as described by Equation~\ref{eq:xh}.}
+The observed value of [X/H] can be described as the $K$ process expected value plus observational noise and/or other sources of intrinsic abundance scatter, as described by Equation~\ref{eq:xh}.
 The expression in this equation can be thought of as the key assumption underlying our likelihood function.
@@
 where $Q$ is a softening parameter.
-\add{Our results are largely insensitive to the choice of $Q$ (e.g., $1 < Q < 10$), so we choose to set $Q=5$.
-Very small values (e.g., $Q=.1$) will erase some of the abundance structure and produce poorer fits.}
+Our results are largely insensitive to the choice of $Q$ (e.g., $1 < Q < 10$), so we choose to set $Q=5$.
+Very small values (e.g., $Q=.1$) will erase some of the abundance structure and produce poorer fits.
 
@@
 With the above assumptions in place, the likelihood function can be optimized to a set of stellar abundances.
-The model is initialized at the Mg and Fe process vector components from Equations~\ref{eq:qcc_mg_solar} --~\ref{eq:qcc_fe_z}.
+The model is initialized at the Mg and Fe process vector components from Equations~\ref{eq:qcc_mg_solar} and~\ref{eq:qcc_fe_solar}.
 It subsequently optimizes the process amplitudes (dubbed the $A$-step) using only Mg and Fe at fixed process vector components, and then optimizes the process vector components (dubbed the $q$-step) for all elements at fixed process amplitudes.
-The $A$-step and $q$-step are alternated, repeating 48 rounds of optimization, \add{in the $K=2$ case,} and updating the best-fit parameters when the objective function improves.
+The $A$-step and $q$-step are alternated, repeating 48 rounds of optimization, in the $K=2$ case, and updating the best-fit parameters when the objective function improves.
 We find few differences in the best-fit parameters when we decrease the number of iterations to 32, indicating that the model quickly finds a good solution.
@@
 APOGEE DR17 reports stellar parameters, including $\teff$ and $\logg$, as well as 20 elemental abundances: C, \ion{C}{1}, N, O, Na, Mg, Al, Si, S, K, Ca, \ion{Ti}{1}, \ion{Ti}{2}, V, Cr, Mn, Fe, Co, Ni, and Ce for 657,135 stars.
-Among these elements and ions, some are measured more precisely than others.
+In DR17, new spectral libraries \citep{hubeny2021} are generated using the Synspec code and incorporate NLTE corrections for Na, Mg, K, and Ca \citep{osorio2020}.
+Among the reported elements and ions, some are measured more precisely than others.
 We exclude Ti from our analysis as there are large differences between the abundances derived from the \ion{Ti}{1} and \ion{Ti}{2} lines \citep{jonsson2020}.
@@
 Both P and V display strong abundance artifacts and large scatter.
-Among the remaining elements, we note the following concerns: weak Na spectral features, large abundance scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, potentially strong unaccounted-for NLTE effects on Mn abundances \citep{bergemann2019}, and large abundance scatter in Co and Ce---both derived from one line.
-Further, we note that DR17 is the first time Ce abundances have been included in APOGEE data products.
-\ejg{Comments that this is not correct and more Ce lines are used, but the DR17 paper isn't out yet.
-Sten to help.} For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
+Among the remaining elements, we note the following concerns: weak Na spectral features, large abundance scatter in S, significant systematic artifacts in Cr abundances at super-solar metallicities, potentially strong unaccounted-for NLTE effects on Mn abundances \citep{bergemann2019}, and large abundance scatter in Co and Ce.
+For a more detailed discussion of abundance systematics and their effects on population trends, see \citet{jonsson2020} and \citet{griffith2021a}.
 
@@
 
-These cuts result in a sample of 48,659 stars \add{that span the Galactic disk.
+These cuts result in a sample of 48,659 stars that span the Galactic disk.
 We plot their $Z$ vs.
-$R$ distribution, as well as the distributions of distances and eccentricities in Figure~\ref{fig:star_dist}, taking distances and kinematics from \citep{queiroz2023}.
+$R$ location, as well as the distributions of distances and eccentricities in Figure~\ref{fig:star_dist}, taking distances and kinematics from \citep{queiroz2023}.
 While our stellar sample extends from Galactic center, to the outer disk, to the halo, the majority of our stars ($75\%$) are within 3.5 kpc of the sun.
@@
 In this paper, we assume that the KPM fits will be consistent across the Galactic disk, as the median high-Ia and low-Ia [X/Mg] vs.
-[Mg/H] abundance tends are insensitive to Galactic location (W19, \citealp{griffith2021a}.}
+[Mg/H] abundance tends are insensitive to Galactic location (W19, \citealp{griffith2021a}).
 \begin{figure*}[htb!]
@@
     \includegraphics[width=\textwidth]{Paper/Figures/star_sample.pdf}
-    \caption{\add{Left: distribution of our stellar sample in $Z$ (kpc) vs.
-$R$ (kpc).
-Center: distribution of distances (kpc).
-Right: distribution of eccentricity.
-Our stellar sample spans the Galactic disk, but the majority of our stars are within 3.5 kpc of the sun.}}
+    \caption{Left: distribution of our stellar sample in $Z$ (kpc) vs.
+$R$ (kpc) where (0,0) is the Galactic center.
+Center: distribution of stellar distances (kpc).
+Right: distribution of stellar eccentricity.
+Our stellar sample spans the Galactic disk, but the majority of our stars are within 3.5 kpc of the sun and have kinematics consistent with \textit{in situ} origin.}
     \label{fig:star_dist}
@@
 In the analysis of each element, X, we drop stars with \texttt{X\_FE\_FLAG}.
-Ce has the most problematic abundances, with $\sim 700$ flagged stars.
+Ce abundances are flagged in the most stars, resulting in $\sim 700$ Ce labels being excluded.
 While the surface abundances of C and N differ from the stellar birth abundances for RGB stars due to the CNO processes and dredge-up events \citep{iben1965, shetrone2019}, the total C+N abundance remains constant.
@@
 \begin{equation}
-    [\text{C+N}/\text{H}] = \log_{10}(10^{\text{[C/H]}+8.39} + 10^{\text{[N/H]}+7.78}) - \log_{10}(10^{8.39} + 10^{7.78})
+    [\text{C+N}/\text{H}] = \log_{10}(10^{\text{[C/H]}+8.39} + 10^{\text{[N/H]}+7.78}) - \log_{10}(10^{8.39} + 10^{7.78}),
 \end{equation}
@@
 Second column: The predicted [X/Mg] vs.
-[Mg/H] abundance distribution of the fiducial plus estimated noise.
-\add{By comparing the first two columns we can evaluate the success of \name{} in reproducing the observed abundance distributions.} Third column: process vector components $\qcc$ (thin, purple) and $\qIa$ (thick, orange) from this work (G23, solid, dark lines) and W22 (light, dashed lines).
-\add{Overall offsets between the solid and dashed lines are driven largely by our normalization that places the [Mg/Fe] plateau at $+0.4$, rather than $+0.3$ in W22.} Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial model.
-We plot the median $\fcc$ values of the low-Ia (orange square) and high-Ia (purple circle) populations in the solar metallicity bin from W22 for comparison.}
+[Mg/H] abundance distribution of the fiducial model plus estimated noise.
+By comparing the first two columns we can evaluate the success of \name{} in reproducing the observed abundance distributions.
+Third column: process vector components $\qcc$ (thin, purple) and $\qIa$ (thick, orange) from this work (G23, solid, dark lines) and W22 (light, dashed lines).
+Overall offsets between the solid and dashed lines are driven largely by our normalization that places the [Mg/Fe] plateau at $+0.4$, rather than $+0.3$ in W22.
+Fourth column: distribution of fractional contribution from the prompt process ($\fcc$) predicted by the fiducial model.
+We plot the median $\fcc$ values of the low-Ia (orange square) and high-Ia (purple circle) populations in the solar metallicity bin from W22 for comparison.
+All density plots are logarithmically scaled.}
     \label{fig:all_param1}
@@
 This fit produces process vector components $\qcc$ and $\qIa$ as a function of $\mgh$ for each element and process amplitudes $\Acc$ and $\AIa$ for each star.
-From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted $K=2$ process abundances, \add{shown in the second column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}}.
+From the model parameters, we can calculate fractional contributions from each process as well as a full suite of predicted $K=2$ process abundances, shown in the second column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
 
@@
 
-We plot the process vector components as a function of $\mgh$ in the third column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}.
+We plot the process vector components as a function of $\mgh$ in the third column of Figures~\ref{fig:all_param1} and~\ref{fig:all_param2} and provide the values at the [Mg/H] knots in Tables~\ref{tab:qcc} and~\ref{tab:qIa}.
 The process vector components inform us about the relative contribution of prompt and delayed processes to the formation of the elements, as well as the metallicity dependence of the enrichment.
 By definition, $\qccFe=0.4$ at all metallicities.
-For \add{Mg and} Fe, we also require $\qcc + \qIa = 1$, implying $\qIaFe=0.6$.
+For Mg and Fe, we also require $\qcc + \qIa = 1$, implying $\qIaFe=0.6$.
 No such constraints are placed on other elements.
-\add{We note that \name{} differs from the previous two-process models in this regard, as G22 and W22 require that the process vectors for all elements sum to 1 at solar metallicity.}
+We note that \name{} differs from the previous two-process models in this regard, as G22 and W22 require that the process vector components for all elements sum to 1 at solar metallicity.
+
+\begin{deluxetable}{cccccccccccccccc}
+    \tablecaption{Fiducial model $\qcc$ values at [Mg/H] knot values for each element.
+    \label{tab:qcc}}
+    \tablehead{
+\colhead{[Mg/H]} &	\colhead{C+N} &	\colhead{O} &	\colhead{Na} &	\colhead{Mg} &	\colhead{Al} &	\colhead{Si} &	\colhead{S} &	\colhead{K} &	\colhead{Ca} &	\colhead{Cr} &	\colhead{Mn} &	\colhead{Fe} &	\colhead{Co} &	\colhead{Ni} &	\colhead{Ce}}
+    \startdata
+-0.8 &	0.34 &	1.06 &	0.26 &	1.0 &	0.62 &	0.90 &	0.98 &	0.78 &	0.77 &	0.33 &	0.19 &	0.4 &	0.37 &	0.44 &	0.40 \\
+-0.5 &	0.44 &	1.04 &	0.36 &	1.0 &	0.77 &	0.82 &	1.02 &	0.88 &	0.70 &	0.34 &	0.22 &	0.4 &	0.48 &	0.48 &	0.27 \\ 
+-0.4 &	0.48 &	1.03 &	0.33 &	1.0 &	0.80 &	0.79 &	0.98 &	0.88 &	0.67 &	0.35 &	0.24 &	0.4 &	0.52 &	0.50 &	0.21 \\
+-0.3 &	0.52 &	1.01 &	0.37 &	1.0 &	0.84 &	0.77 &	0.96 &	0.92 &	0.65 &	0.35 &	0.25 &	0.4 &	0.58 &	0.51 &	0.18 \\
+-0.2 &	0.55 &	0.98 &	0.42 &	1.0 &	0.86 &	0.75 &	0.93 &	0.93 &	0.64 &	0.38 &	0.27 &	0.4 &	0.62 &	0.53 &	0.17 \\
+-0.1 &	0.58 &	0.97 &	0.45 &	1.0 &	0.85 &	0.74 &	0.90 &	0.96 &	0.61 &	0.39 &	0.29 &	0.4 &	0.66 &	0.53 &	0.18 \\
+0.0 &	0.62 &	0.95 &	0.46 &	1.0 &	0.84 &	0.72 &	0.87 &	0.99 &	0.60 &	0.39 &	0.29 &	0.4 &	0.67 &	0.52 &	0.22 \\
+0.1 &	0.64 &	0.93 &	0.43 &	1.0 &	0.85 &	0.71 &	0.80 &	0.98 &	0.60 &	0.40 &	0.24 &	0.4 &	0.62 &	0.49 &	0.26 \\
+0.2 &	0.57 &	0.85 &	0.26 &	1.0 &	0.85 &	0.66 &	0.68 &	0.92 &	0.63 &	0.49 &	0.09 &	0.4 &	0.49 &	0.45 &	0.37 \\
+0.3 &	0.61 &	0.78 &	0.18 &	1.0 &	0.78 &	0.63 &	0.62 &	0.76 &	0.66 &	0.64 &	0.01 &	0.4 &	0.48 &	0.44 &	0.47 \\
+0.6 &	0.66 &	0.65 &	0.61 &	1.0 &	0.66 &	0.58 &	0.49 &	0.64 &	0.70 &	0.64 &	0.28 &	0.4 &	0.70 &	0.50 &  0.36 \\ 	
+\enddata
+\end{deluxetable}
+
+\begin{deluxetable}{cccccccccccccccc}
+    \tablecaption{Fiducial model $\qIa$ values at [Mg/H] knot values for each element.
+    \label{tab:qIa}}
+    \tablehead{
+\colhead{[Mg/H]} &	\colhead{C+N} &	\colhead{O} &	\colhead{Na} &	\colhead{Mg} &	\colhead{Al} &	\colhead{Si} &	\colhead{S} &	\colhead{K} &	\colhead{Ca} &	\colhead{Cr} &	\colhead{Mn} &	\colhead{Fe} &	\colhead{Co} &	\colhead{Ni} &	\colhead{Ce}}
+    \startdata
+-0.8 &	0.54 &	0.15 &	0.28 &	0.0 &	0.02 &	0.08 &	0.37 &	0.17 &	0.21 &	0.38 &	0.55 &	0.6 &	0.47 &	0.49 &	0.28 \\
+-0.5 &	0.62 &	0.01 &	0.67 &	0.0 &	0.16 &	0.13 &	0.27 &	0.11 &	0.18 &	0.61 &	0.83 &	0.6 &	0.74 &	0.63 &	0.60 \\
+-0.4 &	0.54 &	0.01 &	0.70 &	0.0 &	0.11 &	0.15 &	0.18 &	0.10 &	0.24 &	0.63 &	0.81 &	0.6 &	0.67 &	0.56 &	0.78 \\
+-0.3 &	0.46 &	0.04 &	0.66 &	0.0 &	0.11 &	0.19 &	0.15 &	0.09 &	0.29 &	0.64 &	0.79 &	0.6 &	0.58 &	0.51 &	0.93 \\
+-0.2 &	0.42 &	0.08 &	0.54 &	0.0 &	0.10 &	0.23 &	0.15 &	0.07 &	0.33 &	0.60 &	0.75 &	0.6 &	0.48 &	0.46 &	0.98 \\
+-0.1 &	0.39 &	0.09 &	0.50 &	0.0 &	0.13 &	0.25 &	0.15 &	0.04 &	0.36 &	0.58 &	0.74 &	0.6 &	0.43 &	0.45 &	0.88 \\
+0.0 &	0.40 &	0.10 &	0.51 &	0.0 &	0.12 &	0.26 &	0.14 &	0.00 &	0.35 &	0.60 &	0.79 &	0.6 &	0.45 &	0.49 &	0.67 \\
+0.1 &	0.45 &	0.12 &	0.68 &	0.0 &	0.08 &	0.27 &	0.19 &	0.03 &	0.32 &	0.63 &	0.95 &	0.6 &	0.59 &	0.57 &	0.49 \\
+0.2 &	0.61 &	0.21 &	1.05 &	0.0 &	0.06 &	0.31 &	0.31 &	0.15 &	0.25 &	0.53 &	1.26 &	0.6 &	0.83 &	0.65 &	0.28 \\
+0.3 &	0.63 &	0.29 &	1.32 &	0.0 &	0.15 &	0.35 &	0.35 &	0.40 &	0.19 &	0.42 &	1.46 &	0.6 &	0.96 &	0.70 &	0.09 \\
+0.6 &	0.62 &	0.37 &	1.13 &	0.0 &	0.30 &	0.34 &	0.36 &	0.48 &	0.13 &	0.43 &	1.40 &	0.6 &	0.83 &	0.64 &	0.16\\
+\enddata
+\end{deluxetable}
 
@@
 O, a Mg-like element theoretically purely produced in prompt CCSN, shows $\fccX{O}$ near 1 from $\mgh=-0.75$ to solar.
-At supersolar $\mgh$, the delayed process contributes to O production, driving the $\fccX{O}$ value down to $\sim 0.8$ at $\mgh=0.4$.
+At supersolar metallicity, the delayed process contributes to O production, driving the $\fccX{O}$ value down to $\sim 0.8$ at $\mgh=0.4$.
 S behaves like O, with almost entirely prompt production up to solar metallicity, after which delayed enrichment contributes more significantly.
@@
 By construction, $\qccFe=0.4$ and $\qIaFe=0.6$ at all metallicities.
-This produces a bimodal distribution in $\fcc$ similar to that observed in abundance space.
+This produces a bimodal distribution in $\fccX{Fe}$ similar to that observed in abundance space.
 Because of our choice of $\qccFe$, only a few stars have $\fccX{Fe}=1$ (see Section~\ref{subsec:qccFe}).
@@
 
-In addition to process vector components, each star is fit with a prompt and delayed process amplitude, $\Acc$ and $\AIa$ respectively.
-All elemental abundances are used in the calculation of these amplitudes, so they can be interpreted as ``de-noised'' abundance labels \add{that suppress observational scatter by averaging over elements via the data-driven model}.
+In addition to process vector components, each star is fit with a prompt and delayed process amplitude, $\Acc$ and $\AIa$ respectively (Table~\ref{tab:As}).
+All elemental abundances are used in the calculation of these amplitudes, so they can be interpreted as ``de-noised'' abundance labels that suppress observational scatter by averaging over elements via the data-driven model.
 The value of $\Acc$ traces the metallicity (specifically $\mgh$) while the ratio of $\AIa/\Acc$ traces the $\femg$ abundance.
@@
 The stars with larger $\AIa/\Acc$ values correspond to the high-Ia population, and those with low $\AIa/\Acc$ correspond to the low-Ia population.
-While in the Tinsley-Wallerstein diagram the two populations blend together at high-metallicity, they are more distinguishable in amplitude space.
+While in the Tinsley-Wallerstein diagram the two populations blend together at high metallicity, they are more distinguishable in our amplitude space.
 We plot $\AIa/\Acc$ vs.
@@
 The high-Ia and low-Ia populations are clearly separable through $\mgh$ of 0.4.
-\add{This is further shown through the $\AIa/\Acc$ distributions in the right panel of Figure~\ref{fig:As} for [Mg/H] bins of $-0.75$ to $-0.425$, $-0.425$ to $-0.1$, $-0.1$ to 0.225, and 0.225 to 0.55.
-The three lowest metallicity bins display a bimodal distribution and the highest metallicity bin is dominated by high-Ia stars.}
+This is further shown through the $\AIa/\Acc$ distributions in the right panel of Figure~\ref{fig:As} for [Mg/H] bins of $-0.75$ to $-0.425$, $-0.425$ to $-0.1$, $-0.1$ to 0.225, and 0.225 to 0.55.
+The three lowest metallicity bins display a bimodal distribution and the highest metallicity bin is dominated by high-Ia stars.
+
+\begin{deluxetable}{cccc}
+    \tablecaption{Fiducial model $\Acc$ and $\AIa$ values for our stellar sample.
+    \label{tab:qIa}}
+    \tablehead{
+\colhead{APOGEE ID} &	\colhead{[Mg/H]} & \colhead{$\Acc$} &	\colhead{$\AIa$}} 
+\startdata
+2M00000546+6152107 &	-0.20 &	0.61 &	0.48\\
+2M00000866+7122144 &	-0.10 &	0.82 &	0.69\\
+2M00001328+5725563 &	0.04 &	1.09 &	1.02\\
+2M00001653+5540107 &	0.06 &	1.13 &	0.36\\
+2M00001717+6147500 &	-0.23 &	0.60 &	0.39\\
+... & ... & ... & ...\\
+\enddata
+\tablecomments{Full table available online.}
+\end{deluxetable}
 
@@
 $\Acc$ for the fiducial model.
-\add{This plot is similar to a [Fe/Mg] vs.
+This plot is similar to a [Fe/Mg] vs.
 [Mg/H] distribution where $\AIa/\Acc$ is a proxy for [Fe/Mg] and $\Acc$ is a proxy for [Mg/H].
-Note that $\Acc = 1$ corresponds to $\mgh = 0$}.
+Note that $\Acc = 1$ corresponds to $\mgh = 0$.
 Center: distribution of $\AIa/\Acc$ vs.
@@
 In the left and center panels, we can clearly see the bimodality to high values of $\Acc$ and $\mgh$.
-\add{Right: distribution of $\AIa/\Acc$ for ranges of [Mg/H] with metallicity bin increasing from top to bottom.
-[Mg/H] bins are of width 0.325 dex and span $-0.75$ to 0.55.}}
+Both density plots are logarithmically scaled.
+Right: distribution of $\AIa/\Acc$ for ranges of [Mg/H] with metallicity bin increasing from top to bottom.
+[Mg/H] bins are of width 0.325 dex and span $-0.75$ to 0.55.}
     \label{fig:As}
@@
 The predicted abundances plus estimated noise are not, however, able to reproduce the observed abundance scatter.
-This is especially noticeable at low-metallicity for C+N, Na, Al, K, Co, and Ce.
-For these elements the scatter in the observed abundance distribution is much larger than in the predicted distribution, suggesting that either APOGEE observational scatter is underestimated or that the $K=2$ model is insufficient--\add{a likely case for elements produced by AGB stars, such as C+N and Ce }.
+This is especially noticeable for O, C+N, Na, Al, K, Co, and Ce.
+For these elements the scatter in the observed abundance distribution is larger than in the predicted distribution, suggesting that the APOGEE observational scatter is underestimated, that there are $\teff$ or $\logg$ dependent abundance trends (e.g., \citealp{griffith2021a}, W22), or that the $K=2$ model is insufficient--a likely case for elements produced by AGB stars, such as C+N and Ce.
 
@@
 
-As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, \name{} is based upon the two-process model developed in W19 and W22, but with increased flexibility, \add{minimal normalization}, and no forced dependence upon the [Fe/Mg] vs.
+As discussed in Sections~\ref{sec:intro} and~\ref{sec:model}, \name{} is based upon the two-process model developed in W19 and W22, but with increased flexibility, minimal normalization, and no forced dependence upon the [Fe/Mg] vs.
 [Fe/H] bimodality or population abundance trends.
@@
 Because \name{} uses all elements in its optimization, Mg, Ca, and Fe are effectively de-weighted relative to the W22 model, while C+N and Mn influence the model parameters.
-\add{If we re-fit \name{} using only the Mg, O, Si, Ca, Fe, and Ni abundances in the $A$-step (as in W22), we find that \name{} and the two-process model predict the abundances of all elements but Mn with similar accuracy, and that the two-process model better predicts Mn.
+If we re-fit \name{} using only the Mg, O, Si, Ca, Fe, and Ni abundances in the $A$-step (as in W22), we find that \name{} and the two-process model predict the abundances of all elements but Mn with similar accuracy, and that the two-process model better predicts Mn.
 Our fiducial model's success in predicting C+N and Mn is likely attributable to the inclusion of the elements in the $A$-step.
 The choice to include all elements or a subset of elements in the fits should be considered when implementing \name{}.
-If searching for stars with anomalous abundances of element X relative to the expected abundances of other elements, one may want to exclude X from the $A$-step.}
+If searching for stars with anomalous abundances of element X relative to the expected abundances of others, one may want to exclude X from the $A$-step.
 
@@
     \includegraphics[width=\textwidth]{Paper/Figures/comp_w22.pdf}
-    \caption{Left: cumulative distribution of $\log \chi^2$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line).
+    \caption{Left: cumulative distribution of $\log_{10}(\chi^2)$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line).
 Right: $\chi^2$ per element for the same model fits with elements ordered by atomic number.
-\add{Overall, our model has a smaller cumulative $\chi^2$ than the previous two-process model and better predicts the abundances of C+N, Na, K, Mn, Co, Ni, and Ce.}}
+Overall, our model has a smaller cumulative $\chi^2$ than the previous two-process model and better predicts the abundances of C+N, Na, K, Mn, Co, Ni, and Ce.}
     \label{fig:comp_w22}
@@
 
-\subsection{\add{Impact of Fe Process Assumptions}} \label{subsec:qccFe}
+\subsection{Impact of Fe Process Assumptions} \label{subsec:qccFe}
 
 While \name{} is flexible, we still include some quantitative assumptions, which we make to break exact model degeneracies (see Section~\ref{sec:model}).
-Specifically, for each process, we choose one element to assign a ``known'' process vector element at all metallicities.
+Specifically, for each process, we choose one element to assign a ``known'' process vector component at all metallicities.
 These are Mg and Fe in the $K=2$ case.
@@
 Unfortunately, there is no comparable pure SNIa element, nor is there an element for which we know the relative CCSN/SNIa ratio.
-In order to break an exact degeneracy between the prompt and delayed processes, we choose to fix the Fe process vector components, \add{which effectively makes assumptions about the exact fractional contribution of CCSN and SNIa (or prompt and delayed processes) to Fe enrichment.}
+In order to break an exact degeneracy between the prompt and delayed processes, we choose to fix the Fe process vector components, which effectively makes assumptions about the exact fractional contribution of CCSN and SNIa (or prompt and delayed processes) to Fe enrichment.
 
@@
 Because our model is non-negative, the choice of $\qccFe$ sets the minimum [Fe/Mg] value attainable by our model ($\log_{10}(\qccFe)$).
-In this section, we explore the implications of different $\qccFe$ assumptions, varying the zero point and metallicity dependence ($\dqccFe$).
+In this Section, we explore the implications of different $\qccFe$ assumptions, varying the zero point and metallicity dependence ($\dqccFe$).
 In Figure~\ref{fig:qccFe_FeMg}, we plot the minimum [Fe/Mg] as a function of $\mgh$ for the $\qccFe$ and $\dqccFe$ parameters we explore.
@@
     \caption{Minimum [Fe/Mg] value attainable for $\qccFe$ and $\dqccFe$ assumptions.
-Left: For $\dqccFe=0$ with $\qccFe=0.5$, 0.45, 0.4, and 0.35 (light to dark purple).
-Right: For $\dqccFe=0.15$ with $\qccFe=0.5$, 0.4, 0.35 (light to dark orange).}
+Left: for $\dqccFe=0$ with $\qccFe=0.5$, 0.45, 0.4, and 0.35 (light to dark purple).
+Right: for $\dqccFe=0.15$ with $\qccFe=0.5$, 0.4, 0.35 (light to dark orange).}
     \label{fig:qccFe_FeMg}
@@
 We repeat the optimization of the \name{} with $K=2$ and these $\qccFe$ assumptions.
-In Figure~\ref{fig:qccFe_FeMgpred}, we plot the resulting predicted abundance distributions plus estimated noise \add{alongside the observed distribution}.
+In Figure~\ref{fig:qccFe_FeMgpred}, we plot the resulting predicted abundance distributions plus estimated noise alongside the observed distribution.
 We do not plot the prediction for the fiducial model ($\qccFe=0.4$, $\dqccFe=0.0$), as this is shown in Figure~\ref{fig:all_param2}.
@@
     \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMgpred.pdf}
-    \caption{\add{Top: observed [Fe/Mg] vs.
-[Mg/H] abundance distribution.} Bottom: predicted [Fe/Mg] vs.
+    \caption{Top: observed [Fe/Mg] vs.
+[Mg/H] abundance distribution.
+Bottom: predicted [Fe/Mg] vs.
 [Mg/H] abundance distributions plus estimated noise for models with $\dqccFe=0.0$ (middle row) and $\dqccFe=0.15$ (bottom row).
 The $\qccFe$ value increase from left to right from 0.35 to 0.5.
-\add{Note that the center panels have different $\qccFe$ values (middle: 0.45, bottom: 0.4) and that the predicted abundance distribution for $\qccFe=0.4$ and $\dqccFe=0.0$ can be found in Figure~\ref{fig:all_param2}}.
+All density plots are logarithmically scaled.
+Note that the center panels have different $\qccFe$ values (middle: 0.45, bottom: 0.4) and that the predicted abundance distribution for $\qccFe=0.4$ and $\dqccFe=0.0$ can be found in Figure~\ref{fig:all_param2}.
 The $\qccFe$ and $\dqccFe$ parameters are listed in each panel.
-\add{By comparing the lower panels to the observed distribution (top) we can evaluate the success or failure of each model; the low-Ia population is most sensitive to the Fe assumptions.} \ejg{Looks brown???}}
+By comparing the lower panels to the observed distribution (top) we can evaluate the success or failure of each model; the low-Ia population is most sensitive to the Fe assumptions.}
     \label{fig:qccFe_FeMgpred}
@@
 Of the seven models explored here, the case with $\qccFe=0.4$ and $\dqccFe=0.15$ has the lowest average $\chi^2$ per star, indicating that the Fe abundances are best fit by a metallicity dependent prompt process.
-\add{Introducing this metallicity dependence subtly changes the shape of the predicted low-Ia distribution in a way that achieves better agreement with APOGEE observations.}
+Introducing this metallicity dependence subtly changes the shape of the predicted low-Ia distribution in a way that achieves better agreement with APOGEE observations.
 
@@
 We only show the median $\fcc$ values for the models with $\dqccFe=0.0$ as the solar metallicity median $\fcc$ values for the metallicity dependent models are almost identical for matching values of $\qccFe$.
-We find that the choice of $\qccFe$ has little impact on the median $\fcc$ values of elements dominated by CCSN enrichment (e.g.
-O, S, Al, K).
+We find that the choice of $\qccFe$ has little impact on the median $\fcc$ values of elements dominated by CCSN enrichment (e.g., O, Al, S, K).
 As the delayed contribution increases, the median elemental $\fcc$ values decrease more significantly with decreasing $\qccFe$.
@@
     \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for \name{} with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.
-\add{Elements are ordered by atomic number.
-The median $\fcc$ changes most dramatically for elements with strong delayed contributions.}}
+Elements are ordered by atomic number.
+The median $\fcc$ changes most dramatically for elements with strong delayed contributions.}
     \label{fig:qccFe_fcc}
@@
 Potential sources of such scatter include metallicity-dependent SN yields with a bursty star formation history, environmental variations in the IMF, stochastic sampling of the IMF, and more than two distinct processes (e.g., AGB stars, merging neutron stars, and unique classes of SNIa) with different time delays for enrichment \citep[e.g.][]{belokurov2022, griffith2023}.
-\add{Note that the existence of many enrichment channels is not in itself sufficient for producing scatter around a $K=2$ model (or even a $K=1$ model); one needs star-to-star variation in the relative amplitude of these channels.
-For example, in a fully mixed one-zone model, all abundances depend only on time, even if many enrichment channels contribute.}
+Note that the existence of many enrichment channels is not in itself sufficient for producing scatter around a $K=2$ model (or even a $K=1$ model); one needs star-to-star variation in the relative amplitude of these channels.
+For example, in a fully mixed one-zone model, all abundances depend only on time, even if many enrichment channels contribute.
 
 In this Section, we will explore the impact of adding additional processes to our model, increasing from $K=2$ to $K=4$.
-Our goal is to demonstrate the potential of using \name{} to capture more of the observed abundance diversity.
 Because \name{} is sensitive to enrichment with different time delays, adding components could be interpreted as adding sources with distinct enrichment time scales.
 For example, if AGB stars and SNIa enrich with the \textit{same} time delay, the model would fit both sources in one delayed component.
-If AGB and SNIa enrich with \textit{different} delay times, a third component should pick up delayed AGB enrichment not captured by the original delayed process.
+If AGB and SNIa enrich with \textit{different} delay times, a third component could pick up delayed AGB enrichment not captured by the original delayed process.
 Indeed, evidence of a distinct AGB-like process is identified in G22 and W22, where correlated residuals are used to expand the two-process model.
@@
 
-We take a more flexible approach, allowing the model to identify the elements best-fit with additional components and modify the $K=2$ process parameters.
-Ultimately, such a method could be used to identify elements with more than two enrichment channels, \add{but our data set may not be capable of doing so robustly}.
-Our model now includes four components, such that
+Our goal is to demonstrate the potential for using \name{} to flexibly model more than two enrichment channels and improve the accuracy of the abundance predictions.
+We allow the model to identify the elements best-fit with additional components and modify the $K=2$ process parameters.
+Ultimately, such a method could be used to identify elements with more than two enrichment channels, but our data set may not be capable of doing so robustly.
+In the $K=4$ case, our model becomes
 \begin{equation}\label{eq:mij_4}
@@
 We choose Ce and Mn, two elements with larger residuals that likely have additional nucleosynthetic sources---Ce from AGB stars and Mn from distinct classes of SNIa \citep[e.g.][]{gallino1998, reyes2020, gronow2021}.
-\ejg{why do we choose these and what happens if we choose others?} We initialize the $K=4$ model at the $K=2$ model values of $\qcc$, $\qIa$, $\Acc$, and $\AIa$ with the added constraints that
+To test the impact of our choice of representative elements we also fit the $K=4$ model with the third and fourth processes fixed to C+N and Cr.
+We find that similar groups of elements are better fit with additional components.
+We initialize the $K=4$ model at the $K=2$ model values of $\qcc$, $\qIa$, $\Acc$, and $\AIa$ with the added constraints that
 \begin{equation}\label{eq:q3_z}
@@
 The model converges upon a set of process vector components and amplitudes that can be combined with Equation~\ref{eq:mij_4} to predict the stellar abundances and calculate the fractional contribution from each process.
-The model parameters themselves are less directly interpretable, as we set the third and fourth process vector components for Ce and Mn to an arbitrary value with no metallicity dependence, so we do not show them here.
-\ejg{Weinberg says this is a cop-out and we should add something about the vectors...} We calculate $\fcc$, $f_{{\rm Ia}, ij}$, $f_{3, ij}$, and $f_{4, ij}$ for each abundance of each star where
-\begin{equation}\label{eq:fX}
-    f_{k, ij} = \frac{A_{i}^{k} \, q_{k,j}^Z}{\Acc\,\qcc + \AIa\,\qIa + A_{i}^{3}\,q_{3, j}^{Z} + A_{i}^{4}\,q_{4, j}^{Z}}.
-\end{equation}
-We find that the third process, regularized to Ce, contributes at a low level to O, Si, S, Al, and K and more significantly to Ca, Na, Cr, and Ce.
-The fourth process, regularized to Mn, contributes at a low level to K and more significantly to S, C+N, Na, Cr, Ni, Mn, and Co.
-These best-fit element groupings resemble but are not identical to the elements selected for additional components in W22, where the third process included Ca, Na, Al, K, Cr, and Ce and the fourth process included Ni, V, Mn, and Co.
+In Figure~\ref{fig:A4}, we plot $A^k_i/\Acc$ vs.
+$\Acc$ for the SNIa, third, and fourth processes.
+We find that processes 3 and 4 are most prominent in stars at low metallicity and that there is a large population of stars with $A^3_i$ and/or $A^4_i \approx 0$.
+In Figure~\ref{fig:all_paramK} we plot the observed and predicted abundance distributions as well as the process vector components and fractional contribution from each component for a subset of elements.
+We note that the model parameters $q_{3,j}^{Z}$ and $q_{4,j}^{Z}$ should be interpreted in conjunction with the amplitudes, as we set the third and fourth process vector components for Ce and Mn to an arbitrary value with no metallicity dependence.
 
-In the fourth column of Figure~\ref{fig:all_paramK}, we plot the median $f_{K, ij}$ as a function of $\mgh$ of the low-Ia population (Equation~\ref{eq:lowIa}) for a subset of elements with significant contributions from the third and/or fourth processes.
-We include median $\fcc$ and $f_{{\rm Ia},ij}$ from the $K=2$ model for comparison.
-We see that the third process contributes significantly to Ca, Na, Cr, and Ce at low metallicity, with decreasing contribution up to $\mgh\approx0.1$.
-The fractional contribution from the $K=2$ prompt and delayed processes to these elements decreases under the $K=4$ model, with median $\fcc$ decreasing more substantially than $f_{{\rm Ia}, ij}$.
-The fourth process behaves in a similar manner but with elements C+N, Na, Cr, Ni, Mn, and Co.
-We find that the addition of a fourth process decreases $\fcc$ and $f_{\rm Ia}$ values by roughly equal amounts at low metallicities.
-The fractional contribution from the third and fourth process is nearly identical in the high-Ia population, though the median $\fcc$ and $f_{{\rm Ia}, ij}$ values vary more significantly (as seen in Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}).
-
-Adding model components increases the abundance diversity that \name{} can achieve.
-\ejg{Clarify what abundance diversity means and how significant the improvement is.
-Rewrite so that we don't invalidate that two processes are sufficient to describe abundance features.} In the left-most columns of Figure~\ref{fig:all_paramK}, we plot the $\xmg$ v.s.
-$\mgh$ distributions for the observed stellar sample, the $K=2$ model predictions, and the $K=4$ model predictions for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
-We note that the predicted abundances do \textit{not} have noise added (unlike Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}) \add{to highlight the differences between the $K=2$ and $K=4$ predictions}.
-Comparing the predicted abundances from the $K=2$ and $K=4$ process models, we see that the $K=4$ process model is better able to capture the observed abundance distribution than the $K=2$ model.
-Specifically, it better captures the scatter in the low metallicity end of the low-Ia population.
-\ejg{Notes from Weinberg: Not adding the noise helps in comparing the K=2 and K=4.
-However, I don't think you can conclude from this figure that the K=4 model fits the data better because you have to add errors to make the comparison.
-I think a good diagnostic would be P(X/Mg) at a couple of specified (Mg/H) values for the data and the K=2,4 models with APOGEE errors added.}
+\begin{figure*}[htb!]
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/A4s.pdf}
+    \caption{$A^k_i/\Acc$ vs.
+$\Acc$ distribution for $\AIa$ (left), $A^3_i$ (center), and $A^4_i$ (right).
+All density plots are logarithmically scaled.
+The third and fourth processes contribute most to low metallicity stars.}
+    \label{fig:A4}
+\end{figure*}
 
@@
 [Mg/H] abundance distributions for the observed sample (first column), $K=2$ model (second column) and $K=4$ model (third column) for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
-\add{Observational errors are \textit{not} added to the model predictions.} Right: median fractional contribution from each process for the $K=4$ (solid lines) and $K=2$ (dashed lines) models to the low-Ia population as a function of $\mgh$.
-We plot the median $\fcc$ in light purple, $f_{{\rm Ia}, ij}$ in dark purple, $f_{3, ij}$ in light orange, and $f_{4, ij}$ in dark orange as well as a dotted grey line at 0 for reference.}
+Observational errors are \textit{not} added to the model predictions.
+All density plots are logarithmically scaled.
+Right: process vector components (fourth column) and median low-Ia fractional contribution from each process (fifth column) for the $K=4$ (solid lines) and $K=2$ (dashed lines) models to the low-Ia population as a function of $\mgh$.
+We plot the median $\qcc$ and $\fcc$ in light purple, $\qIa$ and $f^{\rm Ia}_{ij}$ in dark purple, $q^Z_{3,i}$ and $f^{3}_{ij}$ in light orange, and $q^Z_{4,i}$ and $f^{4}_{ij}$ in dark orange.
+In the final column we plot a dotted grey line at 0 for reference.}
     \label{fig:all_paramK}
@@
 
-The improved ability of the $K=4$ model to capture the abundance diversity of our stellar sample is also clear in the fit statistics.
-In Figure~\ref{fig:comp_Ks}, we plot the cumulative $\log(\chi^2)$ distributions for the fits to each star and the total $\chi^2$ for each element for the fiducial $K=2$ model and the $K=4$ model.
-We see that the cumulative $\log(\chi^2)$ distribution decreases with the increase in model components.
+We find that the third process, regularized to Ce, contributes at a low level to O, Si, S, Al, and K and more significantly to Ca, Na, Cr, and Ce.
+The fourth process, regularized to Mn, contributes at a low level to K and more significantly to S, C+N, Na, Cr, Ni, Mn, and Co.
+These best-fit element groupings resemble, but are not identical to, the elements selected for additional components in W22, where the third process included Ca, Na, Al, K, Cr, and Ce and the fourth process included Ni, V, Mn, and Co.
+
+In the left-most columns of Figure~\ref{fig:all_paramK}, we plot the $\xmg$ v.s.
+$\mgh$ distributions for the observed stellar sample, the $K=2$ model predictions, and the $K=4$ model predictions for Ca, C+N, Na, Cr, Ni, Mn, Co, and Ce.
+We note that the predicted abundances do \textit{not} have noise added (unlike Figures~\ref{fig:all_param1} and~\ref{fig:all_param2}) to highlight the differences between the $K=2$ and $K=4$ predictions.
+Comparing the predicted abundances from the $K=2$ and $K=4$ process models, we see that the $K=4$ process model is better able to capture the abundance scatter than the $K=2$ model, especially at the low metallicity end of the low-Ia population.
+This result is expected, as adding more model components will increase the abundance space that \name{} is able to reproduce.
+
+In the fourth and fifth columns of Figure~\ref{fig:all_paramK}, we plot the process vector components and median $f^{k}_{ij}$ as a function of $\mgh$ of the low-Ia population (Equation~\ref{eq:lowIa}), respectively, where
+\begin{equation}\label{eq:fX}
+    f^{k}_{ij} = \frac{A_{i}^{k} \, q_{k,j}^Z}{\Acc\,\qcc + \AIa\,\qIa + A_{i}^{3}\,q_{3, j}^{Z} + A_{i}^{4}\,q_{4, j}^{Z}}.
+\end{equation}
+We include $\qcc$ and $\qIa$ as well as median $\fcc$ and $f^{\rm Ia}_{ij}$ from the $K=2$ model in respective columns for comparison.
+We see that the third process contributes significantly to Ca, Na, Cr, and Ce at low metallicity, with decreasing contribution up to $\mgh\approx0.1$.
+The fractional contribution from the $K=2$ prompt and delayed processes to these elements decreases under the $K=4$ model.
+The fourth process behaves in a similar manner but with elements C+N, Na, Cr, Ni, Mn, and Co.
+The fractional contribution from the third and fourth process is nearly identical in the high-Ia population.
+
+=The statistical improvement in the \name{} between the $K=2$ and $K=4$ models is evident in the $\chi^2$ values.
+In Figure~\ref{fig:comp_Ks}, we plot the cumulative $\log_{10}(\chi^2)$ distributions for the fits to each star and the total $\chi^2$ for each element for the fiducial $K=2$ model and the $K=4$ model.
+We find that the cumulative $\log_{10}(\chi^2)$ distribution decreases with the increase in model components by greater than two for most stars, expected for the addition of two degrees of freedom. 
 We also find that the $\chi^2$ per element is lower for all elements in the $K=4$ model. 
-Significant improvements to Ca, C+N, Mn, and Ce are likely due to the additional third and fourth components capturing abundance patterns that the original prompt and delayed processes could not.
+Significant improvements to Ca, C+N, Mn, and Ce are likely due to the additional third and fourth components capturing abundance scatter that the original two processes could not. 
 Notably, we also see a significant improvement in the Fe fit, even though we require $q_{\rm 3,Fe}^{Z} = q_{\rm 4,Fe}^{Z} = 0$.
@@
 With the additional components able to account for the non-Fe-like enrichment, the original two processes are better able to capture the Fe enrichment.
-\ejg{Weinberg comment: Better $\chi^2$ is guaranteed right because more freedom of fit?
-maybe you want to plot the distribution of $\chi^2_2 - \chi^2_4$ and show that it typically improves by more than 2.}
 
@@
     \includegraphics[width=\textwidth]{Paper/Figures/comp_Ks.pdf}
-    \caption{Left: cumulative distribution of $\log \chi^2$ for the $K=2$ model (solid dark purple line) and our the $K=4$ model (dotted light purple line).
+    \caption{Left: cumulative distribution of $\log_{10} (\chi^2)$ for the $K=2$ model (dotted light purple line) and the $K=4$ model (solid dark purple line).
 Right: $\chi^2$ per element for the same model fits.
@@
 Through this investigation, we find that \name{} is extendable to $K>2$ processes.
-Adding components improves the model's ability to capture the observed abundance diversity.
-We will not interpret these results in terms of nucleosynthesis here, but provide a discussion of the future science that \name{} and the $K=4$ model enable below.
+The additional processes improve the model quantitatively, but additional work is needed to improve the nucleosynthetic interpretability.
+We provide a discussion of the future science that \name{} and the $K=4$ model enable below.
 
@@
 In the $K=2$ model, the first process, fixed to Mg, represents prompt CCSN-like enrichment, and the second process, fixed to Fe, represents delayed SNIa-like enrichment---but other nucleosynthetic sources with similar time delays may be mixed into each.
-\add{Under our adopted assumptions, the prompt process also contributes to Fe, but the delayed process does not contribute to Mg, in accordance with theoretical expectations for CCSN and SNIa.} Overall, we find that $K=2$ is a good fit to the data and that the model successfully recovers the global abundance patterns in the Milky Way.
+Under our adopted assumptions, the prompt process also contributes to Fe, but the delayed process does not contribute to Mg, in accordance with theoretical expectations for CCSN and SNIa.
+Overall, we find that $K=2$ is a good fit to the data and that the model successfully recovers the global abundance patterns in the Milky Way.
 While \name{} does not rely on $\femg$ vs.
 $\mgh$ bimodality or median abundance trends, it is able to recover the observed bimodal abundance distribution.
-Further, the fit parameters $\Acc$ and $\AIa$ act as ``denoised'' abundance labels, revealing a clearer signature of bimodality at high-metallicity in $\AIa/\Acc$ vs.
+Further, the fit parameters $\Acc$ and $\AIa$ act as combined individual-process abundance labels, revealing a clearer signature of bimodality at high metallicity in $\AIa/\Acc$ vs.
 $\mgh$ space than in $\femg$ vs.
 $\mgh$.
-This suggests that the \name{} fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are condensing information from 15 elements into two variables.
-\ejg{Hogg, BR asks if As are truly denoised or if they are just in a different dimensional space (vs.
-mij which are denoised abundances).}
+This suggests that the \name{} fit parameters and predicted abundances could be used as a higher signal-to-noise tracer of nucleosynthesis, as they are using a justified likelihood to condense information from 15 elements into two variables.
 
@@
 We find that high values of $\qccFe$ (0.5 and 0.45) are not able to reproduce the observed [Fe/Mg] vs [Mg/H] abundance distribution, regardless of the process vector component's metallicity dependence.
-\add{Our requirement that $\Acc$ and $\AIa$ are non-negative makes it impossible for the model to reproduce the lowest $\femg$ values in the APOGEE data.} Values $\qccFe = 0.4$ and 0.35 with $\dqccFe = 0$ or 0.15 produces similarly successful fits.
+Our requirement that $\Acc$ and $\AIa$ are non-negative makes it impossible for the model to reproduce the lowest $\femg$ values in the APOGEE data.
+Values $\qccFe = 0.4$ and 0.35 with $\dqccFe = 0$ or 0.15 produces similarly successful fits.
 While predicted abundance distributions appear similar for these models, the implied fractional contribution from the prompt process is dependent upon the Fe assumption for elements with substantial delayed enrichment.
@@
 We find that S, Ca, C+N, Na, Cr, Mn, Co, Ni, and Ce are best fit with a third and/or fourth component, with such processes contributing most significantly at low metallicity.
-\add{The information for constraining the $q^{Z}_{k,j}$ values for the third (fourth) process come from the star-by-star deviations of Ce (Mn) from the $K=2$ model predictions and their correlation with deviations for other elements $X_i$.
-Relative to the approach taken in W22 (Section 8), our $K=4$ model requires non-negative $q^Z_{k,j}$ and $A_i^k$ for all elements and stars, and it starts by tying the third and fourth processes to individual elements rather than groups of elements.}
+The information for constraining the $q^{Z}_{k,j}$ values for the third (fourth) process come from the star-by-star deviations of Ce (Mn) from the $K=2$ model predictions and their correlation with deviations for other elements $\text{X}_i$.
+Relative to the approach taken in W22 (Section 8), our $K=4$ model requires non-negative $q^Z_{k,j}$ and $A_i^k$ for all elements and stars, and it starts by tying the third and fourth processes to individual elements rather than groups of elements.
 The $K=4$ model improves the ability of \name{} to fit the abundances of all elements but especially improves predictions of Ca, C+N, Fe, Mn, and Ce.
@@
 While assumptions (4) and (5) on Mg and Fe production are flexible, \name{} requires that both elements have fixed process vector components.
-If our assumptions are incorrect and, for instance, Mg is not a pure prompt element or (in the $K=4$ case) Fe has contributions from multiple delayed sources, our nucleosynthetic interpretation of \name{} may be incorrect.
-\add{This becomes more challenging as $K$ increases and we have to make more assumptions to break rotational symmetries.} Additionally, assumption (7) states that the APOGEE data products can be used for this project, but that we inflate outlying-star abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
-\add{It is also possible that $Q$ is accounting for some of the real intrinsic scatter in the data and inflating the observational error on true outlier stars.} In future \name{} implementation, the development of a more robust method to justifiably down-weight outlier stars from the global fits would be beneficial.
-\add{This method should account for both non-Gaussian observational errors (e.g., from bad telluric subtraction or unlucky line blends) and physically interesting outliers (e.g., from binary mass transfer).}
+If our assumptions are incorrect and, for instance, Mg is not a pure prompt element or (in the $K=4$ case) Fe has contributions from multiple delayed sources, our nucleosynthetic interpretation of \name{} may be wrong.
+This becomes more challenging as $K$ increases and we have to make more assumptions to break rotational symmetries.
+Additionally, assumption (7) states that the APOGEE data products can be used for this project, but we inflate outlying-star abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
+It is also possible that $Q$ is accounting for some of the real intrinsic scatter in the data and inflating the observational error on true outlier stars.
+In future \name{} implementation, the development of a more robust method to justifiably down-weight outlier stars from the global fits would be beneficial.
+This method should account for both non-Gaussian observational errors (e.g., from bad telluric subtraction or unlucky line blends) and physically interesting outliers (e.g., from binary mass transfer).
 Finally, \name{} fits process vector components along a spline with 11 knots (assumption 6), and those knots have fixed locations in metallicity.
@@
 Beyond improvements to the underlying model assumptions and implementation, \name{} needs to include parameter uncertainty.
-While the model delivers process vector components and amplitudes, which can be used to calculate $f_{K, ij}$ and $K$ process predicted abundances, the current implementation does not return errors on any variable.
+While the model delivers process vector components and amplitudes, which can be used to calculate $f^{k}_{ij}$ and $K$ process predicted abundances, the current implementation does not return errors on any variable.
 The best method to derive such errors has not been explored, but one could use the likelihood function or bootstrapping.
@@
 The best-fit values of $\Acc$ and $\AIa$, in particular, are powerful tracers of nucleosynthesis.
-They show a bimodality at all metallicities, as do the de-noised abundances. \hogg{EJG: Is this true? I just wrote it.}
-And---because the model is a maximum-likelihood model---they represent information-theory optimal combined measures of alpha  and iron abundances.
-That is, these data-driven amplitudes could replace more theory-driven measures of the relative contributions of core-collapse and Ia enrichment channels.
+They show a bimodality at all metallicities, as do some of the de-noised abundances.
+And---because the model is a maximum-likelihood model---they represent information-theory optimal combined measures of $\alpha$ and Fe-peak abundances.
+That is, these data-driven amplitudes could replace more theory-driven measures of the relative contributions of CCSN and SNIa enrichment channels.
 
@@
 Beyond improving the definition of high-Ia and low-Ia populations, the \name{} parameters and predicted abundances could be used in any current analysis that strives to show trends with abundance labels.
-We predict that trends of stellar parameters with [X/H] will be clearer when comparing to $[\text{X}/\text{H}]_{\rm pred}$, $\Acc$, or $\AIa$.
+We predict that trends of stellar parameters with [X/H] will be clearer when comparing to $m_{ij}$, $\Acc$, or $\AIa$.
 
@@
 The high-Ia and low-Ia populations have been labeled in both panels for clarity.
-\add{The symbols emphasize the stars at the edge of the populations but the reclassified stars make up only $\sim 2\%$ of the total population.}
-    \label{fig:pop_divis}}
+The symbols emphasize the stars at the edge of the populations but the re-classified stars make up only $\sim 2\%$ of the total population.}
+    \label{fig:pop_divis}
 \end{figure*}
@@
 However, in this paper we only present fits for a small population with restricted stellar parameters, relative to the full APOGEE sample.
-\ejg{Add some discussion about the data products that are available for the sample in this paper and the availability of our code....} While \name{} could be fit to the full APOGEE sample, systematic abundance effects with $\teff$ and $\logg$, as well as other abundance artifacts \citep[e.g.,][]{jonsson2020, griffith2021a}, cause the abundance trends to differ across the Hertzsprung-Russell diagram.
+\ejg{Add references to tables with q values at knots and A values for all stars.} While \name{} could be fit to the full APOGEE sample, systematic abundance effects with $\teff$ and $\logg$, as well as other abundance artifacts \citep[e.g.,][]{jonsson2020, griffith2021a}, cause the abundance trends to differ across the Hertzsprung-Russell diagram.
 The best-fit \name{} parameters for the giants would differ from those for the dwarfs.
@@
 
-The success of the two-process model (W19, W22) and \name{} with $K=2$ suggests that the \add{distribution of disk stars in APGOEE abundance space} is largely two-dimensional (2D), \add{though more dimensions are required to fully explain the data (\citealp{ting2022}, W22)}.
+The success of the two-process model (W19, W22) and \name{} with $K=2$ suggests that the distribution of disk stars in APGOEE abundance space is largely two-dimensional (2D), though more dimensions are required to fully explain the data (\citealp{ting2022}, W22).
 In this paper, we have focused on a 2D nucleosynthetic model, with the two dimensions representing prompt CCSN-like enrichment and delayed SNIa-like enrichment.
@@
 If they are, then the nucleosynthetic parameters from \name{} ($\AIa$ and $\Acc$) should predict asteroseismic ages (or masses), up to unpredictable aspects of mass transfer, as well as the guiding center radius, up to unpredictable aspects of radial migration.
-While a deeper study of the implications of the disk's two-dimensionality is outside the scope of this work, we show the relationship between \add{asteroseismic age from the APOKASC sample \citep{pinsonneault2018}} and process amplitudes in Figure~\ref{fig:age}.
+While a deeper study of the implications of the disk's two-dimensionality is outside the scope of this work, we show the relationship between asteroseismic age from the APOKASC sample \citep{pinsonneault2018} and process amplitudes in Figure~\ref{fig:age}.
 Here we see a clear gradient in age with $\Acc$ and $\AIa/\Acc$ (as in G22 and W22), though outlier stars are scattered throughout.
@@
     \caption{$\AIa/\Acc$ vs.
-$\Acc$ distribution for stars in the APOKASC sample \citep{pinsonneault2018} Each point is colored by the star's asteroseismic $\log$(age), with younger stars in black and older stars in yellow.
-\add{A clear gradient with $\log$(age) and process parameters exists with young outliers scattered throughout.
+$\Acc$ distribution for stars in the APOKASC sample \citep{pinsonneault2018} Each point is colored by the star's asteroseismic $\log_{10}$(age), with younger stars in black and older stars in yellow.
+A clear gradient with $\log_{10}$(age) and process parameters exists with young outliers scattered throughout.
 This shows that the process amplitudes constitute a good-quality age indicator.}
-    \label{fig:age}}
+    \label{fig:age}
 \end{figure*}
@@
 
-\ejg{Some concluding statement about the tons of future science that \name{} can do and how readers can access it.}
+In the $K=2$ and $K>2$ cases, results from \name{} will help us disentangle our Galactic formation and enrichment history.
+This data-driven model opens doors to many new research projects and exciting future scientific results.
+To use \name{} yourself, please reference the KPM GitHub repository\footnote{\url{https://github.com/13emilygriffith/KProcessModel}} or contact the corresponding author.
 
@@
   Polly Frazer (NYU),
-  Melissa Ness (Columbia),
   Adrian Price-Whelan (Flatiron),
@@
   Soledad Villar (JHU),
-  David Weinberg (OSU),
+  the Darling research group at CU Boulder,
   CU Boulder Research Computing services and staff,
@@
 E.J.G. is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135.
+B.R. acknowledges support by the Deutsche Forschungsgemeinschaft under the 
+grant MI 2009/2-1.
 

### 2023-10-16 Paper/main.tex

@@
 
-\documentclass[modern]{aastex631}
+\documentclass[modern, linenumbers]{aastex631}
 \usepackage{amsmath}
@@
 \usepackage{soul}
+% \usepackage{lineno}
+% \linenumbers
 
@@
 \begin{abstract}\noindent
-The element abundance pattern found by APOGEE and GALAH in Milky Way disk stars is close to two-dimensional, dominated by production from one prompt process and one delayed process.
-This simplicity is remarkable, since the elements are produced by a multitude of nucleosynthesis mechanisms operating in stars with a wide range of progenitor masses.
+The element abundance pattern found by APOGEE in Milky Way disk stars is close to two-dimensional, dominated by production from one prompt process and one delayed process.
+This is remarkable, since the elements are known to be produced by many more than two nucleosynthetic sources.
 We fit the abundances of 14 elements for 48,659 red-giant stars from APOGEE DR17 using a flexible, data-driven $K$-process model---dubbed \name.
@@
     \tablecaption{Fiducial model $\Acc$ and $\AIa$ values for our stellar sample.
-    \label{tab:qIa}}
+    \label{tab:As}}
     \tablehead{
@@
 However, in this paper we only present fits for a small population with restricted stellar parameters, relative to the full APOGEE sample.
-\ejg{Add references to tables with q values at knots and A values for all stars.} While \name{} could be fit to the full APOGEE sample, systematic abundance effects with $\teff$ and $\logg$, as well as other abundance artifacts \citep[e.g.,][]{jonsson2020, griffith2021a}, cause the abundance trends to differ across the Hertzsprung-Russell diagram.
+While \name{} could be fit to the full APOGEE sample, systematic abundance effects with $\teff$ and $\logg$, as well as other abundance artifacts \citep[e.g.,][]{jonsson2020, griffith2021a}, cause the abundance trends to differ across the Hertzsprung-Russell diagram.
 The best-fit \name{} parameters for the giants would differ from those for the dwarfs.

### 2023-10-16 API/kpm/general.py
implement fourier sum model; breaking everything

@@ -7,11 +7,9 @@ import numpy as np
 
 def get_lnqs(fixed, fit):
     """
-    linear interpolation on vmap?
+    see `internal_get_lnqs` for actual information.
     """
-    return jnp.concatenate([vmap(jnp.interp, in_axes=(None, None, 1),
-                                 out_axes=(1))(fixed.xs, fixed.knot_xs[k], fit.lnqs[k])[None, :, :]
-                            for k in range(fixed.K)], axis=0)
+    return internal_get_lnqs(fit.lnq_pars, fixed.xlim[1] - fixed.xlim[0], fixed.xs)
 
 ## Not needed 
 # def get_processes(K):
@@ -21,11 +19,11 @@ def get_lnqs(fixed, fit):
 
 def all_stars_KPM(fixed, fit):
     """
-    ## inputs
+    ## inputs -- actually these are things in `fixed` and `fit`
     - `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
-    - `lnqs`: shape `(K, Nknot, M)` natural-logarithmic processes
-    - `knot_xs`: shape `(Nknot, )` metallicity bin centers
-    - `xs`: shape `(N, )` abundance data (used to interpolate the `lnqs`)
+    - `lnq_pars`: shape `(K, 2*J+1, M)` amplitudes
+    - `xlim`: shape `(2, )` metallicity range
+    - `xs`: shape `(N, )` abundance data (used to get the `lnqs`)
 
     ## outputs
     shape `(M, )` log_10 abundances
@@ -36,10 +34,18 @@ def all_stars_KPM(fixed, fit):
     return logsumexp(fit.lnAs[:, :, None]
                      + get_lnqs(fixed, fit), axis=0) / _LN10
 
-def internal_get_lnqs(K, lnqs, knot_xs, xs):
+def fourier_sum(amps, argument):
+    foo = amps[0]
+    for j in range(1, (len(amps) - 1) // 2 + 1):
+        foo += amps[2*j - 1] * jnp.cos(j * argument) \
+             + amps[2*j]     * jnp.sin(j * argument)
+    return foo
+
+fourier_sum_orama = vmap(vmap(fourier_sum, in_axes=(0, None), out_axes=1), in_axes=(0, None), out_axes=0)
+
+def internal_get_lnqs(lnq_pars, L, xs):
     """
-    linear interpolation on vmap?
+    sums of sines and cosines
     """
[…]

### 2023-10-17 API/kpm/data.py
updated qparm but bugs

@@ -201,21 +201,16 @@ class fixed_params:
 	q_CC_Fe: int
 		Value of q_CC for Ia_element at Z=0. 
 		Default is 0.4
-	dq_CC_Fe_dZ: int
-		Value of slope in q_CC for Ia_element with respect to Z. 
-		Default is 0.0
 	xs: numpy array shape(N)
 		Metallicity values for each item. Default is [Mg/H]
-	Nknot: int
-		Number of knots in the spine for the process vectors
-	knot_xs: numpy array shape(K, Nknot)
-		Array of knots for each process. Default is values at 'Nknot' linearly
-		spaced percintiles of 'xs'
+	J: int
+		Number of parameters in lnq_par model (only odd used)
+	xlim: numpy array shape(2)
+		min and max of xs
+		**** what we care about
 
 	Class Methods
 	-------------
-	update_knot_xs: function
-		User can suply their own array of knots
 		
 	
 	TO DO 
@@ -225,7 +220,7 @@ class fixed_params:
 	
 	def __init__(self, data, K=2, Lambda_a=1.e6, Lambda_c=1.e3,
 				 Lambda_d=1.e3, CC_elem='Mg', Ia_elem='Fe', 
-				 q_CC_Fe=0.4, dq_CC_Fe_dZ=0.0, Nknot=10):
+				 q_CC_Fe=0.4, J=9):
 		
 		if isinstance(K, int): pass
 		else:
@@ -274,16 +269,12 @@ class fixed_params:
 			raise ValueError("Atrribute 'q_CC_Fe' must lie between 0 and 1."
 				"Got %.2f" % (q_CC_Fe))
 			
-		if isinstance(dq_CC_Fe_dZ, float): pass
-		elif isinstance(dq_CC_Fe_dZ, int): dq_CC_Fe_dZ = float(dq_CC_Fe_dZ)
+		if isinstance(J, int): pass
 		else:
-			raise TypeError("Attribute 'dq_CC_Fe_dZ' must be a float. Got: %s" 
-				% (type(dq_CC_Fe_dZ)))
-
-		if isinstance(Nknot, int): pass
-		else:
-			raise TypeError("Attribute 'Nknot' must be an int. Got: %s" 
-				% (type(Nknot)))
+			raise TypeError("Attribute 'J' must be an int. Got: %s" 
+				% (type(J)))
+		if J%2==0: raise warnings.warn("The number of parameters in the q \
+			model must be odd. Got J= %f, using %f" % (J, J-1))
 		
 		
[…]

### 2023-10-17 API/kpm/general.py

@@ -9,7 +9,7 @@ def get_lnqs(fixed, fit):
     """
     see `internal_get_lnqs` for actual information.
     """
-    return internal_get_lnqs(fit.lnq_pars, fixed.xlim[1] - fixed.xlim[0], fixed.xs)
+    return internal_get_lnqs(fit.lnq_pars, fixed.L, fixed.xs)
 
 ## Not needed 
 # def get_processes(K):
@@ -41,7 +41,8 @@ def fourier_sum(amps, argument):
              + amps[2*j]     * jnp.sin(j * argument)
     return foo
 
-fourier_sum_orama = vmap(vmap(fourier_sum, in_axes=(0, None), out_axes=1), in_axes=(0, None), out_axes=0)
+fourier_sum_orama = vmap(vmap(fourier_sum, in_axes=(0, None), out_axes=1), \
+    in_axes=(0, None), out_axes=0)
 
 def internal_get_lnqs(lnq_pars, L, xs):
     """

### 2023-10-17 API/kpm/initialize.py

@@ -24,14 +24,14 @@ def initialize_2(data, fixed):
 	regs = regularizations(data, fixed)
 	fit = fit_params(data, fixed)
 
-	fit.lnqs = jnp.where(regs.Q.fixed_q, regs.Q.lnq0s, fit.lnqs)
+	fit.lnq_pars = jnp.where(regs.Q.fixed_q, regs.Q.lnq_par0s, fit.lnq_pars)
 
 	I = [el in [fixed.CC_elem, fixed.Ia_elem] for el in data.elements]
-	fit.lnAs, _ = A_step(data, fixed, fit.lnqs, fit.lnAs, I=I)
+	fit.lnAs, _ = A_step(data, fixed, fit.lnq_pars, fit.lnAs, I=I)
 	print("initialize_2():", np.median(fit.lnAs[1:] - fit.lnAs[0], axis=1))
 
-	fit.lnqs, _ = q_step(data, fixed, fit.lnqs, fit.lnAs)
-	fit.lnAs, _ = A_step(data, fixed, fit.lnqs, fit.lnAs)
+	fit.lnq_pars, _ = q_step(data, fixed, fit.lnq_pars, fit.lnAs)
+	fit.lnAs, _ = A_step(data, fixed, fit.lnq_pars, fit.lnAs)
 	print("initialize_2():", np.median(fit.lnAs[1:] - fit.lnAs[0], axis=1))
 
 	data.allivars = inflate_ivars(data, fixed, fit, Q=7)
@@ -56,8 +56,8 @@ def run_kpm(data, fixed, file_path, name='kpm_allstars', N_rounds=3, N_itters=16
     # Need to update so if early file is missing but later isn't it reruns whole thing
     data, fit = initialize_2(data, fixed)
 
-    pik_suffix = file_path+'/'+name+'_K'+str(fixed.K)+'_qccFe'+str(fixed.q_CC_Fe)+'_dq'+str(fixed.dq_CC_Fe_dZ)
-
+    pik_suffix = file_path+'/'+name+'_K'+str(fixed.K)+'_qccFe'+str(fixed.q_CC_Fe)
+    
     # run round of itterations
     for r in range(N_rounds):
         pik_name = pik_suffix + '_' + str(r) + '.out'

### 2023-10-17 API/kpm/one_star.py

@@ -4,7 +4,7 @@ from jax.scipy.special import logsumexp
 import jaxopt
 
 from ._globals import _LN10
-from .general import internal_get_lnqs as get_lnqs
+from .general import internal_get_lnqs
 
 def one_star_KPM(lnAs, lnqs):
     """
@@ -38,7 +38,7 @@ def one_star_chi(lnAs, lnqs, alldata, sqrt_ivars, sqrt_Lambda):
 def one_star_A_step(lnqs, alldata, sqrt_ivars, sqrt_Lambda, init):
     """
     ## inputs
-    - `lnqs`: shape `(K, M)` natural-logarithmic processes
+    - `lnqs`: shape `(K, M)` natural-logarithmic processes 
     - `alldata`: shape `(M, )` log_10 abundance measurements
     - `sqrt_ivars`: shape `(M, )` inverse errors on the data
     - `sqrt_Lambda`: shape `(K, )` regularization
@@ -73,39 +73,38 @@ def one_element_KPM(lnqs, lnAs):
     """
     return logsumexp(lnqs + lnAs, axis=0) / _LN10
 
-def one_element_chi(lnqs, lnAs, alldata, sqrt_ivars, knot_xs, xs, sqrt_Lambdas, q0s):
+def one_element_chi(lnq_pars, lnAs, alldata, sqrt_ivars, L, xs, sqrt_Lambdas, q0s):
     """
     ## inputs
-    - `lnqs`: shape `(K, Nknot)` natural-logarithmic process vectors
+    - `lnqs`: shape `(K, J)` natural-logarithmic process vectors
     - `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
     - `alldata`: shape `(N, )` log_10 abundance measurements
     - `sqrt_ivars`: shape `(N, )` inverse variances on the data
-    - `knot_xs`: shape `(Nknot, )` metallicity bin "centers"
+    - `L`: xrange
     - `xs` : shape `(N, )` metallicities to use with `metallicities`
     - `sqrt_Lambdas`: shape `(K, Nbin)` list of regularization amplitudes
-    - `q0s`: shape `(K, Nknot)` 
+    - `q0s`: shape `(K, J)` 
 
     ## outputs
     chi for this one star (weighted residual)
     """
-    K, Nknot = knot_xs.shape
-    interp_lnqs = get_lnqs(K, lnqs[:, :, None], knot_xs, xs)[:, :, 0]
[…]

### 2023-10-17 API/kpm/optimize.py

@@ -5,7 +5,7 @@ from jax import vmap
 from ._globals import _RNG, _LN_NOISE
 from .regularize import regularizations
 from .general import all_stars_KPM
-from .general import internal_get_lnqs as get_lnqs
+from .general import internal_get_lnqs
 from .one_star import one_star_A_step, one_element_q_step, one_element_chi, one_star_chi
 
 __all__ = ["inflate_ivars", "A_step", "q_step", "Aq_step", "run_kpm"]
@@ -14,13 +14,6 @@ __all__ = ["inflate_ivars", "A_step", "q_step", "Aq_step", "run_kpm"]
 def inflate_ivars(data, fixed, fit, Q=5):
 	"""
 	## inputs
-	- `data`: shape `(M, )` log_10 abundance measurements
-	- `ivars`: shape `(M, )` inverse errors on the data
-	- `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
-	- `lnqs`: shape `(K, Nknot, M)` natural-logarithmic processes
-	- `knot_xs`: shape `(Nknot, )` metallicity bin centers
-	- `xs`: shape `(N, )` abundance data (used to interpolate the `lnqs`)
-	- Q softening parameter, smaller is more agressive 
 
 	## outputs
 	shape `(M, )` new array of ivars
@@ -35,16 +28,9 @@ def inflate_ivars(data, fixed, fit, Q=5):
 
 	return (data.allivars_orig * Q**2) / (Q**2 + diff**2 * data.allivars_orig)
 
-def A_step(data, fixed, lnqs, lnAs, I=None):
+def A_step(data, fixed, lnq_pars, lnAs, I=None):
     """
     ## inputs
-    - `lnqs`: shape `(K, Nknot, M)` natural-logarithmic processes
-    - `data`: shape `(N, M)` log_10 abundance measurements
-    - `sqrt_ivars`: shape `(N, M)` inverse variances on alldata
-    - `knot_xs`: shape `(Nknot, )` metallicity knot locations
-    - `xs`: shape `(N, )` metallicities (to use with the knots)
-    - `old_lnAs`: previous `lnAs`; used for initialization of the optimizer
-
     ## outputs
     shape `(K, N)` best-fit natural-logarithmic amplitudes
 
[…]

### 2023-10-17 API/kpm/regularize.py

@@ -42,16 +42,18 @@ class regularizations:
 
 		def __init__(self, data, fixed, init_q = 0.1):
 
-			q_array = np.zeros((fixed.K, fixed.Nknot, data.M))
+			q_array = np.zeros((fixed.K, fixed.J, data.M))
 			Lambdas = q_array + fixed.Lambda_c
-			q0s = q_array + init_q
+			q0s = q_array 
+			q0s[:,0,:] += init_q
 			fixed_q = q_array.astype(bool)
 
 			# 1: Strongly require that q_X = 1 for CC process for CC_elem
 			proc = fixed.processes == "CC"
 			elem = data.elements == fixed.CC_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = 1.0
+			q0s[    proc, :, elem] = 0.0
+			q0s[    proc, 0, elem] = 1.0
 			fixed_q[  proc, :, elem] = True
 
 			# 2: Require that q_X = 0 for ALL except CC process for CC_elem
@@ -65,20 +67,22 @@ class regularizations:
 			proc = fixed.processes == "CC"
 			elem = data.elements == fixed.Ia_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = fixed.q_CC_Fe + fixed.dq_CC_Fe_dZ * fixed.knot_xs[proc]
+			q0s[    proc, :, elem] = 0.0
+			q0s[    proc, 0, elem] = fixed.q_CC_Fe 
 			fixed_q[  proc, :, elem] = True
 
 			# 4: Strongly require that q_X sum to 1 for Ia_elem
 			proc = fixed.processes == "Ia"
 			elem = data.elements == fixed.Ia_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = 1.0 - (fixed.q_CC_Fe + fixed.dq_CC_Fe_dZ * fixed.knot_xs[proc])
+			q0s[    proc, :, elem] = 0.0
+			q0s[    proc, 0, elem] = 1.0 - fixed.q_CC_Fe
 			fixed_q[  proc, :, elem] = True
 
 			self._init_q = init_q
 			self._Lambdas = Lambdas
 			self._q0s = q0s
-			self._lnq0s = np.log(np.clip(q0s, 1.e-7, None))
[…]

### 2023-10-17 API/kpm/visualize.py

@@ -18,8 +18,8 @@ def plot_qs(data, fixed, fit):
     - Assumes a rigid structure for the processes?
     - Need to set size and number of subplots based on number of elements
     """
-    MgH = np.linspace(np.min(fixed.knot_xs[0]), np.max(fixed.knot_xs[0]), 300) # plotting xs
-    new_qs = np.exp(internal_get_lnqs(fixed.K, fit.lnqs, fixed.knot_xs, MgH)) # interp to plotting xs
+    MgH = np.linspace(fixed.xlim[0], fixed.xlim[1], 300) # plotting xs
+    new_qs = np.exp(internal_get_lnqs(fit.lnq_pars, fixed.L, MgH)) # interp to plotting xs
     # w22_MgH = w22_metallicities
     # w22_qs = np.exp(w22_lnqs)
 
@@ -45,7 +45,7 @@ def plot_qs(data, fixed, fit):
           plt.plot(MgH, new_q4, 'c-', alpha=0.9, label='q4')
 
         plt.xlabel('[Mg/H]')
-        plt.xlim(np.min(fixed.knot_xs), 0.55) #np.max(knot_xs))
+        plt.xlim(np.min(fixed.xs), np.max(fixed.xs))
         plt.ylabel('q '+data.elements[i])
         plt.ylim(-0.15, 1.5)
 

### 2023-10-17 API/kpm/general.py
fixed vmap and initialization bugs

@@ -35,8 +35,9 @@ def all_stars_KPM(fixed, fit):
                      + get_lnqs(fixed, fit), axis=0) / _LN10
 
 def fourier_sum(amps, argument):
-    foo = amps[0]
+    foo = amps[0] * jnp.ones_like(argument)
     for j in range(1, (len(amps) - 1) // 2 + 1):
+        #print('fourier_sum', j)
         foo += amps[2*j - 1] * jnp.cos(j * argument) \
              + amps[2*j]     * jnp.sin(j * argument)
     return foo

### 2023-10-17 API/kpm/initialize.py

@@ -23,6 +23,7 @@ def initialize_2(data, fixed):
 
 	regs = regularizations(data, fixed)
 	fit = fit_params(data, fixed)
+	print(np.shape(fit.lnq_pars))
 
 	fit.lnq_pars = jnp.where(regs.Q.fixed_q, regs.Q.lnq_par0s, fit.lnq_pars)
 
@@ -39,47 +40,47 @@ def initialize_2(data, fixed):
 
 
 def run_kpm(data, fixed, file_path, name='kpm_allstars', N_rounds=3, N_itters=16, overwrite=False):
-    """
+	"""
 	Maybe this should move to a different file
 
-    Add notes
-    N_itters = number of itterations of Aq step to run per round
-    N_rounds = number of rounds of itterations. After each itteration we recalculate the ivars and save
+	Add notes
+	N_itters = number of itterations of Aq step to run per round
+	N_rounds = number of rounds of itterations. After each itteration we recalculate the ivars and save
 
-    """
+	"""
 
-    # add error handeling so that N_rounds > 0 and N_itters > 0
-    # set some maximum limit on the number of itterations
+	# add error handeling so that N_rounds > 0 and N_itters > 0
+	# set some maximum limit on the number of itterations
 
-    # initialize fit
-    # should only initialize if first file doesn't exist
-    # Need to update so if early file is missing but later isn't it reruns whole thing
-    data, fit = initialize_2(data, fixed)
+	# initialize fit
+	# should only initialize if first file doesn't exist
+	# Need to update so if early file is missing but later isn't it reruns whole thing
+	data, fit = initialize_2(data, fixed)
 
-    pik_suffix = file_path+'/'+name+'_K'+str(fixed.K)+'_qccFe'+str(fixed.q_CC_Fe)
-    
-    # run round of itterations
-    for r in range(N_rounds):
-        pik_name = pik_suffix + '_' + str(r) + '.out'
-        if (os.path.isfile(pik_name)==True) and (overwrite==False):
-            print('File %s exists, loading data' % (pik_name))
-            with open(pik_name, "rb") as f:
-                fit, fixed = pickle.load(f)
-                # NEED TO CHECK IF FIXED IS THE SAME AS ORIGINAL
-                # NEED TO CHECK IF EMPTY
+	pik_suffix = file_path+'/'+name+'_K'+str(fixed.K)+'_qccFe'+str(fixed.q_CC_Fe)
 
[…]

### 2023-10-17 API/kpm/regularize.py

@@ -7,12 +7,12 @@ __all__ = ["regularizations"]
 
 class regularizations:
 
-	def __init__(self, data, fixed, init_q=0.1):
+	def __init__(self, data, fixed):
 
-		self.A = self.A(fixed)
-		self.Q = self.Q(data, fixed, init_q)
+		self.A = self.A_c(fixed)
+		self.Q = self.Q_c(data, fixed)
 
-	class A:
+	class A_c:
 		"""
 		Add Text
 
@@ -32,7 +32,7 @@ class regularizations:
 		def sqrt_Lambda_A(self):
 			return self._sqrt_Lambda_A
 
-	class Q:
+	class Q_c:
 
 		"""
 		Add Text
@@ -40,19 +40,18 @@ class regularizations:
 		TO DO: ADD For K>2
 		"""
 
-		def __init__(self, data, fixed, init_q = 0.1):
+		def __init__(self, data, fixed):
 
 			q_array = np.zeros((fixed.K, fixed.J, data.M))
 			Lambdas = q_array + fixed.Lambda_c
-			q0s = q_array 
-			q0s[:,0,:] += init_q
+			q0s = q_array + 1.0
 			fixed_q = q_array.astype(bool)
 
 			# 1: Strongly require that q_X = 1 for CC process for CC_elem
 			proc = fixed.processes == "CC"
 			elem = data.elements == fixed.CC_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = 0.0
+			q0s[    proc, :, elem] = 1.0
 			q0s[    proc, 0, elem] = 1.0
 			fixed_q[  proc, :, elem] = True
 
@@ -60,14 +59,15 @@ class regularizations:
 			proc = fixed.processes != "CC"
 			elem = data.elements == fixed.CC_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = 0.0
+			q0s[    proc, :, elem] = 1.0
+			q0s[    proc, 0, elem] = 0.0
 			fixed_q[  proc, :, elem] = True
 
 			# 3: Require that q_X has some value / form for CC process for Ia_elem
 			proc = fixed.processes == "CC"
 			elem = data.elements == fixed.Ia_elem
 			Lambdas[proc, :, elem] = fixed.Lambda_a
-			q0s[    proc, :, elem] = 0.0
[…]

### 2024-10-25 API/kpm/data.py
updating meta-data

@@ -31,9 +31,6 @@ class abund_data:
 	N: int
 		Number of stars
 
-	Class Methods
-	----------
-
 
 	TO DO
 	-----
@@ -379,10 +376,10 @@ class fixed_params:
 		else:
 			raise ValueError("First element of 'xlim' must be less than the \
 				second element.")
-		if (value[0] > np.nanmax(self._xs)) or (value[1] < np.nanmin(self._xs)):
-			raise ValueError("Attribute 'xlim' must overlap with 'xs' whose \
-				minimum is %s and maximum is %s" % (np.nanmin(self._xs,
-					np.nanmax(self._xs))))
+		# if (value[0] > np.nanmax(self._xs)) or (value[1] < np.nanmin(self._xs)):
+		# 	raise ValueError("Attribute 'xlim' must overlap with 'xs' whose \
+		# 		minimum is %s and maximum is %s" % (np.nanmin(self._xs,
+		# 			np.nanmax(self._xs))))
 
 		self._xlim = value
 		self._L = value[0] - value[1]
@@ -519,7 +516,6 @@ class fit_params:
 
 	lnAs: numpy array shape(K, N)
 		Array of log of process amplitudes for each star
-		ADD about dilution
 	"""
 
 	def __init__(self, data, fixed):

### 2024-10-25 API/kpm/general.py

@@ -7,34 +7,42 @@ import numpy as np
 
 def get_lnqs(fixed, fit):
     """
-    see `internal_get_lnqs` for actual information.
+    Calculate lnq values from lnq_pars
+
+    Inputs
+    ------
+    - `fixed`: KPM `fixed_params` class
+    - `fit`: KPM `fit_params` class
+
+    Outputs
+    -------
+    - shape `(K, N, M)` `lnqs` for all metallicities in `fixed.xs`
     """
     return internal_get_lnqs(fit.lnq_pars, fixed.L, fixed.xs, fit.lnAs, fixed.Delta)
 
-## Not needed 
-# def get_processes(K):
-#     processes_all = np.array(['CC', 'Ia', 'third', 'fourth']) # process names
-#     processes = processes_all[:K]
-#     return processes
-
 def all_stars_KPM(fixed, fit):
     """
-    ## inputs -- actually these are things in `fixed` and `fit`
-    - `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
-    - `lnq_pars`: shape `(K, 2*J+1, M)` amplitudes
-    - `xlim`: shape `(2, )` metallicity range
-    - `xs`: shape `(N, )` abundance data (used to get the `lnqs`)
+    Calculate all star abundances from fit parameters
 
-    ## outputs
-    shape `(M, )` log_10 abundances
+    Inputs
+    ------
+    - `fixed`: KPM fixed_params class
+    - `fit`: KPM fit_params class
 
-    ## comments
-    - Note the `ln10`.
+
+    Outputs
+    -------
+    - shape `(M, N)` log_10 predicted abundances
+
+    Comments
+    --------
+    - Note the `ln10`
     """
     return (logsumexp(fit.lnAs[:, :, None]
                      + get_lnqs(fixed, fit), axis=0) / _LN10) - (fixed.Delta)
 
 def fourier_sum(amps, argument):
+    # Used in internal_get_lnqs
     foo = amps[0] * jnp.ones_like(argument)
     for j in range(1, (len(amps) - 1) // 2 + 1):
         #print('fourier_sum', j)
@@ -42,33 +50,69 @@ def fourier_sum(amps, argument):
              + amps[2*j]     * jnp.sin(j * argument)
     return foo
 
+# Used in internal_get_lnqs
 fourier_sum_orama = vmap(vmap(fourier_sum, in_axes=(0, None), out_axes=1), \
[…]

### 2024-10-25 API/kpm/initialize.py

@@ -3,6 +3,7 @@ import numpy as np
 import jax.numpy as jnp
 import os
 import pickle
+import warnings
 
 from .data import fit_params
 from .regularize import regularizations
@@ -13,11 +14,19 @@ from ._globals import _LN10
 __all__ = ["initialize", "initialize_As", "find_As", "initialize_from_2"]
 
 def initialize(data, fixed, verbose=False): 
-	#, K, q_CC_Fe, dq_CC_Fe_dZ, elements, knot_xs, alldata, allivars_orig):
 	"""
-	## Bugs:
-	- very brittle
-	- relies on global variables
+	Initialize the fit from zero using only the process elements
+
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
+	- `fixed`: KPM `fixed_params` class
+	- `verbose`: boolean
+
+	Outputs
+	-------
+	- `data`: KPM `abund_data` class
+	- `fit`: KPM `fit_params` class
 	"""
 
 	regs = regularizations(data, fixed)
@@ -40,6 +49,22 @@ def initialize(data, fixed, verbose=False):
 	return data, fit
 
 def initialize_from_2(data, fixed, fit_2, verbose=False):
+	"""
+	Initialize the fit from previous K=2 fit using only the process elements
+
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
+	- `fixed`: KPM `fixed_params` class
+	- `fit_2`: KPM `fit_params` class with K=2
+	- `verbose`: boolean
+
+	Outputs
+	-------
+	- `data`: KPM `abund_data` class
+	- `fit`: KPM `fit_params` class
+	"""
+
 	fit = fit_params(data, fixed)
 	fit.lnq_pars[:2,:,:] = fit_2.lnq_pars
 	fit.lnAs[:2,:] = fit_2.lnAs[:2,:]
@@ -62,12 +87,20 @@ def initialize_from_2(data, fixed, fit_2, verbose=False):
 	
 
 def initialize_As(data, fixed, fit_old, verbose=False): 
-	#, K, q_CC_Fe, dq_CC_Fe_dZ, elements, knot_xs, alldata, allivars_orig):
 	"""
-	## Bugs:
-	- DOESN'T WORK for K > 2 ??
-	- very brittle
-	- relies on global variables
+	Initialize the As only from previous `lnq_parms`
+
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
[…]

### 2024-10-25 API/kpm/one_star.py

@@ -8,30 +8,39 @@ from .general import internal_get_lnqs
 
 def one_star_KPM(lnAs, lnqs, Delta):
     """
-    ## inputs
+    Calcualte abundances for one star
+
+    Inputs
+    ------
     - `lnAs`: shape `(K+1)` natural-logarithmic amplitudes
     - `lnqs`: shape `(K, M)` natural-logarithmic processes
-    - `D`: binary (1 = dilution on)
+    - `Delta`: float dilution value
 
-    ## outputs
-    shape `(M, )` log_10 abundances
+    Outputs
+    -------
+    - shape `(M, )` log_10 abundances
 
-    ## comments
+    Comments
+    --------
     - Note the `ln10`. 
     """
     return (logsumexp(lnAs[:, None] + lnqs, axis=0) / _LN10) - (Delta)
 
 def one_star_chi(lnAs, lnqs, alldata, sqrt_ivars, sqrt_Lambda_A, Delta):
     """
-    ## inputs
+    Calcualte chi value for one star 
+
+    Inputs
+    ------
     - `lnAs`: shape `(K, )` natural-logarithmic amplitudes
     - `lnqs`: shape `(K, M)` natural-logarithmic processes
     - `alldata`: shape `(M, )` log_10 abundance measurements
     - `sqrt_ivars`: shape `(M, )` inverse errors on the data
     - `sqrt_Lambda`: shape `(K, )` regularization strength on As
 
-    ## outputs
-    chi for this one star
+    Outputs
+    -------
+    - chi for one star
     """
 
     return jnp.concatenate([sqrt_ivars * (alldata - one_star_KPM(lnAs, lnqs, Delta)),
@@ -39,17 +48,22 @@ def one_star_chi(lnAs, lnqs, alldata, sqrt_ivars, sqrt_Lambda_A, Delta):
 
 def one_star_A_step(lnqs, alldata, sqrt_ivars, sqrt_Lambda_A, Delta, init):
     """
-    ## inputs
+    Optimize the lnA values for one star
+
+    Inputs
+    ------
     - `lnqs`: shape `(K, M)` natural-logarithmic processes 
     - `alldata`: shape `(M, )` log_10 abundance measurements
     - `sqrt_ivars`: shape `(M, )` inverse errors on the data
     - `sqrt_Lambda`: shape `(K, )` regularization
     - `init`: shape `(K,)` initial guess for the A vector
 
-    ## outputs
-    shape `(K,)` best-fit natural-logarithmic amplitudes
[…]

### 2024-10-25 API/kpm/optimize.py

@@ -13,12 +13,21 @@ __all__ = ["inflate_ivars", "A_step", "q_step", "Aq_step", "run_kpm"]
 
 def inflate_ivars(data, fixed, fit, Q=5):
 	"""
-	## inputs
+	Inflate `ivars` to discourage outliers from skewing model fits
 
-	## outputs
-	shape `(M, )` new array of ivars
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
+	- `fixed`: KPM `fixed_params` class
+	- `fit`: KPM `fit_params` class
+	- `Q`: int strength of ivar inflation
 
-	## comments
+	Outputs
+	-------
+	- shape `(M, )` new array of ivars
+
+	Comments
+	--------
 	- This sucks
 
 	"""
@@ -30,11 +39,23 @@ def inflate_ivars(data, fixed, fit, Q=5):
 
 def A_step(data, fixed, lnq_pars, lnAs, I=None, verbose=False):
 	"""
-	## inputs
-	## outputs
+	Optimize the `lnAs` for all stars
+
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
+	- `fixed`: KPM `fixed_params` class
+	- `lnq_pars`: shape `(K, J, M)` natural-logarithmic processes
+	- `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
+	- `I`: shape `(M)` boolean of element ids to include in the fit
+	- `verbose`: boolean print fit information
+
+	Outputs
+	-------
 	shape `(K, N)` best-fit natural-logarithmic amplitudes
 
-	## bugs
+	Comments
+	--------
 	- Ridiculous post-processing of outputs, with MAGIC numbers.
 	"""
    
@@ -57,19 +78,24 @@ def A_step(data, fixed, lnq_pars, lnAs, I=None, verbose=False):
 		new_lnAs = jnp.where(new_lnAs < -9.0, -9.0, new_lnAs)
 	return new_lnAs, dc2
 
+
 def q_step(data, fixed, lnq_pars, lnAs, verbose=False):
 	"""
-	## inputs
+	Optimize the `lnq_pars` for all stars
+
+	Inputs
+	------
+	- `data`: KPM `abund_data` class
+	- `fixed`: KPM `fixed_params` class
+	- `lnq_pars`: shape `(K, J, M)` natural-logarithmic processes
 	- `lnAs`: shape `(K, N)` natural-logarithmic amplitudes
-	- `alldata`: shape `(N, M)` log_10 abundance measurements
[…]

### 2024-10-25 API/kpm/regularize.py

@@ -6,6 +6,10 @@ from ._globals import *
 __all__ = ["regularizations"]
 
 class regularizations:
+	"""
+	Regularizations of process amplitudes (`A`) and process vector 
+	components (`Q`)
+	"""
 
 	def __init__(self, data, fixed):
 
@@ -14,10 +18,17 @@ class regularizations:
 
 	class A_c:
 		"""
-		Add Text
+		Regularizations of process amplitudes
 
-		sqrt_Lambda_A: jax array shape(K)
-		Array of squareroot of regularizations for all processes
+		Inputs
+		------
+		- `data`: KPM `abund_data` class
+		- `fixed`: KPM `fixed_params` class
+
+		Parameters
+		----------
+		- sqrt_Lambda_A: jax array shape(K)
+			Array of squareroot of regularizations for all processes
 
 		"""
 
@@ -32,10 +43,28 @@ class regularizations:
 	class Q_c:
 
 		"""
-		Add Text
+		Regularizations of process vector components
 
-		TO DO: ADD For K>2
-		# q0s array is confusing. First element is the value of a flat line
+		Inputs
+		------
+		- `data`: KPM `abund_data` class
+		- `fixed`: KPM `fixed_params` class
+
+		Parameters
+		----------
+		- Lambdas: shape(K, J, M)
+			Array of regularizations for all elements and all J
+		- q0s: shape(K, J, M)
+			Array of initial q params
+		- lnq_par0: shape(K, J, M)
+			Array of initial lnq params
+		- fixed_q: shape(K, J, M)
+			Array of boolean values to delineate which `lnq_params` are fixed
+
+
+		Comments
+		--------
+		- q0s array is confusing. First element is the value of a flat line
 		  subsequent values are the coefficients of cos/sin to deviate away 
 		"""
 

### 2024-10-25 API/kpm/visualize.py

@@ -14,10 +14,15 @@ __all__ = ["plot_qs", "plot_As", "plot_model_abundances", "plot_fk", "plot_chi2"
 
 def plot_qs(data, fixed, fit):
     """
-    # Bugs:
-    - Assumes a rigid structure for the processes?
-    - Need to set size and number of subplots based on number of elements
+    Creates a subplot of q vectors for all elements
+
+    Inputs
+    ------
+    - `data`: KPM `abund_data` class
+    - `fixed`: KPM `fixed_params` class
+    - `fit`: KPM `fit_params` class
     """
+
     MgH = np.linspace(fixed.xlim[0]-0.2, fixed.xlim[1]+0.2, 300) # plotting xs
     new_qs = np.exp(internal_get_lnqs(fit.lnq_pars, fixed.L, MgH, np.zeros((fixed.K, len(MgH))), fixed.Delta)) # interp to plotting xs
 
@@ -42,22 +47,39 @@ def plot_qs(data, fixed, fit):
     plt.tight_layout()
 
 def plot_As(fit):
-	plt.figure(figsize=(3,3))
+    """
+    Creates a plot of A2/A1 vs. A1 
 
-	Acc = np.exp(fit.lnAs[0,:])
-	AIa = np.exp(fit.lnAs[1,:])
+    Inputs
+    ------
+    - `data`: KPM `abund_data` class
+    - `fixed`: KPM `fixed_params` class
+    - `fit`: KPM `fit_params` class
+    """
+    plt.figure(figsize=(3,3))
 
-	plt.hist2d(Acc, AIa/Acc, bins=100, range=[[0,3],[-0.05,1.5]],
-	           norm=LogNorm(), cmap='PuOr_r', rasterized=True)
-	plt.xlabel(r'$A^{\rm CC}_{i}$', fontsize=12)
-	plt.ylabel(r'$A^{\rm Ia}_{i}/A^{\rm CC}_{i}$', fontsize=12)
+    Acc = np.exp(fit.lnAs[0,:])
+    AIa = np.exp(fit.lnAs[1,:])
+
+    plt.hist2d(Acc, AIa/Acc, bins=100, range=[[0,3],[-0.05,1.5]],
+               norm=LogNorm(), cmap='PuOr_r', rasterized=True)
+    plt.xlabel(r'$A^{\rm CC}_{i}$', fontsize=12)
+    plt.ylabel(r'$A^{\rm Ia}_{i}/A^{\rm CC}_{i}$', fontsize=12)
 
[…]

### 2024-10-25 2024_KPM_paper/LaTex/main.tex

--- 2023-10-16 Paper/main.tex
@@
 
-\documentclass[modern, linenumbers]{aastex631}
+\documentclass[modern]{aastex631}
 \usepackage{amsmath}
@@
 \usepackage{soul}
-% \usepackage{lineno}
-% \linenumbers
 
@@
 \newcommand{\add}[1]{\textcolor{teal}{#1}}
-
+\newcommand{\remove}[1]{\textcolor{red}{#1}}
 \newcommand{\hogg}[1]{\textcolor{blue}{Hogg says: #1}}
@@
 
-\author[0000-0003-1124-7378]{Bridget Ratcilffe}
+\author[0000-0003-1124-7378]{Bridget Ratcliffe}
 \affiliation{Leibniz-Institut f\"{u}r Astrophysik Potsdam (AIP), An der Sternwarte 16, 
@@
 \begin{abstract}\noindent
-The element abundance pattern found by APOGEE in Milky Way disk stars is close to two-dimensional, dominated by production from one prompt process and one delayed process.
-This is remarkable, since the elements are known to be produced by many more than two nucleosynthetic sources.
-We fit the abundances of 14 elements for 48,659 red-giant stars from APOGEE DR17 using a flexible, data-driven $K$-process model---dubbed \name.
+The element abundance pattern found in Milky Way disk stars is close to two-dimensional, dominated by production from one prompt process and one delayed process. 
+This simplicity is remarkable, since the elements are produced by a multitude of nucleosynthesis mechanisms operating in stars with a wide range of progenitor masses. 
+We fit the abundances of 14 elements for 48,659 red-giant stars from APOGEE DR17 using a flexible, data-driven K-process model---dubbed \name. 
 In our fiducial model, with $K=2$, each abundance in each star is described as the sum of a prompt and a delayed process contribution. 
-We find that \name{} with $K=2$ is able to explain the abundances well, recover the observed abundance bimodality, and detect the bimodality over a greater range in metallicity than previously has been possible.
-We compare to prior work by \citet{weinberg2022}, finding that \name{} produces similar results, but that \name{} better predicts stellar abundances, especially for elements C+N and Mn and for stars at super-solar metallicities.
-The model makes assumptions, including especially that it fixes some parameters to break degeneracies and improve interpretability; we find that some of the nucleosynthetic implications are dependent upon these detailed parameter choices.
-We add a third and fourth process (to make $K=4$), finding that the additional processes give the model more freedom and improve the model's ability to predict the stellar abundances, as expected, but they don't qualitatively change the story.
-The results of \name{} have implications for the formation of the Galaxy disk, the relationship between abundances and ages, and the physics of nucleosynthesis.
+We find that \name with $K=2$ is able to explain the abundances well, recover the observed abundance bimodality, and detect the bimodality over a greater range in metallicity than previously has been possible.
+We compare to prior work by \citet{weinberg2022}, finding that \name produces similar results, but that \name better predicts stellar abundances, especially for elements C+N and Mn and for stars at super-solar metallicities.
+The model fixes the relative contribution of the prompt and delayed process to two elements to break degeneracies and improve interpretability; we find that some of the nucleosynthetic implications are dependent upon these detailed choices.
+We find that moving to four processes adds flexibility and improves the model's ability to predict the stellar abundances, but doesn't qualitatively change the story. 
+The results of \name will help us to interpret and constrain the formation of the Galaxy disk, the relationship between abundances and ages, and the physics of nucleosynthesis.
 \end{abstract}
@@
 In the long run, it is incumbent upon us to understand these issues and correct the assumptions or calculations underlying our nucleosynthetic and astrophysical models.
-In the short run, however, we gather data---tens of millions of abundance measurements on millions of stars in different astronomical surveys such as RAVE, SEGUE, LAMOST, Gaia-ESO, APOGEE/MWM, GALAH, and H3 \citep{steinmetz2006, yanny2009, gilmore2012, desilva2015, luo2015, majewski2017, conroy2019}.
+In the short run, however, we gather data---tens of millions of abundance measurements on millions of stars in different astronomical surveys such as RAVE \citep{steinmetz2006}, SEGUE \citep{yanny2009}, LAMOST \citep{luo2015}, Gaia-ESO \citep{gilmore2012, gilmore2022}, APOGEE/MWM \citep{majewski2017}, GALAH \citep{desilva2015}, and H3 \citep{conroy2019}.
 This raises the question: \emph{Can we take a data-driven approach to nucleosynthesis?}
@@
 [Fe/H]\footnote{Where $[{\rm X}/{\rm Y}] = \log({\rm X}/{\rm Y}) - \log({\rm X}/{\rm Y})_{\odot}$ and $({\rm X}/{\rm Y})_{\odot}$ is the solar abundance ratio.} \citep[e.g.,][]{fuhrmann1998, bensby2003, adibekyan2012} to separate stars into populations with high and low SNIa enrichment.
+As established in \citet{griffith2019}, these populations are referred to as high-Ia and low-Ia, to reflect their enrichment origins, instead of the traditional low-$\alpha$ and high-$\alpha$ nomenclature.
+We adopt this updated naming convention in this \documentname.
 Using the median [X/Mg] vs.
-[Mg/H] abundance trends, these works explain data from the GALAH\footnote{GALAH = GALactic Archaeology with HERMES.} and SDSS-IV APOGEE\footnote{APOGEE = Apache Point Observatory Galactic Evolution Experiment, part of the Sloan Digital Sky Survey} surveys, respectively, with a two-process model.
+[Mg/H] abundance trends, these prior works explain data from the GALAH\footnote{GALAH = GALactic Archaeology with HERMES.} and SDSS-IV APOGEE\footnote{APOGEE = Apache Point Observatory Galactic Evolution Experiment, part of the Sloan Digital Sky Survey} surveys, respectively, with a two-process model.
 Because the median abundance trends in [X/Mg] vs.
@@
 The parameters output by our model can thus be used as de-noised abundance labels; these will sharpen relationships between abundances and stellar parameters (including birth location and time).
-Our main contribution is to construct a data-driven model for nucleosynthesis that has good statistical properties, only enforcing constraints to break rotational degeneracies.
+Our main contribution is to construct a data-driven model for nucleosynthesis that has good statistical properties, only enforcing a small number of constraints to break the degeneracies that arise in models of this form.
 All other \name{} parameters are set by the data with no fixed normalization.
@@
 where ``noise'' represents observational noise and/or other sources of intrinsic abundance scatter that are not included in this model.
-For detailed examples of a similar model with $K=2$, see Section 2 and Figures 2 and 3 of W22.
+For detailed examples of a similar model with $K=2$, see Section 2 and Figures 2 and 3 of W22, where they demonstrate the vector addition and describe the process parameters for a few example stars.
 
-In \name{}, we put forth the following set of assumptions:
+In \name{}, we adopt the following set of assumptions:
 
@@
 These processes themselves will depend on metallicity, but a linear sum is sufficient to explain all element abundances at any overall metallicity.
-Because yields depend on stellar masses and progenitor structure, and because different stars can get to their metallicities by different histories, this assumption must be at least slightly wrong in detail.
+Because different stars can get to their metallicities by different histories, and because detailed abundances beyond metallicity must matter at some level, the true enrichment mechanism is at least slightly nonlinear; thus this assumption
+must be at least slightly wrong in detail.
 
@@
 All Mg is produced in a prompt process and no other processes contribute to its production.
-This is substantiated by theoretical yields where Mg is purely produced by prompt CCSN \citep[e.g.,][]{anderson2019, rybizki2017}.
+This is substantiated by theoretical yields where Mg is purely produced by prompt CCSN \citep[e.g.,][]{woosley1995, arnett1996, anderson2019, rybizki2017}.
 This assumption (along with non-negativity) breaks a set of symmetries in the process space and makes the processes quasi-interpretable in terms of nucleosynthesis sources.
@@
 Fe is produced through a combination of a prompt and delayed process.
-Because the delayed process is likely dominated by SNIa \citep[e.g.,][]{andrews2017}, we label the delayed process with ``Ia''\footnote{While other enrichment channels with similar timescales may be included in the respective processes, the ``CC'' and ``Ia'' naming convention conforms to the choices in W22 and G22, and avoids the possible confusion of process numbers (1 and 2) with supernova type (II and Ia).}.
+Because the delayed process is likely dominated by SNIa \citep[e.g.,][]{thielemann2002, andrews2017}, we label the delayed process with ``Ia''\footnote{While other enrichment channels with similar timescales may be included in the respective processes, the ``CC'' and ``Ia'' naming convention conforms to the choices in W22 and G22, and avoids the possible confusion of process numbers (1 and 2) with supernova type (II and Ia).}.
 While the prompt process constraint (Mg) is grounded in nucleosynthesis theory, there is no equivalent nucleosynthesis fact to constrain the delayed process.
@@
 We permit the process vector components for all elements other than Mg and Fe to float as a function of metallicity.
-The variation is parameterized by a linear spline in log-process space, attached to a set of variable control points.
-We assume that a particular set of hard-coded knots are sufficient to capture the metallicity dependence.
+The variation is parameterized by a linear spline in log-process space, attached to a set of variable control points, knots, where the piecewise functions are joined.
+We assume that a particular set of 11 hard-coded knots between [Mg/H] of -0.8 and 0.6 are sufficient to capture the metallicity dependence.
+We choose knot number and location such that we capture the complex metallicity dependence of the abundance trends while maintaining a sufficient number of stars to fit with each linear component.
 
@@
 The actual derived values of $q_{k,j}^{Z}$ will be affected by systematic offsets in the abundances.
-We add a softening parameter $Q$ (Equation~\ref{eq:inflate_ivar}) to allow for the possibility that APOGEE observational errors are underestimated or that there is intrinsic scatter around the \name{} predictions.
+We add a softening parameter $Q$ (Equation~\ref{eq:inflate_ivar}) to allow for the possibility that APOGEE observational errors are underestimated, or that there is intrinsic scatter around the \name{} predictions.
 
@@
 where $Q$ is a softening parameter.
-Our results are largely insensitive to the choice of $Q$ (e.g., $1 < Q < 10$), so we choose to set $Q=5$.
-Very small values (e.g., $Q=.1$) will erase some of the abundance structure and produce poorer fits.
+Our results are largely insensitive to the choice of $Q$.
+We find that the predicted abundances of all elements change by less than 0.01 dex for Q between 1 and 10, so we choose to set $Q=5$.
+Very small Q values (e.g., $Q=.1$) will erase some of the abundance structure and produce poorer fits.
 
@@
 While our stellar sample extends from Galactic center, to the outer disk, to the halo, the majority of our stars ($75\%$) are within 3.5 kpc of the sun.
-Further, $94\%$ of our stellar sample has an eccentricity less than 0.4, indicative of \textit{in situ} origin.
-In this paper, we assume that the KPM fits will be consistent across the Galactic disk, as the median high-Ia and low-Ia [X/Mg] vs.
+Further, $94\%$ of our stellar sample has an eccentricity less than 0.4, indicative of \textit{in situ} origin \citep[e.g.,][]{sales2009}.
+In this paper, we assume that the \name fits will be consistent across the Galactic disk, as the median high-Ia and low-Ia [X/Mg] vs.
 [Mg/H] abundance tends are insensitive to Galactic location (W19, \citealp{griffith2021a}).
+While we fit a large sample of stars in this work, \name performs similarly when fitting smaller populations, down to 500 stars.
 \begin{figure*}[htb!]
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/star_sample.pdf}
+    \includegraphics[width=\textwidth]{star_sample.pdf}
     \caption{Left: distribution of our stellar sample in $Z$ (kpc) vs.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/all_param1.pdf}
+    \includegraphics[width=\textwidth]{all_param1.pdf}
     \caption{Abundance distributions and \name{} parameters for C+N, $\alpha$, and light odd-$Z$ elements.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/all_param2.pdf}
+    \includegraphics[width=\textwidth]{all_param2.pdf}
     \caption{Same as Figure~\ref{fig:all_param1}, but for Fe-peak elements and Ce.}
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/As.pdf}
+    \includegraphics[width=\textwidth]{As.pdf}
     \caption{Left: distribution of $\AIa/\Acc$ vs.
@@
 For these elements the scatter in the observed abundance distribution is larger than in the predicted distribution, suggesting that the APOGEE observational scatter is underestimated, that there are $\teff$ or $\logg$ dependent abundance trends (e.g., \citealp{griffith2021a}, W22), or that the $K=2$ model is insufficient--a likely case for elements produced by AGB stars, such as C+N and Ce.
+The model performs similarly well when the population is downsampled to 5000, 1000, and 500 stars, though the number of nodes has to be decreased from 11 to 7.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/comp_w22.pdf}
+    \includegraphics[width=\textwidth]{comp_w22.pdf}
     \caption{Left: cumulative distribution of $\log_{10}(\chi^2)$ for W22 (dashed orange line) and our fiducial model (G23, solid purple line).
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMg.pdf}
+    \includegraphics[width=\textwidth]{qccFe_FeMg.pdf}
     \caption{Minimum [Fe/Mg] value attainable for $\qccFe$ and $\dqccFe$ assumptions.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_FeMgpred.pdf}
+    \includegraphics[width=\textwidth]{qccFe_FeMgpred.pdf}
     \caption{Top: observed [Fe/Mg] vs.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/qccFe_fcc.pdf}
+    \includegraphics[width=\textwidth]{qccFe_fcc.pdf}
     \caption{Elemental median values of $\fcc$ at solar metallicity for the low-Ia population for \name{} with $\qccFe=0.35$ (darkest purple) to 0.5 (lightest purple) and $\dqccFe=0.0$.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/A4s.pdf}
+    \includegraphics[width=\textwidth]{A4s.pdf}
     \caption{$A^k_i/\Acc$ vs.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/all_param_k4.pdf}
+    \includegraphics[width=\textwidth]{all_param_k4.pdf}
     \caption{Left: [X/Mg] vs.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/comp_Ks.pdf}
+    \includegraphics[width=\textwidth]{comp_Ks.pdf}
     \caption{Left: cumulative distribution of $\log_{10} (\chi^2)$ for the $K=2$ model (dotted light purple line) and the $K=4$ model (solid dark purple line).
@@
 If our assumptions are incorrect and, for instance, Mg is not a pure prompt element or (in the $K=4$ case) Fe has contributions from multiple delayed sources, our nucleosynthetic interpretation of \name{} may be wrong.
-This becomes more challenging as $K$ increases and we have to make more assumptions to break rotational symmetries.
+This becomes more challenging as $K$ increases and we have to make more assumptions to break rotational symmetries (the symmetries in which the process amplitudes and the process vectors are transformed in corresponding ways to leave the predictions unchanged).
 Additionally, assumption (7) states that the APOGEE data products can be used for this project, but we inflate outlying-star abundance errors with a softening parameter, $Q$ to account for their likely underestimation.
@@
     \centering
-    \includegraphics[width=.9\textwidth]{Paper/Figures/pop_divis.pdf}
+    \includegraphics[width=.9\textwidth]{pop_divis.pdf}
     \caption{Left: distribution of stars in $\AIa/\Acc$ vs.
@@
     \centering
-    \includegraphics[width=.6\textwidth]{Paper/Figures/AIaAcc_age.pdf}
+    \includegraphics[width=.6\textwidth]{AIaAcc_age.pdf}
     \caption{$\AIa/\Acc$ vs.
@@
 Finally, because of the flexibility of \name{}, new scientific applications are enabled that were not feasible before.
-Because \name{} does not rely on [Mg/Fe] vs.
+Because \name{} performs well with a low number of stars and does not rely on [Mg/Fe] vs.
 [Fe/H] bimodality, non-bimodal populations can now be fit with a multi-component nucleosynthetic model.
@@
 This data-driven model opens doors to many new research projects and exciting future scientific results.
-To use \name{} yourself, please reference the KPM GitHub repository\footnote{\url{https://github.com/13emilygriffith/KProcessModel}} or contact the corresponding author.
+To use \name{} yourself, please reference the \name{} GitHub repository\footnote{\url{https://github.com/13emilygriffith/KProcessModel}} or contact the corresponding author.
 
